---
title: "Hypothesis Tests: H1a to H4b"
author: "Master's Thesis -- Media Quality / Media Diet"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = FALSE, message = TRUE)
```

# Overview

Estimates the models of Chapter 4 on the analysis dataset built by `03a`. No
merging happens here; the dataset is read as-is.

All models are estimated separately by wave. Each wave covers one policy topic
and its own randomization, so there are no wave fixed effects and no
clustering: each model contains at most one observation per participant.

## Structure

| Part | Content | Equation |
|---|---|---|
| 1--2 | Setup, data, coverage |  |
| 2b | Covariate missingness and the covariate-complete subsample |  |
| 3 | Benchmark ITT and first stage, on uptake and on effort | 4.11, 4.12 |
| 4 | Encountered quality: three estimation samples, observability, scored cases by arm, Lee bounds | 4.13 |
| 5 | H1b: effort and encountered quality | 4.14 |
| 6 | H2: quality and attitude change, three estimation samples | 4.15 |
| 7 | H3a: quality pathway by habitual-quality group | 4.16 |
| 8 | H4a: treatment effect by habitual-quality group, split and continuous | 4.17 |
| 9 | H4b: subgroup LATE, split, continuous, and reduced form | 4.18, 4.19 |
| 10 | H3b: conditional indirect effects and sensitivity | 4.20--4.22 |
| 11 | Sensitivity: weightings, category sets, need for cognition |  |
| 12 | Knowledge outcome |  |
| 13 | Detection limits: MDE and design analysis |  |
| 14 | Hypothesis index |  |

## Reading rules fixed in advance

| Rule | Applies to |
|---|---|
| A subgroup difference requires the interaction term, not two separate significances | H3a, H4a, H4b |
| Indirect effects are assumption-dependent and labelled as such | H3b |
| A weak first stage makes a LATE uninformative, not null | H4b |
| Where a 2SLS estimate and its reduced form disagree materially, the reduced form governs | H4b |
| An estimate below the minimum detectable effect of its own model is read as imprecise, whether or not it reaches significance | all |
| Wave 2 quality estimates rest on 22 to 24 participants and are read as imprecise | H1a, H1b, H2, H3a, H3b |

## Outputs

Tables are written as LaTeX fragments to `Output/03_analysis/tables/` and as
CSV alongside.

| File | Content |
|---|---|
| `tab_covariate_missingness` | Covariates with missing values, by wave |
| `tab_itt_absolute`, `tab_itt_signed` | ITT on absolute and signed attitude change |
| `tab_first_stage`, `tab_first_stage_effort` | First stage on uptake and on effort |
| `tab_h1a_treatment_quality` | Encountered quality, three estimation samples |
| `tab_h1a_observability` | Treatment effect on quality-score observability |
| `tab_h1a_scored_by_arm` | Participants with a constructible quality score, by arm |
| `tab_h1a_lee_bounds` | Trimming bounds on encountered quality |
| `tab_h1b_effort_quality` | Effort and encountered quality |
| `tab_h2_quality_attitude` | Quality and attitude change, three estimation samples |
| `tab_h3a_quality_moderation` | Quality pathway by habitual-quality group |
| `tab_h4a_treatment_moderation` | Treatment effect by habitual-quality group |
| `tab_h4a_common_sample` | H4a on a sample common to all three diet definitions |
| `tab_h4a_continuous` | H4a under a continuous moderator |
| `tab_h4b_late_full`, `tab_h4b_late_interaction`, `tab_h4b_subgroups` | Uptake LATE, interaction, subgroups |
| `tab_h4b_continuous` | H4b under a continuous moderator |
| `tab_h3b_indirect_effects`, `tab_h3b_sensitivity` | Conditional indirect effects and sensitivity |
| `tab_sens_weighting`, `tab_sens_category_set`, `tab_sens_nfc` | Sensitivity analyses |
| `tab_knowledge_*` | Knowledge outcome: ITT, ANCOVA, quality, LATE, moderation |
| `tab_detection_limits`, `tab_design_analysis` | MDE and design analysis |
| `hypothesis_index.csv` | Hypothesis-to-table index |

# Part 1: Setup

```{r libraries, message=FALSE, warning=FALSE}

library(dplyr)
library(tidyr)
library(purrr)
library(readr)
library(stringr)
library(AER)
library(broom)
library(mediation)

# AER and mediation load MASS, whose select() masks dplyr's.
select <- dplyr::select
filter <- dplyr::filter
```


```{r paths-config, echo=FALSE}
project_root <- "~/Desktop/GitHub/DoesMediaQualityMatter"
input_dir  <- file.path(project_root, "Output", "03_analysis_data")
table_dir  <- file.path(input_dir, "tables")
dir.create(table_dir, showWarnings = FALSE, recursive = TRUE)
```


```{r config}
WAVE_TOPICS <- c("1" = "Child support", "2" = "Energy transition", "3" = "Cannabis")

# Short labels for tables; full names stay in the console output.
TOPIC_SHORT <- c("Child support" = "T1", "Energy transition" = "T2", "Cannabis" = "T3")
TOPIC_NOTE  <- "T1 = child support, T2 = renewable-energy transition, T3 = cannabis legalization."

DIET_VARIANTS <- c("overall", "news", "news_corrected")
DIET_SHORT    <- c("overall" = "All", "news" = "OIE-a", "news_corrected" = "OIE-c")
DIET_NOTE <- "All = overall scored OIE; OIE-a = automatically classified OIE; OIE-c = manually coded OIE."

# Covariate set, minus the wave-specific ones added per model where relevant.
COVARS <- c("att_baseline", "prior_engagement", "polknow_total",
            "pol_interest_general", "newsuse_online", "edu_time", "age", "gender_f")

set.seed(20260912)
N_BOOT <- 2000
```


Three helpers: fit a model and return a tidy row set, format numbers, and
write a LaTeX fragment in the thesis table style.

```{r helpers-estimation}
# OLS or 2SLS depending on whether an instrument is supplied.
fit_model <- function(data, y, rhs, instruments = NULL, keep = NULL) {
  f <- if (is.null(instruments)) {
    as.formula(paste(y, "~", paste(rhs, collapse = " + ")))
  } else {
    as.formula(paste(y, "~", paste(rhs, collapse = " + "), "|",
                     paste(instruments, collapse = " + ")))
  }
  fit <- try(if (is.null(instruments)) lm(f, data = data) else ivreg(f, data = data),
             silent = TRUE)
  if (inherits(fit, "try-error")) return(NULL)

  out <- broom::tidy(fit, conf.int = TRUE, conf.level = 0.95) %>%
    transmute(term, estimate, std.error, conf.low, conf.high, p.value) %>%
    mutate(n = nobs(fit))

  g <- tryCatch(broom::glance(fit), error = function(e) NULL)
  out$r2     <- if (!is.null(g) && "r.squared" %in% names(g)) g$r.squared else NA_real_
  out$adj_r2 <- if (!is.null(g) && "adj.r.squared" %in% names(g)) g$adj.r.squared else NA_real_

  pick <- function(d, pattern, col, agg = function(x) x[1]) {
    if (is.null(d) || !col %in% colnames(d)) return(NA_real_)
    hit <- grep(pattern, rownames(d))
    if (length(hit) == 0) return(NA_real_)
    unname(agg(d[hit, col]))
  }

  if (!is.null(instruments)) {
    d <- tryCatch(summary(fit, diagnostics = TRUE)$diagnostics,
                  error = function(e) NULL)
    out$first_stage_F <- pick(d, "^Weak instruments", "statistic", min)
    out$wu_hausman_p  <- pick(d, "^Wu-Hausman", "p.value")
    out$sargan_p      <- pick(d, "^Sargan", "p.value")
  } else {
    out$first_stage_F <- NA_real_
    out$wu_hausman_p  <- NA_real_
    out$sargan_p      <- NA_real_
  }

  if (!is.null(keep)) out <- out %>% filter(str_detect(term, keep))
  out
}

# Run one specification across all three waves.
across_waves <- function(dat, ...) {
  imap_dfr(dat, function(d, nm) {
    res <- fit_model(d, ...)
    if (is.null(res)) return(NULL)
    res %>% mutate(wave = as.integer(str_remove(nm, "wave")), .before = 1)
  }) %>%
    mutate(topic = WAVE_TOPICS[as.character(wave)], .after = wave)
}

stars <- function(p) case_when(is.na(p) ~ "", p < .001 ~ "***", p < .01 ~ "**",
                               p < .05 ~ "*", p < .10 ~ "+", TRUE ~ "")
```

```{r helpers-latex}
# Booktabs table in the style of a regression table: estimate with significance
# markers, standard error in parentheses, confidence interval, exact p-value,
# and sample size. Topic and variant labels are abbreviated, with the key in
# the note.
write_latex_table <- function(df, file, digits = 3, caption = NULL,
                              label = NULL, note = NULL) {

  esc  <- function(x) str_replace_all(as.character(x), "([_%&#$])", "\\\\\\1")
  num  <- function(x, d = digits) ifelse(is.na(x), "--", formatC(x, format = "f", digits = d))
  # Integer-valued columns are printed without decimals.
  is_int <- function(x) is.numeric(x) && all(is.na(x) | abs(x - round(x)) < 1e-9)
  pfmt <- function(p) ifelse(is.na(p), "--",
                      ifelse(p < .001, "$<$.001",
                             sub("^0", "", formatC(p, format = "f", digits = 3))))

  d <- df

  if ("Topic" %in% names(d)) {
    d$Topic <- dplyr::coalesce(TOPIC_SHORT[as.character(d$Topic)], as.character(d$Topic))
    d$Topic <- factor(d$Topic, levels = c("T1", "T2", "T3"))
    d <- d %>% arrange(Topic, .by_group = FALSE)
    d$Topic <- as.character(d$Topic)
  }
  if ("Variant" %in% names(d)) {
    d$Variant <- dplyr::coalesce(DIET_SHORT[as.character(d$Variant)], as.character(d$Variant))
  }
  if ("Category set" %in% names(d)) {
    lab <- c(primary = "Primary", news_only = "News only", incl_search = "Incl. search")
    d[["Category set"]] <- dplyr::coalesce(lab[as.character(d[["Category set"]])],
                                           as.character(d[["Category set"]]))
  }

  # Significance markers merged into the estimate column, then dropped.
  est_col <- intersect(c("Estimate", "Split", "Continuous (per SD)",
                         "Reduced form", "Naive diff"), names(d))
  if (length(est_col) && "Sig" %in% names(d)) {
    s <- ifelse(d$Sig == "" | is.na(d$Sig), "", paste0("$^{", d$Sig, "}$"))
    d[[est_col[1]]] <- paste0(num(d[[est_col[1]]]), s)
    d$Sig <- NULL
  }

  # Confidence bounds collapsed into one bracketed column.
  ci <- intersect(c("CI low", "CI_low", "conf.low"), names(d))
  ch <- intersect(c("CI high", "CI_high", "conf.high"), names(d))
  if (length(ci) && length(ch)) {
    d[["95% CI"]] <- paste0("[", num(d[[ci]]), ", ", num(d[[ch]]), "]")
    d[[ci]] <- NULL; d[[ch]] <- NULL
    d <- d %>% relocate(`95% CI`, .after = any_of(c("SE", est_col, "Estimate")))
  }

  if ("SE" %in% names(d)) d$SE <- ifelse(is.na(d$SE), "--", paste0("(", num(d$SE), ")"))
  if ("p"  %in% names(d)) d$p  <- pfmt(d$p)

  body <- d %>%
    mutate(across(where(is_int), ~ num(.x, 0))) %>%
    mutate(across(where(is.numeric), ~ num(.x))) %>%
    mutate(across(everything(), ~ {
      x <- as.character(.x)
      x <- ifelse(is.na(x) | x == "NA", "--", x)
      # Leave cells that already contain maths or brackets untouched.
      ifelse(str_detect(x, "\\$|\\[|\\("), x, esc(x))
    }))

  hdr <- names(d)
  hdr <- ifelse(hdr == "adj. R2", "adj. $R^2$", esc(hdr))

  rows <- apply(body, 1, function(r) paste0("  ", paste(r, collapse = " & "), " \\\\"))

  notes <- c(TOPIC_NOTE,
             if ("Variant" %in% names(df)) DIET_NOTE,
             note,
             "$^{+}p<.10$, $^{*}p<.05$, $^{**}p<.01$, $^{***}p<.001$.")
  notes <- paste(notes[!is.na(notes)], collapse = " ")

  lines <- c(
    "\\begin{table}[htbp]",
    "\\centering",
    "\\begin{threeparttable}",
    if (!is.null(caption)) paste0("\\caption{", caption, "}"),
    paste0("\\label{tab:", if (is.null(label)) file else label, "}"),
    paste0("\\begin{tabular}{l", paste(rep("c", ncol(d) - 1), collapse = ""), "}"),
    "\\toprule",
    paste0("  ", paste(hdr, collapse = " & "), " \\\\"),
    "\\midrule",
    rows,
    "\\bottomrule",
    "\\end{tabular}",
    paste0("\\begin{tablenotes}\\footnotesize\\item \\textit{Note.} ", notes, "\\end{tablenotes}"),
    "\\end{threeparttable}",
    "\\end{table}"
  )

  writeLines(lines[!is.na(lines)], file.path(table_dir, paste0(file, ".tex")))
  write_csv(df, file.path(table_dir, paste0(file, ".csv")))
  invisible(df)
}


# Standard presentation: one row per wave, estimate with stars, SE, CI, p, N,
# and the model fit where it is defined.
present <- function(res, term_filter, label_col = "Topic", fit = TRUE, digits = 3) {
  out <- res %>%
    filter(str_detect(term, term_filter)) %>%
    transmute(Topic = topic,
              Estimate = round(estimate, digits),
              SE = round(std.error, digits),
              `CI low` = round(conf.low, digits),
              `CI high` = round(conf.high, digits),
              p = round(p.value, 3),
              Sig = stars(p.value),
              N = n,
              `adj. R2` = round(adj_r2, 3))
  if (!fit || all(is.na(out[["adj. R2"]]))) out[["adj. R2"]] <- NULL
  out
}
```

# Part 2: Data

```{r load-data}
analysis_data <- readRDS(file.path(input_dir, "analysis_data_by_wave.Rds"))

stopifnot(length(analysis_data) == 3)
imap(analysis_data, ~ cat(.y, ":", nrow(.x), "rows\n")) %>% invisible()

# Coverage of the variables that limit the quality models.
map_dfr(analysis_data, ~ tibble(n = nrow(.x),
                                q_primary = sum(!is.na(.x$q_primary)),
                                uptake = sum(!is.na(.x$exp_topic_uptake_yn))),
        .id = "wave") %>%
  as.data.frame() %>% print()
```
## Part 2b: Estimation Samples
```{r estimation-samples}


# Two conditions restrict a model's sample and are kept apart here:
# covariate missingness (prior_engagement, from the survey) and exposure
# coverage (q_primary, from the tracking data).

covar_missing <- map_dfr(analysis_data, function(d) {
  summarise(d, across(all_of(COVARS), ~ sum(is.na(.x))))
}, .id = "wave") %>%
  pivot_longer(-wave, names_to = "Covariate", values_to = "n_missing") %>%
  filter(n_missing > 0) %>%
  pivot_wider(names_from = wave, values_from = n_missing, values_fill = 0L) %>%
  rename_with(~ unname(TOPIC_SHORT[WAVE_TOPICS[str_remove(.x, "wave")]]),
              starts_with("wave"))

cat("Covariates with missing values (blank means complete):\n")
print(as.data.frame(covar_missing))

# The covariate-complete subsample. lm() drops incomplete rows, so adjusted
# models are fitted on it in any case.
cc_data <- map(analysis_data, ~ filter(.x, if_all(all_of(COVARS), ~ !is.na(.x))))

map_dfr(list(full = analysis_data, complete = cc_data),
        ~ map_dfr(.x, ~ tibble(n = nrow(.x)), .id = "wave"),
        .id = "sample") %>%
  pivot_wider(names_from = sample, values_from = n) %>%
  mutate(lost = full - complete) %>%
  as.data.frame() %>% print()

write_latex_table(covar_missing, "tab_covariate_missingness",
                  caption = "Covariate missingness by wave")
```

# Part 3: Benchmark Effects and First Stage (Eq. 4.11, 4.12)

Not a hypothesis of this thesis. These models establish comparability with
the original study and supply the treatment and first-stage quantities the
IV models in Part 9 require.

```{r benchmark-itt}
itt_abs <- across_waves(analysis_data, y = "y_abs",
                        rhs = c("t_verbal", "t_money"))
itt_signed <- across_waves(analysis_data, y = "y_signed",
                           rhs = c("t_verbal", "t_money"))

cat("ITT on absolute attitude change:\n")
tab_itt_abs <- bind_rows(
  present(itt_abs, "^t_verbal") %>% mutate(Arm = "Verbal", .after = Topic),
  present(itt_abs, "^t_money")  %>% mutate(Arm = "Monetary", .after = Topic)
) %>% arrange(Topic, Arm)
print(as.data.frame(tab_itt_abs))
write_latex_table(tab_itt_abs, "tab_itt_absolute", caption = "ITT, absolute change")

cat("\nITT on signed attitude change:\n")
tab_itt_signed <- bind_rows(
  present(itt_signed, "^t_verbal") %>% mutate(Arm = "Verbal", .after = Topic),
  present(itt_signed, "^t_money")  %>% mutate(Arm = "Monetary", .after = Topic)
) %>% arrange(Topic, Arm)
print(as.data.frame(tab_itt_signed))
write_latex_table(tab_itt_signed, "tab_itt_signed", caption = "ITT, signed change")
```

```{r benchmark-first-stage}
fs <- across_waves(analysis_data, y = "exp_topic_uptake_yn",
                   rhs = c("t_verbal", "t_money"))

cat("Behavioural first stage (Eq. 4.3):\n")
tab_fs <- bind_rows(
  present(fs, "^t_verbal") %>% mutate(Arm = "Verbal", .after = Topic),
  present(fs, "^t_money")  %>% mutate(Arm = "Monetary", .after = Topic)
) %>% arrange(Topic, Arm)
print(as.data.frame(tab_fs))
write_latex_table(tab_fs, "tab_first_stage", caption = "First stage on uptake")
```
```{r first-stage-effort}
# First stage on effort rather than on uptake.
fs_effort <- across_waves(analysis_data, y = "effort_count",
                          rhs = c("t_verbal", "t_money"))

cat("First stage on effort (count of topic-relevant visits):\n")
tab_fs_effort <- bind_rows(
  present(fs_effort, "^t_verbal") %>% mutate(Arm = "Verbal", .after = Topic),
  present(fs_effort, "^t_money")  %>% mutate(Arm = "Monetary", .after = Topic)
) %>% arrange(Topic, Arm)
print(as.data.frame(tab_fs_effort))
write_latex_table(tab_fs_effort, "tab_first_stage_effort",
                  caption = "First stage on effort")

# Distribution of effort by arm, alongside the mean reported above.
cat("\nEffort distribution by arm:\n")
dat_all <- bind_rows(analysis_data)
dat_all %>%
  group_by(Topic = WAVE_TOPICS[as.character(wave)], Arm = group_f) %>%
  summarise(n = n(),
            pct_any = round(100 * mean(effort_count > 0), 1),
            median_if_any = median(effort_count[effort_count > 0]),
            mean = round(mean(effort_count), 2),
            max = max(effort_count),
            .groups = "drop") %>%
  as.data.frame() %>% print()
```

# Part 4: Realization and the Level of Encountered OIEQ (Eq. 4.13)

> **H1a:** Randomized encouragement increases the probability that a
> participant realizes a topic-relevant online information environment whose
> quality can be characterized.

Realization is the binary outcome `realized`: at least one topic-relevant
visit to a domain carrying a quality score. It is defined for every
participant-wave, so H1a is estimated on the full wave sample.

The level of encountered quality is estimated afterwards. That outcome exists
only where `realized == 1`, so its sample is defined by a post-treatment
variable; the arm composition and the trimming bounds below quantify what
follows from that.

```{r h1a-realization}
realized <- across_waves(
  map(analysis_data, ~ mutate(.x, realized = as.integer(!is.na(q_primary)))),
  y = "realized", rhs = c("t_verbal", "t_money"))

cat("H1a: encouragement and realization of a characterizable environment\n")
tab_h1a_real <- bind_rows(
  present(realized, "^t_verbal") %>% mutate(Arm = "Verbal", .after = Topic),
  present(realized, "^t_money")  %>% mutate(Arm = "Monetary", .after = Topic)
) %>% arrange(Topic, Arm)
print(as.data.frame(tab_h1a_real))

write_latex_table(tab_h1a_real, "tab_h1a_realization",
                  caption = "H1a: encouragement and realization of a characterizable environment")
```

Realization requires topic-relevant activity and rating coverage, so the
effect is bounded above by the first stage on uptake reported in Part 3.

```{r h1a-realization-vs-uptake}
# Realization against uptake, same arms and samples. The gap is the share of
# topic-relevant activity that reached no rated domain.
bind_rows(
  present(fs, "^t_money")       %>% mutate(Outcome = "Uptake", .after = Topic),
  present(realized, "^t_money") %>% mutate(Outcome = "Realization", .after = Topic)
) %>% arrange(Topic, Outcome) %>% as.data.frame() %>% print()
```

## Level of encountered OIEQ

```{r qlevel-three-samples}
# Three columns: 1 to 2 is the change of sample, 2 to 3 the adjustment.
qlevel     <- across_waves(analysis_data, y = "q_primary",
                           rhs = c("t_verbal", "t_money"))
qlevel_cc  <- across_waves(cc_data, y = "q_primary",
                           rhs = c("t_verbal", "t_money"))
qlevel_adj <- across_waves(cc_data, y = "q_primary",
                           rhs = c("t_verbal", "t_money", COVARS))

tab_qlevel <- bind_rows(
  present(qlevel,     "^t_money") %>% mutate(Model = "1 Unadjusted, full", .after = Topic),
  present(qlevel_cc,  "^t_money") %>% mutate(Model = "2 Unadjusted, cc",   .after = Topic),
  present(qlevel_adj, "^t_money") %>% mutate(Model = "3 Adjusted",         .after = Topic)
) %>% arrange(Topic, Model)

# Columns 2 and 3 must rest on the same rows.
stopifnot(tab_qlevel %>% filter(Model != "1 Unadjusted, full") %>%
            group_by(Topic) %>% summarise(k = n_distinct(N), .groups = "drop") %>%
            pull(k) %>% (\(x) all(x == 1)))

cat("Level of encountered OIEQ, three estimation samples\n")
print(as.data.frame(tab_qlevel))

write_latex_table(tab_qlevel, "tab_q_level",
                  caption = "Level of encountered OIEQ, three estimation samples")
```

```{r qlevel-scored-by-arm}
# Arm composition of the participants who carry a quality score.
tab_scored_by_arm <- map_dfr(analysis_data, ~ .x %>%
          group_by(Arm = group_f) %>%
          summarise(N          = n(),
                    `n scored` = sum(!is.na(q_primary)),
                    `% scored` = round(100 * mean(!is.na(q_primary)), 1),
                    .groups    = "drop"),
        .id = "wave") %>%
  mutate(Topic = WAVE_TOPICS[str_remove(wave, "wave")], .before = 1) %>%
  select(-wave)

cat("Participants with a quality score, by arm:\n")
print(as.data.frame(tab_scored_by_arm))

write_latex_table(tab_scored_by_arm, "tab_q_level_scored_by_arm", digits = 1,
                  caption = "Participants with a constructible quality score, by arm")
```

```{r qlevel-lee-bounds}
# Trimming bounds under monotonicity (Lee, 2009), monetary versus control.
# The trim share is the excess selection rate of the treated arm; the bounds
# trim that share from the top and from the bottom of the treated outcome
# distribution.

lee_bounds <- function(d, outcome = "q_primary", treat = "t_money") {
  d <- d %>% filter(group_f != "verbal")
  y  <- d[[outcome]]
  tr <- d[[treat]] == 1
  s  <- !is.na(y)

  p1 <- mean(s[tr])
  p0 <- mean(s[!tr])
  if (p1 <= p0) return(NULL)          # monotonicity runs the other way here

  q   <- (p1 - p0) / p1               # excess share to be trimmed
  y1  <- sort(y[tr & s])
  y0  <- mean(y[!tr & s])
  k   <- floor(length(y1) * q)

  c(trim_share = q,
    lower = mean(head(y1, length(y1) - k)) - y0,   # drop the top q
    upper = mean(tail(y1, length(y1) - k)) - y0,   # drop the bottom q
    naive = mean(y1) - y0,
    n_treated_selected = length(y1))
}

set.seed(20260913)
tab_lee <- imap_dfr(analysis_data, function(d, nm) {
  point <- lee_bounds(d)
  if (is.null(point)) return(NULL)

  boot <- replicate(N_BOOT, {
    r <- lee_bounds(d[sample(nrow(d), replace = TRUE), ])
    if (is.null(r)) c(NA_real_, NA_real_) else r[c("lower", "upper")]
  })

  # Bound low/high are the trimming bounds themselves; Boot. low/high are the
  # bootstrap limits around them. They are kept apart so that the table does
  # not merge two different intervals into one column.
  tibble(Topic = WAVE_TOPICS[str_remove(nm, "wave")],
         `Trim share`   = round(point["trim_share"], 3),
         `Naive diff`   = round(point["naive"], 3),
         `Bound low`    = round(point["lower"], 3),
         `Bound high`   = round(point["upper"], 3),
         `Boot. low`    = round(quantile(boot[1, ], .025, na.rm = TRUE), 3),
         `Boot. high`   = round(quantile(boot[2, ], .975, na.rm = TRUE), 3),
         N              = point["n_treated_selected"])
})

tab_lee <- tab_lee %>%
  mutate(`N trimmed` = floor(N * (1 - `Trim share`)), .after = N)

cat("Level of encountered OIEQ under trimming bounds, monetary versus control:\n")
print(as.data.frame(tab_lee))

write_latex_table(tab_lee, "tab_q_level_lee_bounds",
                  caption = "Trimming bounds on the level of encountered OIEQ")

# Monotonicity requires the treated selection rate to be the larger one.
cat("\nSelection rates by arm (monotonicity requires monetary >= control):\n")
map_dfr(analysis_data, ~ .x %>%
          filter(group_f != "verbal") %>%
          group_by(Arm = group_f) %>%
          summarise(selected = round(mean(!is.na(q_primary)), 3), .groups = "drop"),
        .id = "wave") %>%
  pivot_wider(names_from = Arm, values_from = selected) %>%
  as.data.frame() %>% print()
```

# Part 5: H1b -- Effort and Encountered Quality (Eq. 4.14)

> **H1b:** Greater topic-relevant information-seeking effort is associated
> with higher encountered information quality.

Effort is not randomised, so the coefficient is an adjusted association.
The primary effort measure is the count of topic-relevant visits;
duration and distinct domains are supplementary.

```{r h1b}
h1b <- list(
  count    = "effort_count",
  duration = "topic_duration",
  domains  = "n_topic_domains"
) %>%
  imap_dfr(function(v, nm) {
    across_waves(analysis_data, y = "q_primary", rhs = c(v, COVARS)) %>%
      filter(term == v) %>%
      mutate(Measure = nm)
  })

tab_h1b <- present(h1b, ".", digits = 5) %>%
  mutate(Measure = h1b$Measure, .after = Topic) %>%
  arrange(Topic, Measure)

cat("H1b: effort and encountered quality\n")
print(as.data.frame(tab_h1b))
write_latex_table(tab_h1b, "tab_h1b_effort_quality", digits = 5,
                  caption = "H1b: effort and encountered quality")
```

# Part 6: H2 -- Quality and Attitude Change (Eq. 4.15)

> **H2:** Higher information quality encountered during the experimental
> period is associated with a greater magnitude of policy-attitude change.

Treatment assignment is included so that the coefficient is a conditional
association rather than a re-expression of the total treatment contrast.
Quality is not randomised; this is evidence about a pathway, not an
identified causal effect of quality.

```{r h2}
h2     <- across_waves(analysis_data, y = "y_abs",
                       rhs = c("q_primary", "t_verbal", "t_money"))
h2_cc  <- across_waves(cc_data, y = "y_abs",
                       rhs = c("q_primary", "t_verbal", "t_money"))
h2_adj <- across_waves(cc_data, y = "y_abs",
                       rhs = c("q_primary", "t_verbal", "t_money", COVARS))

tab_h2 <- bind_rows(
  present(h2,     "^q_primary") %>% mutate(Model = "1 Unadjusted, full", .after = Topic),
  present(h2_cc,  "^q_primary") %>% mutate(Model = "2 Unadjusted, cc",   .after = Topic),
  present(h2_adj, "^q_primary") %>% mutate(Model = "3 Adjusted",         .after = Topic)
) %>% arrange(Topic, Model)

stopifnot(tab_h2 %>% filter(Model != "1 Unadjusted, full") %>%
            group_by(Topic) %>% summarise(k = n_distinct(N), .groups = "drop") %>%
            pull(k) %>% (\(x) all(x == 1)))

cat("H2: encountered quality and attitude change\n")
print(as.data.frame(tab_h2))

write_latex_table(tab_h2, "tab_h2_quality_attitude",
                  caption = "H2: quality and attitude change")
```
No bounds are computed for H2. Lee bounds identify a treatment contrast on a selected outcome; H2 is an association between two quantities that both exist only for selected participants, and the trimming logic has no treatment contrast to apply. The selection is instead reported directly:among control participants the quality measure exists for 1.0 to 2.9 percent, so H2 describes a relationship within the encouraged.

# Part 7: H3a -- Habitual Quality Moderates the Quality Pathway (Eq. 4.16)

> **H3a:** The positive association between experimental-period quality and
> the magnitude of attitude change is stronger among participants with low
> habitual OIEQ.

With the low group as reference, its slope is `b1` and the high group's is
`b1 + b3`. H3a predicts `b1 > 0` and `b3 < 0`. The interaction carries the
inferential weight; subgroup estimates are reported for readability only.

```{r h3a}
h3a <- map_dfr(DIET_VARIANTS, function(v) {
  g <- paste0("hab_", v, "_level_group")
  across_waves(analysis_data, y = "y_abs",
               rhs = c(paste0("q_primary * ", g), "t_verbal", "t_money", COVARS)) %>%
    filter(str_detect(term, "^q_primary")) %>%
    mutate(Variant = v,
           Term = if_else(str_detect(term, ":"), "Interaction (b3)", "Low group (b1)"))
})

tab_h3a <- present(h3a, ".") %>%
  mutate(Variant = h3a$Variant, Term = h3a$Term, .after = Topic) %>%
  arrange(Topic, Variant, desc(Term))

cat("H3a: quality x habitual-quality interaction\n")
print(as.data.frame(tab_h3a))
write_latex_table(tab_h3a, "tab_h3a_quality_moderation",
                  caption = "H3a: quality-attitude link by habitual quality")
```

```{r h3a-subgroups}
# Subgroup estimates, read together with the interaction term above.
h3a_sub <- map_dfr(DIET_VARIANTS, function(v) {
  g <- paste0("hab_", v, "_level_group")
  map_dfr(c("low", "high"), function(grp) {
    sub <- map(analysis_data, ~ filter(.x, .data[[g]] == grp))
    across_waves(sub, y = "y_abs",
                 rhs = c("q_primary", "t_verbal", "t_money", COVARS)) %>%
      filter(term == "q_primary") %>%
      mutate(Variant = v, Group = grp)
  })
})

tab_h3a_sub <- present(h3a_sub, "^q_primary$") %>%
  mutate(Variant = h3a_sub$Variant, Group = h3a_sub$Group, .after = Topic) %>%
  arrange(Topic, Variant, desc(Group))

print(as.data.frame(tab_h3a_sub))
write_latex_table(tab_h3a_sub, "tab_h3a_subgroups",
                  caption = "H3a: subgroup estimates (read with the interaction)")
```

# Part 8: H4a -- Habitual Quality Moderates the Treatment Effect (Eq. 4.17)

> **H4a:** The effect of randomized encouragement on the magnitude of
> attitude change is stronger among participants with low habitual OIEQ.

Unlike H3a this uses a randomised regressor, so the subgroup contrast does
not rest on an assumption about quality selection. The moderator is
pre-treatment, so the interaction is well defined.

```{r h4a}
h4a <- map_dfr(DIET_VARIANTS, function(v) {
  g <- paste0("hab_", v, "_level_group")
  across_waves(analysis_data, y = "y_abs",
               rhs = c("t_verbal", "t_money", g,
                       paste0("t_verbal:", g), paste0("t_money:", g),
                       COVARS)) %>%
    filter(str_detect(term, "^t_verbal|^t_money")) %>%
    mutate(Variant = v,
           Arm = if_else(str_detect(term, "verbal"), "Verbal", "Monetary"),
           Term = if_else(str_detect(term, ":"), "Interaction", "Low group"))
})

tab_h4a <- present(h4a, ".") %>%
  mutate(Variant = h4a$Variant, Arm = h4a$Arm, Term = h4a$Term, .after = Topic) %>%
  arrange(Topic, Variant, Arm, desc(Term))

cat("H4a: treatment x habitual-quality interaction\n")
print(as.data.frame(tab_h4a))
write_latex_table(tab_h4a, "tab_h4a_treatment_moderation",
                  caption = "H4a: treatment effect by habitual quality")
```


```{r h4a-common-sample}
# The three diet definitions do not cover the same participants, so a contrast
# between them confounds the definition with the composition of the sample.
# This block holds the sample fixed at the rows for which all three exist.
HAB_GROUPS <- paste0("hab_", DIET_VARIANTS, "_level_group")

common_data <- map(cc_data, ~ filter(.x, if_all(all_of(HAB_GROUPS), ~ !is.na(.x))))

h4a_common <- map_dfr(DIET_VARIANTS, function(v) {
  g <- paste0("hab_", v, "_level_group")
  across_waves(common_data, y = "y_abs",
               rhs = c("t_verbal", "t_money", g,
                       paste0("t_verbal:", g), paste0("t_money:", g),
                       COVARS)) %>%
    filter(str_detect(term, "^t_money:")) %>%
    mutate(Variant = v)
})

# Within a wave the common sample is identical across definitions, so any
# remaining difference is the definition alone.
stopifnot(h4a_common %>% group_by(topic) %>%
            summarise(k = n_distinct(n), .groups = "drop") %>%
            pull(k) %>% (\(x) all(x == 1)))

tab_h4a_common <- h4a %>%
  filter(Term == "Interaction", Arm == "Monetary") %>%
  transmute(Topic = topic, Variant,
            `Own sample` = round(estimate, 3), `p (own)` = round(p.value, 3),
            `N (own)` = n) %>%
  left_join(h4a_common %>%
              transmute(Topic = topic, Variant,
                        `Common sample` = round(estimate, 3),
                        `p (common)` = round(p.value, 3), `N (common)` = n),
            by = c("Topic", "Variant")) %>%
  arrange(Topic, Variant)

cat("H4a monetary interaction: own versus common estimation sample\n")
print(as.data.frame(tab_h4a_common))

write_latex_table(tab_h4a_common, "tab_h4a_common_sample",
                  caption = "H4a interaction on a sample common to all three diet definitions")
```



```{r h4a-continuous}
# Same interaction with the continuous moderator in place of the split,
# standardized within wave. The coefficient is the change in the treatment
# effect per SD of habitual quality.

h4a_cont <- map_dfr(DIET_VARIANTS, function(v) {
  z <- paste0("hab_", v, "_dw_pc1")
  sub <- map(cc_data, ~ mutate(.x, hab_z = as.numeric(scale(.data[[z]]))))
  across_waves(sub, y = "y_abs",
               rhs = c("t_verbal", "t_money", "hab_z",
                       "t_verbal:hab_z", "t_money:hab_z", COVARS)) %>%
    filter(str_detect(term, "^t_money")) %>%
    mutate(Variant = v,
           Term = if_else(str_detect(term, ":"), "Interaction", "Main effect"))
})

tab_h4a_cont <- h4a %>%
  filter(Term == "Interaction", Arm == "Monetary") %>%
  transmute(Topic = topic, Variant,
            `Split` = round(estimate, 3), `p (split)` = round(p.value, 3),
            `N (split)` = n) %>%
  left_join(h4a_cont %>%
              filter(Term == "Interaction") %>%
              transmute(Topic = topic, Variant,
                        `Continuous (per SD)` = round(estimate, 3),
                        `p (cont.)` = round(p.value, 3), `N (cont.)` = n),
            by = c("Topic", "Variant")) %>%
  arrange(Topic, Variant)

cat("H4a monetary interaction: median split versus continuous moderator\n")
print(as.data.frame(tab_h4a_cont))

write_latex_table(tab_h4a_cont, "tab_h4a_continuous",
                  caption = "H4a interaction under a continuous habitual-quality moderator")
```
```{r h4a-sign-test}
# Sign test across all interaction cells.
h4a %>%
  filter(Term == "Interaction") %>%
  summarise(n = n(), n_negative = sum(estimate < 0),
            p = binom.test(sum(estimate < 0), n())$p.value) %>%
  as.data.frame() %>% print()
```

# Part 9: H4b -- Subgroup LATE of Uptake (Eq. 4.18, 4.19)

> **H4b:** The effect of treatment-induced information seeking on attitude
> change is stronger in the low habitual-quality subgroup.

Uptake is instrumented with encouragement. A subgroup LATE refers to that
subgroup's compliers, so the two are not automatically comparable; the
interaction model is reported first for that reason.

```{r h4b-full-sample}
late <- across_waves(analysis_data, y = "y_abs",
                     rhs = c("exp_topic_uptake_yn", COVARS),
                     instruments = c("t_verbal", "t_money", COVARS))

tab_late <- late %>%
  filter(term == "exp_topic_uptake_yn") %>%
  transmute(Topic = topic, Estimate = round(estimate, 3), SE = round(std.error, 3),
            p = round(p.value, 3), Sig = stars(p.value), N = n,
            `First-stage F` = round(first_stage_F, 2))

cat("Uptake LATE, full sample:\n")
print(as.data.frame(tab_late))
write_latex_table(tab_late, "tab_h4b_late_full", caption = "Uptake LATE, full sample")
```

```{r h4b-interaction}
# The instrument is interacted too, so the interaction term is itself
# instrumented rather than only the main effect.
h4b_int <- map_dfr(DIET_VARIANTS, function(v) {
  g <- paste0("hab_", v, "_level_group")
  across_waves(analysis_data, y = "y_abs",
               rhs = c(paste0("exp_topic_uptake_yn * ", g), COVARS),
               instruments = c(paste0("t_verbal * ", g), paste0("t_money * ", g), COVARS)) %>%
    filter(str_detect(term, "^exp_topic_uptake_yn")) %>%
    mutate(Variant = v,
           Term = if_else(str_detect(term, ":"), "Interaction", "Low group"))
})

tab_h4b_int <- present(h4b_int, ".", fit = FALSE) %>%
  mutate(Variant = h4b_int$Variant, Term = h4b_int$Term, .after = Topic) %>%
  mutate(`First-stage F` = round(h4b_int$first_stage_F, 2)) %>%
  arrange(Topic, Variant, desc(Term))

cat("H4b: uptake LATE x habitual-quality interaction\n")
print(as.data.frame(tab_h4b_int))
write_latex_table(tab_h4b_int, "tab_h4b_late_interaction",
                  caption = "H4b: uptake LATE by habitual quality")
```

```{r h4b-subgroups}
h4b_sub <- map_dfr(DIET_VARIANTS, function(v) {
  g <- paste0("hab_", v, "_level_group")
  map_dfr(c("low", "high"), function(grp) {
    sub <- map(analysis_data, ~ filter(.x, .data[[g]] == grp))
    # A subgroup split can leave an instrument without variation.
    ok <- map_lgl(sub, ~ n_distinct(.x$t_money, na.rm = TRUE) > 1 &&
                        n_distinct(.x$exp_topic_uptake_yn, na.rm = TRUE) > 1)
    if (!all(ok)) cat("  skipped (degenerate instrument):", v, grp,
                      names(sub)[!ok], "\n")
    across_waves(sub[ok], y = "y_abs",
                 rhs = c("exp_topic_uptake_yn", COVARS),
                 instruments = c("t_verbal", "t_money", COVARS)) %>%
      filter(term == "exp_topic_uptake_yn") %>%
      mutate(Variant = v, Group = grp)
  })
})

tab_h4b_sub <- present(h4b_sub, "^exp_topic_uptake_yn$", fit = FALSE) %>%
  mutate(Variant = h4b_sub$Variant, Group = h4b_sub$Group, .after = Topic) %>%
  mutate(`First-stage F` = round(h4b_sub$first_stage_F, 2)) %>%
  arrange(Topic, Variant, desc(Group))

print(as.data.frame(tab_h4b_sub))
write_latex_table(tab_h4b_sub, "tab_h4b_subgroups",
                  caption = "H4b: subgroup LATEs (read with the interaction)")
```
```{r h4b-continuous}
# Continuous moderator on the LATE. The moderator enters as a control, inside
# the endogenous interaction, and in the instrument set, so that both
# endogenous terms are instrumented.

h4b_cont <- map_dfr(DIET_VARIANTS, function(v) {
  z   <- paste0("hab_", v, "_dw_pc1")
  sub <- map(cc_data, ~ mutate(.x, hab_z = as.numeric(scale(.data[[z]]))))
  across_waves(sub, y = "y_abs",
               rhs = c("exp_topic_uptake_yn", "exp_topic_uptake_yn:hab_z",
                       "hab_z", COVARS),
               instruments = c("t_verbal", "t_money", "hab_z",
                               "t_verbal:hab_z", "t_money:hab_z", COVARS)) %>%
    filter(str_detect(term, "^exp_topic_uptake_yn")) %>%
    mutate(Variant = v,
           Term = if_else(str_detect(term, ":"), "Interaction", "Main effect"))
})

tab_h4b_cont <- h4b_int %>%
  filter(Term == "Interaction") %>%
  transmute(Topic = topic, Variant,
            Split = round(estimate, 3), `p (split)` = round(p.value, 3),
            `F (split)` = round(first_stage_F, 2), `N (split)` = n) %>%
  left_join(h4b_cont %>%
              filter(Term == "Interaction") %>%
              transmute(Topic = topic, Variant,
                        `Continuous (per SD)` = round(estimate, 3),
                        `p (cont.)` = round(p.value, 3),
                        `F (cont.)` = round(first_stage_F, 2), `N (cont.)` = n),
            by = c("Topic", "Variant")) %>%
  arrange(Topic, Variant)

cat("H4b LATE interaction: median split versus continuous moderator\n")
print(as.data.frame(tab_h4b_cont))

write_latex_table(tab_h4b_cont, "tab_h4b_continuous",
                  caption = "H4b LATE interaction under a continuous habitual-quality moderator")
```
```{r h4b-reduced-form}
# Reduced form of the same interaction: the outcome on the instruments,
# without a first stage. Compared against the 2SLS estimates above.
map_dfr(DIET_VARIANTS, function(v) {
  z   <- paste0("hab_", v, "_dw_pc1")
  sub <- map(cc_data, ~ mutate(.x, hab_z = as.numeric(scale(.data[[z]]))))
  across_waves(sub, y = "y_abs",
               rhs = c("t_verbal", "t_money", "hab_z",
                       "t_verbal:hab_z", "t_money:hab_z", COVARS)) %>%
    filter(term == "t_money:hab_z") %>%
    mutate(Variant = v)
}) %>%
  transmute(Topic = topic, Variant,
            `Reduced form` = round(estimate, 3), p_rf = round(p.value, 3)) %>%
  left_join(tab_h4b_cont %>% select(Topic, Variant, `Continuous (per SD)`, `p (cont.)`),
            by = c("Topic", "Variant")) %>%
  arrange(Topic, Variant) %>%
  as.data.frame() %>% print()
```

# Part 10: H3b -- Conditional Indirect Effects (Eq. 4.20--4.22)

> **H3b:** The indirect effect of encouragement on attitude change through
> experimental-period quality is stronger among participants with low
> habitual OIEQ.

Product of the treatment-quality path `a` from Equation (4.4) and the
group-specific quality-attitude slopes from Equation (4.7). Confidence
intervals by participant bootstrap within wave. Randomisation does not
remove mediator-outcome confounding, so these are assumption-dependent.

```{r h3b}
indirect_once <- function(d, g) {
  a_fit <- try(lm(as.formula(paste("q_primary ~ t_verbal + t_money +",
                                   paste(COVARS, collapse = " + "))), d), silent = TRUE)
  b_fit <- try(lm(as.formula(paste("y_abs ~ q_primary *", g,
                                   "+ t_verbal + t_money +",
                                   paste(COVARS, collapse = " + "))), d), silent = TRUE)
  if (inherits(a_fit, "try-error") || inherits(b_fit, "try-error")) return(NULL)

  a  <- coef(a_fit)["t_money"]
  b1 <- coef(b_fit)["q_primary"]
  b3 <- coef(b_fit)[str_subset(names(coef(b_fit)), "^q_primary:")]
  if (length(b3) != 1 || any(is.na(c(a, b1, b3)))) return(NULL)

  c(ie_low = unname(a * b1), ie_high = unname(a * (b1 + b3)),
    diff = unname(a * b1 - a * (b1 + b3)))
}

h3b <- map_dfr(DIET_VARIANTS, function(v) {
  g <- paste0("hab_", v, "_level_group")
  imap_dfr(analysis_data, function(d, nm) {
    point <- indirect_once(d, g)
    if (is.null(point)) return(NULL)

    boot <- replicate(N_BOOT, {
      idx <- sample(nrow(d), replace = TRUE)
      r <- indirect_once(d[idx, ], g)
      if (is.null(r)) rep(NA_real_, 3) else r
    })

    tibble(wave = as.integer(str_remove(nm, "wave")), Variant = v,
           Quantity = names(point), Estimate = point,
           CI_low  = apply(boot, 1, quantile, .025, na.rm = TRUE),
           CI_high = apply(boot, 1, quantile, .975, na.rm = TRUE),
           N = nrow(filter(d, !is.na(q_primary))))
  })
})

tab_h3b <- h3b %>%
  transmute(Topic = WAVE_TOPICS[as.character(wave)], Variant,
            Quantity = c(ie_low = "IE low", ie_high = "IE high",
                         diff = "Difference")[Quantity],
            Estimate = round(Estimate, 3),
            CI_low = round(CI_low, 3), CI_high = round(CI_high, 3), N) %>%
  arrange(Topic, Variant, Quantity)

cat("H3b: conditional indirect effects\n")
print(as.data.frame(tab_h3b))
write_latex_table(tab_h3b, "tab_h3b_indirect_effects",
                  caption = "H3b: conditional indirect effects, bootstrap CIs")
```

```{r h3b-sensitivity}



# summary.medsens prints three lines of the form "... at which ACME = 0: <value>",
# in the order rho, R^2* product, R^2~ product. They are selected by position,
# because the notation of the R^2 terms differs between package versions.
sens_summary_value <- function(sens, which = 1L) {
  if (is.null(sens)) return(NA_real_)
  txt <- tryCatch(capture.output(summary(sens)), error = function(e) character(0))
  ln  <- grep("at which ACME", txt, value = TRUE)
  if (length(ln) < which) return(NA_real_)
  v <- regmatches(ln[which], regexpr("-?[0-9]*\\.?[0-9]+\\s*$", ln[which]))
  if (length(v) == 0) NA_real_ else as.numeric(trimws(v))
}

sens_rho <- imap_dfr(analysis_data, function(d, nm) {
  d <- d %>% filter(!is.na(q_primary), !is.na(y_abs), group_f != "verbal") %>%
    mutate(treat = as.integer(group_f == "monetary"))
  if (nrow(d) < 20 || n_distinct(d$treat) < 2) return(NULL)

  f_m <- as.formula(paste("q_primary ~ treat +", paste(COVARS, collapse = " + ")))
  f_y <- as.formula(paste("y_abs ~ treat + q_primary +", paste(COVARS, collapse = " + ")))

  m_fit <- do.call(lm, list(formula = f_m, data = d))
  y_fit <- do.call(lm, list(formula = f_y, data = d))

  med <- tryCatch(
    mediation::mediate(m_fit, y_fit, treat = "treat", mediator = "q_primary",
                       sims = 1000, boot = FALSE),
    error = function(e) NULL)
  if (is.null(med)) return(NULL)

  sens <- tryCatch(mediation::medsens(med, rho.by = 0.05, effect.type = "indirect"),
                   error = function(e) NULL)

  tibble(
    wave     = as.integer(str_remove(nm, "wave")),
    N        = nrow(d),
    ACME     = as.numeric(med$d1)[1],
    ACME_p   = as.numeric(med$d1.p)[1],
    ADE      = as.numeric(med$z1)[1],
    ADE_p    = as.numeric(med$z1.p)[1],
    Prop_med = as.numeric(med$n1)[1],
    rho_zero = sens_summary_value(sens, 1),
    R2_zero  = sens_summary_value(sens, 2)
  )
})

# R^2_M* x R^2_Y* equals rho^2 by construction. A mismatch means the value was
# read from the wrong line; an NA means the pattern did not match at all.
stopifnot(!any(is.na(sens_rho$rho_zero)), !any(is.na(sens_rho$R2_zero)))
stopifnot(all(abs(sens_rho$R2_zero - sens_rho$rho_zero^2) < 0.01))


tab_h3b_sens <- sens_rho %>%
  transmute(Topic = WAVE_TOPICS[as.character(wave)],
            N,
            ACME = round(ACME, 3), p = round(ACME_p, 3),
            ADE = round(ADE, 3),
            `Prop. mediated` = round(Prop_med, 3),
            `Rho at ACME = 0` = round(rho_zero, 2),
            `R2 product` = round(R2_zero, 3))

cat("Unmoderated mediation and sensitivity to unobserved confounding:\n")
print(as.data.frame(tab_h3b_sens))
write_latex_table(tab_h3b_sens, "tab_h3b_sensitivity",
                  caption = "Mediation sensitivity: rho at which the ACME is zero")
```

```{r h3b-sensitivity-plot}
# medsens region, one panel per wave.
par(mfrow = c(1, 3))
walk(names(analysis_data), function(nm) {
  d <- analysis_data[[nm]] %>%
    filter(!is.na(q_primary), !is.na(y_abs), group_f != "verbal") %>%
    mutate(treat = as.integer(group_f == "monetary"))
  if (nrow(d) < 20) return(invisible(NULL))

  f_m <- as.formula(paste("q_primary ~ treat +", paste(COVARS, collapse = " + ")))
  f_y <- as.formula(paste("y_abs ~ treat + q_primary +", paste(COVARS, collapse = " + ")))
  m_fit <- do.call(lm, list(formula = f_m, data = d))
  y_fit <- do.call(lm, list(formula = f_y, data = d))

  med <- tryCatch(mediation::mediate(m_fit, y_fit, treat = "treat",
                                     mediator = "q_primary", sims = 500),
                  error = function(e) NULL)
  if (is.null(med)) return(invisible(NULL))
  sens <- tryCatch(mediation::medsens(med, rho.by = 0.1), error = function(e) NULL)
  if (!is.null(sens)) plot(sens, main = WAVE_TOPICS[[str_remove(nm, "wave")]])
})
par(mfrow = c(1, 1))

```


# Part 11: Sensitivity Analyses

Three axes, all prespecified: quality weighting, habitual-diet definition,
and need for cognition. The diet definition is already varied throughout
Parts 7 to 10, so only the other two are added here.

```{r sensitivity-weighting}
sens_w <- c(duration = "q_primary", unweighted = "exp_q_unw", log = "exp_q_log") %>%
  imap_dfr(function(v, nm) {
    across_waves(analysis_data, y = "y_abs",
                 rhs = c(v, "t_verbal", "t_money", COVARS)) %>%
      filter(term == v) %>% mutate(Weighting = nm)
  })

tab_sens_w <- sens_w %>%
  transmute(Topic = topic, Weighting, Estimate = round(estimate, 3),
            p = round(p.value, 3), Sig = stars(p.value), N = n) %>%
  arrange(Topic, Weighting)

cat("H2 under the three weightings:\n")
print(as.data.frame(tab_sens_w))
write_latex_table(tab_sens_w, "tab_sens_weighting",
                  caption = "H2 under three quality weightings")
```

```{r sensitivity-category-set}
sens_c <- c(primary = "q_primary", news_only = "exp_q_dur_news",
            incl_search = "exp_q_dur_all") %>%
  imap_dfr(function(v, nm) {
    across_waves(analysis_data, y = "y_abs",
                 rhs = c(v, "t_verbal", "t_money", COVARS)) %>%
      filter(term == v) %>% mutate(`Category set` = nm)
  })

tab_sens_c <- sens_c %>%
  transmute(Topic = topic, `Category set`, Estimate = round(estimate, 3),
            p = round(p.value, 3), Sig = stars(p.value), N = n) %>%
  arrange(Topic, `Category set`)

print(as.data.frame(tab_sens_c))
write_latex_table(tab_sens_c, "tab_sens_category_set",
                  caption = "H2 under three category sets")
```

```{r sensitivity-nfc}
# Reading rule fixed in advance: if the interaction survives, the moderator
# is not merely a proxy for cognitive engagement; if not, that cannot be
# ruled out, and the adjustment is partial given a reliability of .61.
# Same specification as H4a, plus nfc. Anything else would confound the
# adjustment with a change in the model.
sens_nfc <- map_dfr(DIET_VARIANTS, function(v) {
  g <- paste0("hab_", v, "_level_group")
  across_waves(analysis_data, y = "y_abs",
               rhs = c("t_verbal", "t_money", g,
                       paste0("t_verbal:", g), paste0("t_money:", g),
                       COVARS, "nfc")) %>%
    filter(str_detect(term, "^t_verbal|^t_money")) %>%
    mutate(Variant = v,
           Arm = if_else(str_detect(term, "verbal"), "Verbal", "Monetary"),
           Term = if_else(str_detect(term, ":"), "Interaction", "Low group"))
})

# Side by side with H4a, so the reader sees what the adjustment does rather
# than two tables that have to be compared by hand.
tab_sens_nfc <- h4a %>%
  transmute(topic, Variant, Arm, Term, est_h4a = estimate, p_h4a = p.value, n_h4a = n) %>%
  left_join(sens_nfc %>%
              transmute(topic, Variant, Arm, Term,
                        est_nfc = estimate, p_nfc = p.value, n_nfc = n),
            by = c("topic", "Variant", "Arm", "Term")) %>%
  filter(Term == "Interaction", Arm == "Monetary") %>%
  transmute(Topic = topic, Variant,
            `Without NFC` = round(est_h4a, 3), `p (without)` = round(p_h4a, 3),
            `N (without)` = n_h4a,
            `With NFC` = round(est_nfc, 3), `p (with)` = round(p_nfc, 3),
            `N (with)` = n_nfc) %>%
  arrange(Topic, Variant)

cat("H4a monetary interaction, with and without need for cognition:\n")
print(as.data.frame(tab_sens_nfc))
write_latex_table(tab_sens_nfc, "tab_sens_nfc",
                  caption = "H4a interaction adjusted for need for cognition")

# The sample shrinks because NFC is missing for 107 participants, so part of
# any change is compositional rather than due to the adjustment. Refitting
# H4a on the NFC-complete sample separates the two.
sens_nfc_same_n <- map_dfr(DIET_VARIANTS, function(v) {
  g <- paste0("hab_", v, "_level_group")
  sub <- map(analysis_data, ~ filter(.x, !is.na(nfc)))
  across_waves(sub, y = "y_abs",
               rhs = c("t_verbal", "t_money", g,
                       paste0("t_verbal:", g), paste0("t_money:", g),
                       COVARS)) %>%
    filter(str_detect(term, "^t_money:")) %>%
    mutate(Variant = v)
})

cat("\nH4a on the NFC-complete sample, without the adjustment:\n")
sens_nfc_same_n %>%
  transmute(Topic = topic, Variant, Estimate = round(estimate, 3),
            p = round(p.value, 3), N = n) %>%
  arrange(Topic, Variant) %>%
  as.data.frame() %>% print()
```
# Part 12: Knowledge Outcome


```{r knowledge-itt}
cat("ITT on knowledge change:\n")
kno_itt <- across_waves(analysis_data, y = "kno_signed",
                        rhs = c("t_verbal", "t_money"))

tab_kno_itt <- bind_rows(
  present(kno_itt, "^t_verbal") %>% mutate(Arm = "Verbal", .after = Topic),
  present(kno_itt, "^t_money")  %>% mutate(Arm = "Monetary", .after = Topic)
) %>% arrange(Topic, Arm)
print(as.data.frame(tab_kno_itt))
write_latex_table(tab_kno_itt, "tab_knowledge_itt", caption = "ITT on knowledge change")

# ANCOVA: post-test conditional on baseline, the prespecified robustness
# check. It is more efficient than the difference score when the pre-post
# correlation is below one, which it is here.
cat("\nANCOVA: post-test knowledge conditional on baseline:\n")
kno_ancova <- across_waves(analysis_data, y = "kno_post",
                           rhs = c("t_verbal", "t_money", "kno_pre", COVARS))

tab_kno_ancova <- bind_rows(
  present(kno_ancova, "^t_verbal") %>% mutate(Arm = "Verbal", .after = Topic),
  present(kno_ancova, "^t_money")  %>% mutate(Arm = "Monetary", .after = Topic)
) %>% arrange(Topic, Arm)
print(as.data.frame(tab_kno_ancova))
write_latex_table(tab_kno_ancova, "tab_knowledge_ancova",
                  caption = "Knowledge: ANCOVA robustness check")
```
```{r knowledge-quality}
cat("Encountered quality and knowledge change:\n")
kno_q <- across_waves(analysis_data, y = "kno_signed",
                      rhs = c("q_primary", "t_verbal", "t_money", COVARS))

tab_kno_q <- present(kno_q, "^q_primary$")
print(as.data.frame(tab_kno_q))
write_latex_table(tab_kno_q, "tab_knowledge_quality",
                  caption = "Quality and knowledge change")
```
```{r knowledge-late}
cat("Uptake LATE on knowledge change:\n")
kno_late <- across_waves(analysis_data, y = "kno_signed",
                         rhs = c("exp_topic_uptake_yn", COVARS),
                         instruments = c("t_verbal", "t_money", COVARS))

tab_kno_late <- kno_late %>%
  filter(term == "exp_topic_uptake_yn") %>%
  transmute(Topic = topic, Estimate = round(estimate, 3), SE = round(std.error, 3),
            p = round(p.value, 3), Sig = stars(p.value), N = n,
            `First-stage F` = round(first_stage_F, 2))
print(as.data.frame(tab_kno_late))
write_latex_table(tab_kno_late, "tab_knowledge_late",
                  caption = "Uptake LATE on knowledge change")
```
```{r knowledge-moderation}
# Knowledge analogue of H4b, for the same three diet definitions.
kno_mod <- map_dfr(DIET_VARIANTS, function(v) {
  g <- paste0("hab_", v, "_level_group")
  across_waves(analysis_data, y = "kno_signed",
               rhs = c(paste0("exp_topic_uptake_yn * ", g), COVARS),
               instruments = c(paste0("t_verbal * ", g),
                               paste0("t_money * ", g), COVARS)) %>%
    filter(str_detect(term, "^exp_topic_uptake_yn")) %>%
    mutate(Variant = v,
           Term = if_else(str_detect(term, ":"), "Interaction", "Low group"))
})

tab_kno_mod <- present(kno_mod, ".", fit = FALSE) %>%
  mutate(Variant = kno_mod$Variant, Term = kno_mod$Term, .after = Topic) %>%
  mutate(`First-stage F` = round(kno_mod$first_stage_F, 2)) %>%
  arrange(Topic, Variant, desc(Term))

cat("Knowledge LATE by habitual-quality group:\n")
print(as.data.frame(tab_kno_mod))
write_latex_table(tab_kno_mod, "tab_knowledge_moderation",
                  caption = "Knowledge LATE by habitual quality")
```

# Part 13: Detection Limits

Minimum detectable effect at 80 per cent power and a two-sided level of .05,
and Type S and Type M error at assumed true effects (Gelman & Carlin, 2014).
Nothing is re-estimated; the standard errors come from the models above.
```{r detection-limits}
mde <- function(se, power = .80, alpha = .05) {
  (qnorm(1 - alpha / 2) + qnorm(power)) * se
}

design_analysis <- function(true_effect, se, alpha = .05, n_sim = 2e5) {
  z     <- qnorm(1 - alpha / 2)
  power <- (1 - pnorm(z - true_effect / se)) + pnorm(-z - true_effect / se)
  draws <- rnorm(n_sim, true_effect, se)
  sig   <- abs(draws) > z * se
  c(power        = power,
    type_s       = pnorm(-z - true_effect / se) / power,
    exaggeration = mean(abs(draws[sig])) / abs(true_effect))
}

focal <- bind_rows(
  itt_abs    %>% filter(term == "t_money")   %>% mutate(Model = "ITT, absolute change"),
  realized   %>% filter(term == "t_money")   %>% mutate(Model = "H1a, realization"),
  qlevel_adj %>% filter(term == "t_money")   %>% mutate(Model = "Level of encountered OIEQ"),
  h2_adj     %>% filter(term == "q_primary") %>% mutate(Model = "H2, quality on attitude"),
  late       %>% filter(term == "exp_topic_uptake_yn") %>% mutate(Model = "LATE, uptake"),
  h4a        %>% filter(Term == "Interaction", Arm == "Monetary") %>%
              mutate(Model = paste0("H4a interaction (", DIET_SHORT[Variant], ")"))
) %>%
  transmute(Model, Topic = topic,
            Estimate   = round(estimate, 3),
            SE         = round(std.error, 3),
            MDE        = round(mde(std.error), 3),
            `Est./MDE` = round(abs(estimate) / mde(std.error), 2),
            N = n)

cat("Minimum detectable effect at 80% power, alpha = .05:\n")
print(as.data.frame(focal))

write_latex_table(focal, "tab_detection_limits",
                  caption = "Minimum detectable effects")


# The quality MDE expressed in within-wave SDs of the quality measure.
cat("\nMDE for the level of encountered OIEQ, in within-wave SDs:\n")
map_dfr(analysis_data, ~ tibble(sd_q = sd(.x$q_primary, na.rm = TRUE)), .id = "wave") %>%
  mutate(wave = as.integer(str_remove(wave, "wave"))) %>%
  left_join(qlevel_adj %>% filter(term == "t_money") %>% select(wave, std.error),
            by = "wave") %>%
  transmute(Topic       = WAVE_TOPICS[as.character(wave)],
            SD          = round(sd_q, 3),
            MDE         = round(mde(std.error), 3),
            `MDE in SD` = round(mde(std.error) / sd_q, 2)) %>%
  as.data.frame() %>% print()

# Design analysis at assumed true effects. SEs are taken from the fitted
# models rather than entered manually.
set.seed(20260913)
se_h4a  <- h4a %>% filter(Term == "Interaction", Arm == "Monetary",
                          Variant == "news", wave == 1) %>% pull(std.error)
se_late <- late %>% filter(term == "exp_topic_uptake_yn", wave == 1) %>% pull(std.error)

tab_design <- tibble(Model = c(rep("H4a interaction, news", 3), rep("LATE, child support", 3)),
                     SE    = c(rep(se_h4a, 3), rep(se_late, 3)),
                     `True effect` = rep(c(0.20, 0.30, 0.40), 2)) %>%
  mutate(res = map2(`True effect`, SE, design_analysis),
         Power          = round(map_dbl(res, "power"), 2),
         `Type S`       = round(100 * map_dbl(res, "type_s"), 1),
         Exaggeration   = round(map_dbl(res, "exaggeration"), 1)) %>%
  select(Model, `True effect`, SE, Power, `Type S`, Exaggeration) %>%
  mutate(SE = round(SE, 3))

cat("\nDesign analysis at plausible true effect sizes:\n")
print(as.data.frame(tab_design))

write_latex_table(tab_design, "tab_design_analysis", digits = 2,
                  caption = "Type S and Type M errors at plausible effect sizes")
```


# Part 14: Hypothesis Summary

Index of hypotheses and their principal table, plus a listing of the LaTeX
fragments written by this script.

```{r summary-table}
summary_tab <- tribble(
  ~Hypothesis, ~Question, ~Key_table,
  "H1a", "Encouragement raises the probability of realizing a characterizable environment", "tab_h1a_realization",
  "H1b", "More effort, higher encountered quality",            "tab_h1b_effort_quality",
  "H2",  "Higher quality, more attitude change",               "tab_h2_quality_attitude",
  "H3a", "Quality-attitude link stronger at low habitual quality", "tab_h3a_quality_moderation",
  "H3b", "Indirect effect stronger at low habitual quality",   "tab_h3b_indirect_effects",
  "H4a", "Treatment effect stronger at low habitual quality",  "tab_h4a_treatment_moderation",
  "H4b", "Uptake LATE stronger at low habitual quality",       "tab_h4b_late_interaction"
)

print(as.data.frame(summary_tab))
write_csv(summary_tab, file.path(table_dir, "hypothesis_index.csv"))


print(list.files(table_dir, pattern = "\\.tex$"))
```


