---
title: "Descriptives, Coverage, and Group Composition"
author: "Master's Thesis -- Media Quality / Media Diet"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = FALSE, message = TRUE,
                      fig.width = 10, fig.height = 5)
```

# Overview

Descriptive layer over the analysis dataset built by `03a`. Estimation happens
in `03b`; nothing here tests a hypothesis.

| Part | Content |
|---|---|
| 1 | Setup, constants, helpers |
| 2 | Descriptive statistics of the analysis variables |
| 3 | Coverage by measure and wave, and the quality-coverage triage |
| 4 | Randomization balance, joint test, and covariate missingness by arm |
| 5 | Arm sizes, subgroup sizes, and their cross-tabulation |
| 6 | Distributions of the outcome, the quality measures, effort, and the habitual diet |
| 7 | Habitual quality against political position and vote intention |
| 8 | Listing of the files written |

## Outputs

| File | Content |
|---|---|
| `tab_descriptives` | Analysis variables: mean, SD, min, max, median |
| `tab_coverage` | Non-missing counts by measure and wave |
| `tab_triage` | Three-way quality-coverage triage |
| `tab_balance` | Covariate means by arm and wave, with per-variable p-values |
| `tab_missingness_by_arm` | Missingness of prior engagement by arm |
| `tab_composition_arms` | Arm sizes by wave |
| `tab_composition_arm_by_diet` | Arm by habitual-quality cell sizes |
| `fig_coverage_triage` | Where the quality measure loses the sample |
| `fig_composition_arm_by_diet` | Habitual-quality composition within arms |
| `fig_quality_density` | Habitual and encountered quality distributions |
| `fig_effort_distribution` | Effort distribution by arm |
| `fig_habitual_split` | Habitual quality with the median used for the split |
| `fig_level_vs_diversity` | Level against diversity, by definition |
| `fig_moderator_leaning` | Political self-placement by habitual-quality group |
| `fig_moderator_vote` | Vote intention by habitual-quality group |
| `fig_moderator_attitude_change` | Signed attitude change by habitual-quality group |

Tables are written as LaTeX fragments and as CSV; figures as PNG.

# Part 1: Setup

```{r libraries, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(purrr)
library(readr)
library(stringr)
library(ggplot2)
```

```{r paths-config, echo=FALSE}
project_root <- "~/Desktop/GitHub/DoesMediaQualityMatter"
input_dir <- file.path(project_root, "Output", "03_analysis_data")
table_dir <- file.path(input_dir, "tables")
fig_dir   <- file.path(input_dir, "figures")
panelist_dir <- file.path(project_root, "Output", "00_setup")

walk(c(table_dir, fig_dir), dir.create, showWarnings = FALSE, recursive = TRUE)
```

```{r config}
WAVE_TOPICS <- c("1" = "Child support", "2" = "Energy transition", "3" = "Cannabis")
DIET_VARIANTS <- c("overall", "news", "news_corrected")
DIET_LABELS <- c(overall = "Overall scored diet", news = "Automated news diet",
                 news_corrected = "Corrected news diet")
COVARS_DESC <- c("att_baseline", "prior_engagement", "polknow_total",
                 "pol_interest_general", "newsuse_online", "edu_time",
                 "age", "gender_f")

theme_set(theme_minimal(base_size = 11))
ARM_COLOURS <- c(control = "grey60", verbal = "steelblue", monetary = "firebrick")
```

```{r helpers}
write_latex_table <- function(df, file, digits = 3, caption = NULL) {
  esc <- function(x) str_replace_all(as.character(x), "([_%&#])", "\\\\\\1")
  body <- df %>%
    mutate(across(where(is.numeric), ~ formatC(.x, format = "f", digits = digits))) %>%
    mutate(across(everything(), ~ ifelse(is.na(.x) | .x == "NA", "--", esc(.x))))
  header <- paste(paste0("\\textit{", esc(names(df)), "}"), collapse = " & ")
  rows <- apply(body, 1, function(r)
    paste0("      \\textit{", r[1], "} & ", paste(r[-1], collapse = " & "), " \\\\"))
  lines <- c(paste0("\\begin{tabular}{", paste(rep("c", ncol(df)), collapse = " "), "}"),
             "      \\hline", paste0("      ", header, " \\\\"), "      \\hline",
             rows, "      \\hline", "    \\end{tabular}")
  if (!is.null(caption)) lines <- c(paste0("% ", caption), lines)
  writeLines(lines, file.path(table_dir, paste0(file, ".tex")))
  write_csv(df, file.path(table_dir, paste0(file, ".csv")))
  invisible(df)
}

save_fig <- function(p, name, width = 10, height = 5) {
  print(p)
  ggsave(file.path(fig_dir, paste0(name, ".png")), p, width = width, height = height, dpi = 300)
}
```

```{r load-data}
analysis_data <- readRDS(file.path(input_dir, "analysis_data_by_wave.Rds"))

dat <- bind_rows(analysis_data) %>%
  mutate(topic = factor(WAVE_TOPICS[as.character(wave)], levels = WAVE_TOPICS))

cat("Participant-waves:", nrow(dat), "| participants:", n_distinct(dat$pid), "\n")
```

# Part 2: Descriptive Statistics

Table 5.1 of the Results chapter. Quality variables are summarised on the
participants for whom they exist, not on the full wave, so the `N` column
differs by row by design.

```{r descriptives}
desc_vars <- tribble(
  ~variable,             ~label,
  "y_abs",               "Attitude change (absolute)",
  "y_signed",            "Attitude change (signed)",
  "kno_signed",          "Knowledge change",
  "exp_topic_uptake_yn", "Topic-relevant uptake (0/1)",
  "effort_count",        "Topic-relevant visits",
  "topic_duration",      "Time on topic (s)",
  "q_primary",           "Encountered quality",
  "hab_overall_dw_pc1",  "Habitual quality (overall)",
  "hab_news_corrected_dw_pc1", "Habitual quality (corrected news)",
  "att_baseline",        "Baseline attitude",
  "polknow_total",       "Political knowledge",
  "pol_interest_general","Political interest",
  "newsuse_online",      "Online news use (days/week)",
  "age",                 "Age"
)

tab_desc <- desc_vars %>%
  pmap_dfr(function(variable, label) {
    x <- dat[[variable]]
    x <- x[!is.na(x)]
    tibble(Variable = label, N = length(x), Mean = mean(x), Std = sd(x),
           Minimum = min(x), Maximum = max(x), Median = median(x))
  })

print(as.data.frame(tab_desc))
write_latex_table(tab_desc, "tab_descriptives", caption = "Table 5.1: descriptives")
```

```{r descriptives-by-wave}
tab_desc_wave <- dat %>%
  group_by(Topic = topic) %>%
  summarise(N = n(),
            Uptake = mean(exp_topic_uptake_yn, na.rm = TRUE),
            Effort = median(effort_count, na.rm = TRUE),
            Quality = mean(q_primary, na.rm = TRUE),
            Attitude = mean(y_abs, na.rm = TRUE),
            .groups = "drop")

print(as.data.frame(tab_desc_wave))
write_latex_table(tab_desc_wave, "tab_descriptives_by_wave",
                  caption = "Key measures by wave")
```

# Part 3: Coverage

Non-missing counts per measure and wave. Uptake and the outcomes are complete
by construction; the quality measures and the habitual measures are not.




```{r coverage}
tab_coverage <- dat %>%
  group_by(Topic = topic) %>%
  summarise(
    N              = n(),
    Outcome        = sum(!is.na(y_abs)),
    Uptake         = sum(!is.na(exp_topic_uptake_yn)),
    `Any uptake`   = sum(exp_topic_uptake_yn == 1, na.rm = TRUE),
    `Quality (primary)`      = sum(!is.na(q_primary)),
    `Quality (news)`         = sum(!is.na(exp_q_dur_news)),
    `Quality (incl. search)` = sum(!is.na(exp_q_dur_all)),
    `Habitual (overall)`     = sum(!is.na(hab_overall_dw_pc1)),
    `Habitual (auto news)`   = sum(!is.na(hab_news_dw_pc1)),
    `Habitual (corr. news)`  = sum(!is.na(hab_news_corrected_dw_pc1)),
    # The covariate set is not complete, so adjusted models rest on fewer rows.
    `Covariate-complete`     = sum(if_all(all_of(COVARS_DESC), ~ !is.na(.x))),
    .groups = "drop"
  )


print(as.data.frame(tab_coverage))

write_latex_table(tab_coverage, "tab_coverage", digits = 0,
                  caption = "Coverage by measure and wave")
```


Three groups: no topic-relevant activity, activity without a scored domain,
and at least one scored domain.

```{r triage}
tab_triage <- dat %>%
  mutate(Group = case_when(
    exp_topic_uptake_yn == 0 ~ "1: No topic-relevant activity",
    is.na(q_primary)         ~ "2: Activity, no scored domain",
    TRUE                     ~ "3: At least one scored domain")) %>%
  count(Topic = topic, Group) %>%
  group_by(Topic) %>%
  mutate(Share = round(100 * n / sum(n), 1)) %>%
  ungroup() %>%
  rename(N = n)

print(as.data.frame(tab_triage))
write_latex_table(tab_triage, "tab_triage", digits = 1,
                  caption = "Quality-coverage triage")
```

```{r fig-triage}
p_triage <- tab_triage %>%
  ggplot(aes(x = Topic, y = Share, fill = Group)) +
  geom_col() +
  geom_text(aes(label = N), position = position_stack(vjust = .5), size = 3.2) +
  scale_fill_manual(values = c("grey75", "goldenrod", "steelblue")) +
  labs(title = "Where the quality measure loses the sample",
       subtitle = "Group 2 would be indistinguishable from group 1 under zero imputation",
       y = "Share of participant-waves (%)", x = NULL, fill = NULL) +
  theme(legend.position = "bottom")

save_fig(p_triage, "fig_coverage_triage", height = 5)
```


# Part 4: Randomization Balance

Per-variable means and p-values by arm for each wave, a joint test of
assignment on the covariate set, and the missingness of the one incomplete
covariate by arm.

```{r balance}
balance_vars <- c("att_baseline", "prior_engagement", "polknow_total",
                  "pol_interest_general", "newsuse_online", "edu_time", "age",
                  "hab_overall_dw_pc1")
# Each wave randomizes separately, so balance is computed per wave.
balance_one <- function(w) {
  d <- filter(dat, wave == w)
  means <- d %>%
    dplyr::select(group_f, all_of(balance_vars)) %>%
    pivot_longer(-group_f, names_to = "Variable") %>%
    group_by(Variable, group_f) %>%
    summarise(m = mean(value, na.rm = TRUE), .groups = "drop") %>%
    pivot_wider(names_from = group_f, values_from = m)

  pvals <- map_dfr(balance_vars, ~ tibble(
    Variable = .x,
    p = summary(aov(reformulate("group_f", .x), data = d))[[1]][["Pr(>F)"]][1]))

  means %>% left_join(pvals, by = "Variable") %>%
    mutate(Topic = WAVE_TOPICS[as.character(w)], .before = 1)
}

tab_balance <- map_dfr(1:3, balance_one) %>%
  mutate(across(where(is.numeric), ~ round(.x, 3)))

cat("Covariate balance across arms, by wave:\n")
print(as.data.frame(tab_balance))

# Joint test of assignment on the covariate set, alongside the per-variable
# tests above.
cat("\nJoint test of assignment on the covariate set:\n")
map_dfr(1:3, function(w) {
  d <- filter(dat, wave == w) %>% filter(if_all(all_of(balance_vars), ~ !is.na(.x)))
  fit <- lm(reformulate(balance_vars, "as.integer(group_f == 'monetary')"), data = d)
  f <- summary(fit)$fstatistic
  tibble(Topic = WAVE_TOPICS[as.character(w)], N = nrow(d),
         F = round(f[1], 2),
         p = round(pf(f[1], f[2], f[3], lower.tail = FALSE), 3))
}) %>% as.data.frame() %>% print()

write_latex_table(tab_balance, "tab_balance", caption = "Covariate balance by wave")
```
```{r missingness-by-arm}
# prior_engagement is the only covariate with missing values. Its missingness
# is tested against arm, since adjusted models drop those rows.
miss_by_arm <- dat %>%
  group_by(Topic = topic, Arm = group_f) %>%
  summarise(n = n(),
            n_missing = sum(is.na(prior_engagement)),
            pct = round(100 * mean(is.na(prior_engagement)), 1),
            .groups = "drop")

cat("Missingness of prior_engagement by arm:\n")
print(as.data.frame(miss_by_arm))

miss_test <- dat %>%
  group_by(Topic = topic) %>%
  summarise(p = chisq.test(table(group_f, is.na(prior_engagement)))$p.value,
            .groups = "drop") %>%
  mutate(p = round(p, 3))

cat("\nChi-squared test of missingness against arm:\n")
print(as.data.frame(miss_test))

write_latex_table(miss_by_arm, "tab_missingness_by_arm", digits = 1,
                  caption = "Missingness of prior engagement by treatment arm")
```

# Part 5: Group Composition

Arm sizes, habitual-quality subgroup sizes, and the cross-tabulation of the
two, with chi-squared tests of independence between arm and subgroup.

```{r composition-arms}
tab_arms <- dat %>%
  count(Topic = topic, Arm = group_f) %>%
  pivot_wider(names_from = Arm, values_from = n, values_fill = 0L) %>%
  mutate(Total = rowSums(across(where(is.numeric))))

print(as.data.frame(tab_arms))
write_latex_table(tab_arms, "tab_composition_arms", digits = 0,
                  caption = "Arm sizes by wave")
```

```{r composition-diet}
tab_diet <- map_dfr(DIET_VARIANTS, function(v) {
  dat %>%
    count(Topic = topic, Group = .data[[paste0("hab_", v, "_level_group")]]) %>%
    mutate(Definition = DIET_LABELS[[v]])
}) %>%
  mutate(Group = as.character(Group),
         Group = if_else(is.na(Group), "missing", Group)) %>%
  pivot_wider(names_from = Group, values_from = n, values_fill = 0L)

print(as.data.frame(tab_diet))
write_latex_table(tab_diet, "tab_composition_diet", digits = 0,
                  caption = "Habitual-quality subgroup sizes")
```

```{r composition-arm-by-diet}
tab_cross <- map_dfr(DIET_VARIANTS, function(v) {
  dat %>%
    filter(!is.na(.data[[paste0("hab_", v, "_level_group")]])) %>%
    count(Topic = topic, Arm = group_f,
          Diet = .data[[paste0("hab_", v, "_level_group")]]) %>%
    mutate(Definition = DIET_LABELS[[v]])
}) %>%
  unite("Cell", Arm, Diet, sep = " / ") %>%
  pivot_wider(names_from = Cell, values_from = n, values_fill = 0L)

cat("Arm x habitual-quality cell sizes:\n")
print(as.data.frame(tab_cross))
write_latex_table(tab_cross, "tab_composition_arm_by_diet", digits = 0,
                  caption = "Arm by habitual-quality cells")

# Chi-squared test of arm against habitual-quality group, per definition
# and wave.
cat("\nChi-squared tests of arm against habitual-quality group:\n")
map_dfr(DIET_VARIANTS, function(v) {
  map_dfr(names(WAVE_TOPICS), function(w) {
    d <- filter(dat, wave == as.integer(w), !is.na(.data[[paste0("hab_", v, "_level_group")]]))
    tt <- table(d$group_f, d[[paste0("hab_", v, "_level_group")]])
    tibble(Definition = DIET_LABELS[[v]], Topic = WAVE_TOPICS[[w]],
           p = round(suppressWarnings(chisq.test(tt)$p.value), 3))
  })
}) %>% as.data.frame() %>% print()
```

```{r fig-composition}
p_comp <- map_dfr(DIET_VARIANTS, function(v) {
  dat %>%
    filter(!is.na(.data[[paste0("hab_", v, "_level_group")]])) %>%
    count(topic, group_f, Diet = .data[[paste0("hab_", v, "_level_group")]]) %>%
    mutate(Definition = DIET_LABELS[[v]])
}) %>%
  ggplot(aes(x = group_f, y = n, fill = Diet)) +
  geom_col(position = "fill") +
  facet_grid(Definition ~ topic) +
  scale_fill_manual(values = c(low = "goldenrod", high = "steelblue")) +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Habitual-quality composition within treatment arms",
       subtitle = "Even splits indicate the moderator is not confounded with assignment",
       x = NULL, y = NULL, fill = "Habitual quality") +
  theme(legend.position = "bottom")

save_fig(p_comp, "fig_composition_arm_by_diet", height = 7)
```

# Part 6: Distributions

```{r fig-quality-density}
p_q <- dat %>%
  dplyr::select(topic, `Habitual (overall)` = hab_overall_dw_pc1,
         `Habitual (corr. news)` = hab_news_corrected_dw_pc1,
         `Encountered (experimental)` = q_primary) %>%
  pivot_longer(-topic, names_to = "Measure", values_to = "pc1") %>%
  filter(!is.na(pc1)) %>%
  ggplot(aes(x = pc1, fill = Measure, colour = Measure)) +
  geom_density(alpha = .25) +
  facet_wrap(~ topic, nrow = 1) +
  labs(title = "Domain quality: habitual diet versus experimental period",
       subtitle = "Experimental quality rests on few visits per participant and is wider",
       x = "PC1 (0-1)", y = "Density", fill = NULL, colour = NULL) +
  theme(legend.position = "bottom")

save_fig(p_q, "fig_quality_density")
```

```{r fig-attitude-density}
p_att <- dat %>%
  dplyr::select(topic, group_f, Pre = att_baseline, Post = att_post) %>%
  pivot_longer(c(Pre, Post), names_to = "Block", values_to = "attitude") %>%
  mutate(Block = factor(Block, levels = c("Pre", "Post"))) %>%
  ggplot(aes(x = attitude, fill = Block)) +
  geom_density(alpha = .4, adjust = 1.4) +
  facet_grid(group_f ~ topic) +
  scale_fill_manual(values = c(Pre = "grey60", Post = "firebrick")) +
  labs(title = "Policy attitude before and after the information period",
       subtitle = "1 = should not be introduced, 7 = should be introduced",
       x = "Attitude", y = "Density", fill = NULL) +
  theme(legend.position = "bottom")

save_fig(p_att, "fig_attitude_density", height = 7)
```

```{r fig-attitude-change}
p_chg <- dat %>%
  filter(!is.na(y_signed)) %>%
  ggplot(aes(x = y_signed, fill = group_f)) +
  geom_bar(position = "dodge") +
  facet_wrap(~ topic, nrow = 1, scales = "free_y") +
  scale_fill_manual(values = ARM_COLOURS) +
  labs(title = "Signed attitude change by arm",
       subtitle = "A symmetric spread around zero produces movement without direction",
       x = "Post minus pre", y = "Participants", fill = NULL) +
  theme(legend.position = "bottom")

save_fig(p_chg, "fig_attitude_change")
```

```{r fig-quality-attitude}
p_qa <- dat %>%
  filter(!is.na(q_primary), !is.na(y_abs)) %>%
  ggplot(aes(x = q_primary, y = y_abs)) +
  geom_point(aes(colour = hab_overall_level_group), alpha = .6) +
  geom_smooth(aes(colour = hab_overall_level_group), method = "lm", se = FALSE) +
  facet_wrap(~ topic, nrow = 1) +
  scale_colour_manual(values = c(low = "goldenrod", high = "steelblue"),
                      na.value = "grey80") +
  labs(title = "Encountered quality and attitude change, by habitual-quality group",
       subtitle = "Descriptive; the H3a interaction is tested in 03b",
       x = "Encountered quality (PC1)", y = "Absolute attitude change",
       colour = "Habitual quality") +
  theme(legend.position = "bottom")

save_fig(p_qa, "fig_quality_vs_attitude")
```

```{r fig-uptake}
p_up <- dat %>%
  group_by(topic, group_f) %>%
  summarise(rate = mean(exp_topic_uptake_yn, na.rm = TRUE),
            n = n(), .groups = "drop") %>%
  ggplot(aes(x = group_f, y = rate, fill = group_f)) +
  geom_col() +
  geom_text(aes(label = paste0(round(100 * rate), "%")), vjust = -.4, size = 3.2) +
  facet_wrap(~ topic, nrow = 1) +
  scale_fill_manual(values = ARM_COLOURS, guide = "none") +
  scale_y_continuous(labels = scales::percent, limits = c(0, .6)) +
  labs(title = "Topic-relevant uptake by arm",
       subtitle = "The behavioural first stage, descriptively",
       x = NULL, y = "Share with any topic-relevant visit")

save_fig(p_up, "fig_uptake_by_arm")
```

```{r fig-effort}
p_eff <- dat %>%
  filter(exp_topic_uptake_yn == 1) %>%
  ggplot(aes(x = effort_count, fill = group_f)) +
  geom_histogram(bins = 30, position = "identity", alpha = .5) +
  facet_wrap(~ topic, nrow = 1) +
  scale_x_log10() +
  scale_fill_manual(values = ARM_COLOURS) +
  labs(title = "Topic-relevant visits among participants who engaged",
       subtitle = "Log scale; participants with no topic-relevant visit excluded",
       x = "Visits (log scale)", y = "Participants", fill = NULL) +
  theme(legend.position = "bottom")

save_fig(p_eff, "fig_effort_distribution")
```

Level and diversity of the habitual diet, with the medians that define the
subgroups. Level is the duration-weighted mean PC1, diversity its
duration-weighted standard deviation; both are participant-level and
constant across waves.

```{r fig-habitual-split}
p_hab <- map_dfr(DIET_VARIANTS, function(v) {
  dat %>%
    distinct(pid, .keep_all = TRUE) %>%
    transmute(Definition = DIET_LABELS[[v]],
              pc1 = .data[[paste0("hab_", v, "_dw_pc1")]])
}) %>%
  filter(!is.na(pc1))

p_hab_med <- p_hab %>%
  group_by(Definition) %>%
  summarise(m = median(pc1), .groups = "drop")

p_habitual_split <- p_hab %>%
  ggplot(aes(x = pc1)) +
  geom_density(fill = "steelblue", alpha = .25, colour = "steelblue") +
  geom_vline(data = p_hab_med, aes(xintercept = m),
             linetype = "dashed", colour = "firebrick") +
  facet_wrap(~ Definition, nrow = 1) +
  labs(title = "Habitual quality and the median split",
       subtitle = "Dashed line at the median used to form the subgroups",
       x = "Duration-weighted PC1 (level)", y = "Density")

print(p_habitual_split)
save_fig(p_habitual_split, "fig_habitual_split", width = 11, height = 4)
```

```{r fig-level-vs-diversity}
# Level against diversity per definition, with the two medians that define the
# four subgroups.
lvl_div <- map_dfr(DIET_VARIANTS, function(v) {
  dat %>%
    distinct(pid, .keep_all = TRUE) %>%
    transmute(Definition = DIET_LABELS[[v]],
              level     = .data[[paste0("hab_", v, "_dw_pc1")]],
              diversity = .data[[paste0("hab_", v, "_dw_sd_pc1")]],
              Subgroup  = .data[[paste0("hab_", v, "_level_diversity_group")]])
}) %>%
  filter(!is.na(level), !is.na(diversity), !is.na(Subgroup))

lvl_div_med <- lvl_div %>%
  group_by(Definition) %>%
  summarise(m_level = median(level), m_div = median(diversity), .groups = "drop")

p_level_vs_diversity <- lvl_div %>%
  ggplot(aes(x = level, y = diversity, colour = Subgroup)) +
  geom_point(alpha = .55, size = 1.1) +
  geom_vline(data = lvl_div_med, aes(xintercept = m_level),
             linetype = "dashed", colour = "grey30") +
  geom_hline(data = lvl_div_med, aes(yintercept = m_div),
             linetype = "dashed", colour = "grey30") +
  facet_wrap(~ Definition, nrow = 1) +
  labs(title = "Habitual media diet: level against diversity",
       subtitle = "Dashed lines at the medians that define the subgroups",
       x = "Duration-weighted PC1 (level)",
       y = "Duration-weighted SD of PC1 (diversity)",
       colour = NULL) +
  theme(legend.position = "bottom")

print(p_level_vs_diversity)
save_fig(p_level_vs_diversity, "fig_level_vs_diversity", width = 11, height = 4.5)

# Correlation between the two dimensions, per definition.
lvl_div %>%
  group_by(Definition) %>%
  summarise(n = n(),
            r = round(cor(level, diversity, use = "complete.obs"), 3),
            .groups = "drop") %>%
  as.data.frame() %>% print()
```

# Part 7: Habitual Quality against Political Position

The moderation models treat habitual news quality as a media-exposure trait.
This part compares the habitual-quality groups on left-right self-placement
and on reported vote intention. Both variables are measured before treatment,
so all arms are included.

```{r metadata-inspect}
meta_raw <- readRDS(file.path(panelist_dir, "panelist_metadata_final.Rds"))

cat("Rows:", nrow(meta_raw), "| unique pids:", n_distinct(meta_raw$pid), "\n\n")
print(grep("vot|party|partei|wahl|leaning|ideo|links|rechts|^pol", names(meta_raw),
           value = TRUE, ignore.case = TRUE))
```
```{r metadata-join}
LEANING_VAR <- "pol_attitude"      # left-right self-placement
VOTE_VAR    <- "voting_decision_f"   # party, categorical
MOD_VARIANT <- "news_corrected"    # diet definition carrying the moderation tests
MOD_LEVELS  <- "median"          # "median" for the analysis split, "quartile" for four curves

meta <- readRDS(file.path(panelist_dir, "panelist_metadata_final.Rds")) %>%
  mutate(pid = as.character(pid)) %>%
  dplyr::select(pid, all_of(c(LEANING_VAR, VOTE_VAR))) %>%
  distinct(pid, .keep_all = TRUE)

n_before <- nrow(dat)
dat_pol <- dat %>% left_join(meta, by = "pid")
stopifnot(nrow(dat_pol) == n_before)

cat("Coverage of the joined variables:\n")
dat_pol %>%
  summarise(across(all_of(c(LEANING_VAR, VOTE_VAR)),
                   list(n = ~ sum(!is.na(.x)), pct = ~ round(100 * mean(!is.na(.x)), 1)))) %>%
  as.data.frame() %>% print()
```
Grouping variable for the figures below. `MOD_LEVELS` switches between the
median split used in the models and a quartile split.

```{r moderator-groups}
hab_var <- paste0("hab_", MOD_VARIANT, "_dw_pc1")

dat_pol <- dat_pol %>%
  mutate(Diet = if (MOD_LEVELS == "quartile") {
    cut(.data[[hab_var]],
        breaks = quantile(.data[[hab_var]], probs = seq(0, 1, .25), na.rm = TRUE),
        labels = c("Q1 lowest", "Q2", "Q3", "Q4 highest"),
        include.lowest = TRUE)
  } else {
    factor(.data[[paste0("hab_", MOD_VARIANT, "_level_group")]],
           levels = c("low", "high"), labels = c("Low", "High"))
  })

DIET_COLOURS <- if (nlevels(dat_pol$Diet) == 2) {
  c("Low" = "firebrick", "High" = "steelblue")
} else {
  setNames(c("firebrick", "darkorange", "darkgreen", "steelblue"),
           levels(dat_pol$Diet))
}

cat("\nCell sizes by habitual-quality group and wave:\n")
dat_pol %>% count(topic, Diet) %>%
  pivot_wider(names_from = Diet, values_from = n, values_fill = 0L) %>%
  as.data.frame() %>% print()
```
Two plot helpers: a density for continuous variables and a dodged bar chart
for categorical ones. Both colour by the habitual-quality group.

```{r moderator-plot-helpers}
plot_density <- function(d, var, title, subtitle, xlab, facet_wave = TRUE, bw = 0.8) {
  p <- d %>%
    rename(x = all_of(var)) %>%
    filter(!is.na(x), !is.na(Diet)) %>%
    ggplot(aes(x = x, colour = Diet)) +
    geom_density(linewidth = .8, bw = bw) +
    scale_colour_manual(values = DIET_COLOURS) +
    labs(title = title, subtitle = subtitle, x = xlab, y = "Density",
         colour = "Habitual news quality") +
    theme(legend.position = "right")
  if (facet_wave) p + facet_wrap(~ topic, ncol = 1, scales = "free_y") else p
}

plot_composition <- function(d, var, title, subtitle, xlab) {
  d %>%
    rename(Category = all_of(var)) %>%
    filter(!is.na(Category), !is.na(Diet)) %>%
    count(Diet, Category) %>%
    group_by(Diet) %>% mutate(Share = 100 * n / sum(n)) %>% ungroup() %>%
    ggplot(aes(x = Category, y = Share, fill = Diet)) +
    geom_col(position = position_dodge(width = .8), width = .75) +
    scale_fill_manual(values = DIET_COLOURS) +
    labs(title = title, subtitle = subtitle, x = xlab,
         y = "Share within habitual-quality group (%)",
         fill = "Habitual news quality") +
    theme(axis.text.x = element_text(angle = 30, hjust = 1),
          legend.position = "right")
}
```


```{r moderator-figures}
p_leaning <- dat_pol %>%
  distinct(pid, .keep_all = TRUE) %>%
  rename(x = all_of(LEANING_VAR)) %>%
  filter(!is.na(x), !is.na(Diet)) %>%
  count(Diet, x) %>%
  group_by(Diet) %>% mutate(Share = 100 * n / sum(n)) %>% ungroup() %>%
  ggplot(aes(x = factor(x), y = Share, fill = Diet)) +
  geom_col(position = position_dodge(width = .8), width = .75) +
  scale_fill_manual(values = DIET_COLOURS) +
  labs(title = "Political self-placement by habitual news quality",
       subtitle = "One observation per participant; all arms",
       x = "Left-right self-placement", y = "Share within group (%)",
       fill = "Habitual news quality")

save_fig(p_leaning, "fig_moderator_leaning", height = 4)

# Vote intention, party choices only, ordered left to right.
PARTY_ORDER <- c("Linke", "Gruene", "SPD", "FDP", "CDU/CSU", "AFD")

p_vote <- dat_pol %>%
  distinct(pid, .keep_all = TRUE) %>%
  filter(.data[[VOTE_VAR]] %in% PARTY_ORDER) %>%
  mutate(across(all_of(VOTE_VAR), ~ factor(.x, levels = PARTY_ORDER))) %>%
  plot_composition(VOTE_VAR,
                   "Vote intention by habitual news quality",
                   "Party choices only, ordered left to right; one observation per participant",
                   "Reported vote")
p_vote <- dat_pol %>%
  distinct(pid, .keep_all = TRUE) %>%
  filter(.data[[VOTE_VAR]] %in% PARTY_ORDER) %>%
  mutate(across(all_of(VOTE_VAR), ~ factor(.x, levels = PARTY_ORDER))) %>%
  plot_composition(VOTE_VAR,
                   "Vote intention by habitual news quality",
                   "Party choices only, ordered left to right; one observation per participant",
                   "Reported vote")



save_fig(p_vote, "fig_moderator_vote", height = 5)

# Signed attitude change by habitual-quality group, faceted by wave.
p_change <- dat_pol %>%
  plot_density("y_signed",
               "Signed attitude change by habitual news quality",
               "Participant-waves, all arms; dashed line at no change",
               "Attitude change (post minus pre)", bw = 0.5) +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey40")
save_fig(p_change, "fig_moderator_attitude_change", height = 7)



```
Numerical counterparts to the two figures above.

```{r moderator-association}
cat("Association between habitual quality and political position:\n")
dat_pol %>%
  distinct(pid, .keep_all = TRUE) %>%
  summarise(n = sum(!is.na(.data[[hab_var]]) & !is.na(.data[[LEANING_VAR]])),
            r = round(cor(.data[[hab_var]], .data[[LEANING_VAR]],
                          use = "complete.obs"), 3)) %>%
  as.data.frame() %>% print()

cat("\nMean habitual quality by reported vote:\n")
dat_pol %>%
  distinct(pid, .keep_all = TRUE) %>%
  filter(!is.na(.data[[VOTE_VAR]])) %>%
  group_by(Vote = .data[[VOTE_VAR]]) %>%
  summarise(n = n(), mean_quality = round(mean(.data[[hab_var]], na.rm = TRUE), 3),
            .groups = "drop") %>%
  arrange(desc(mean_quality)) %>%
  as.data.frame() %>% print()



d1 <- dat_pol %>% distinct(pid, .keep_all = TRUE)

cat("Self-placement against habitual quality: r =",
    round(cor(d1[[hab_var]], d1[[LEANING_VAR]], use = "complete.obs"), 3), "\n")

cat("Vote intention against habitual-quality group: p =",
    round(chisq.test(table(d1[[VOTE_VAR]], d1$Diet))$p.value, 3), "\n")
```

# Part 8: Saved Files

```{r file-list}
cat("Tables:\n"); print(list.files(table_dir, pattern = "\\.tex$"))
cat("\nFigures:\n"); print(list.files(fig_dir, pattern = "\\.png$"))
```
