---
title: "App Visits and News-App-to-Domain Mapping"
author: "Master's Thesis -- Media Quality / Media Diet"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = FALSE, message = TRUE)
```

# Overview

Covers in-app browsing: building the `app_visits` table and preparing a
manual news-app-to-domain mapping workbook. Both read the same raw input
(`app_metadata.csv`, `mobile_views.csv`); mobile *web* browsing is covered
separately.

| Part | Does |
|---|---|
| 1 | Builds the `app_visits` table used later in the pipeline, with app metadata already deduplicated and aligned |
| 2 | Prepares an editable Excel workbook for **manual** app-to-domain coding; touches no visit-level data |
| 3 | Checks whether a traffic-based Top-N view of apps (independent of app-store category) would surface anything Part 2's category filter missed |

## Outputs

| Object | Part | Type | Role |
|---|---|---|---|
| `app_metadata_lookup.Rds` / `.RData` | 1 | Metadata, one row per `app_id` | `app_id`, `app_n`, `app_cat`, plus alignment audit columns; both inconsistency directions already resolved |
| `app_id_alignment_log.Rds` / `.RData` | 1 | Diagnostic, one row per aligned group | Documents exactly which `app_id`s were aligned to which representative name/category |
| `app_visits.Rds` / `.RData` | 1 | Visit-level, in-app only | `pid`, `app_id`, `used_at`, `duration`, `app_n`, `app_cat`; feeds into later visit-level processing |
| `app_news_lookup_needs_domain_mapping.xlsx` | 2 | Editable workbook | One row per candidate news app, for manual publisher-domain coding; joined back in later, when habitual media quality is constructed |

## Why apps and web visits stay separate

- A mobile visit row is either **web** (has a `domain`) or **app** (has an
  `app_id`), never both.
- Domain-level quality scoring (PC1, MBFC) needs a registered domain; an
  app has no domain by default.
- Two-stage approach instead of guessing a domain from the app name:
  1. Isolate app visits cleanly (Part 1)
  2. Manually decide which apps map to a real news-publisher domain (Part 2)
- Readers, browsers, aggregators, and platforms are excluded in Part 2, not
  force-mapped to a domain.

# Part 1: Building `app_visits`

## Setup

Filters to valid panel participants right after import, via the same
`pid_lookup_february` reference from the setup stage.

```{r libraries}
library(readr)
library(dplyr)
library(purrr)
library(stringr)
```

```{r paths-and-helper, include=FALSE}

project_root <- "~/Desktop/GitHub/DoesMediaQualityMatter"
code_dir <- file.path(project_root, "Code")
pid_dir <- file.path(project_root, "Output", "00_setup")
output_dir <- file.path(project_root, "Output", "01_visits")
dir.create(output_dir, showWarnings = FALSE, recursive = TRUE)

# Saves as .Rds (readRDS() reuse) and .RData (load(), object under its own
# name, matching how df1/df2/df3 are loaded elsewhere).
save_both <- function(obj, name, dir = output_dir) {
  assign(name, obj)
  saveRDS(obj, file.path(dir, paste0(name, ".Rds")))
  save(list = name, file = file.path(dir, paste0(name, ".RData")))
  message("Saved ", name)
}
```

```{r valid-pids}
pid_lookup_february <- readRDS(file.path(pid_dir, "pid_lookup_february.Rds"))
valid_pids <- as.character(pid_lookup_february$pid)
```

## Raw file paths

Only batches from 1 April 2023 onward have `app_id`-bearing exports in this
format, so this path list is shorter than the full web/mobile lists used
elsewhere.

```{r files, include=FALSE}
mobile_visit_paths <- c(
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-04-01-to-2023-04-15-exports/mobile_views.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/fixed/2023-04-15-to-2023-05-01-exports/mobile_views.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-05-01-to-2023-05-15-exports/mobile_views.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-05-15-to-2023-06-01-exports/mobile_views.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-06-01-to-2023-06-15-exports/mobile_views.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-06-15-to-2023-07-01-exports/mobile_views.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-07-01-to-2023-07-15-exports/mobile_views.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-07-15-to-2023-08-01-exports/mobile_views.csv"
) |> unique()

app_metadata_paths <- c(
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-04-01-to-2023-04-15-exports/app_metadata.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/fixed/2023-04-15-to-2023-05-01-exports/app_metadata.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-05-01-to-2023-05-15-exports/app_metadata.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-05-15-to-2023-06-01-exports/app_metadata.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-06-01-to-2023-06-15-exports/app_metadata.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-06-15-to-2023-07-01-exports/app_metadata.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-07-01-to-2023-07-15-exports/app_metadata.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-07-15-to-2023-08-01-exports/app_metadata.csv"
) |> unique()


missing_mobile_files <- mobile_visit_paths[!file.exists(mobile_visit_paths)]
missing_app_metadata_files <- app_metadata_paths[!file.exists(app_metadata_paths)]

if (length(missing_mobile_files) > 0) {
  stop("Missing mobile_views files:\n", paste(missing_mobile_files, collapse = "\n"))
}
if (length(missing_app_metadata_files) > 0) {
  stop("Missing app_metadata files:\n", paste(missing_app_metadata_files, collapse = "\n"))
}
```

```{r file-paths, include=TRUE}
#mobile_visit_paths <- c() |> unique()

#app_metadata_paths <- c() |> unique()

#missing_mobile_files <- mobile_visit_paths[!file.exists(mobile_visit_paths)]
#missing_app_metadata_files <- app_metadata_paths[!file.exists(app_metadata_paths)]

#if (length(missing_mobile_files) > 0) {
#  stop("Missing mobile_views files:\n", paste(missing_mobile_files, collapse = "\n"))
#}
#if (length(missing_app_metadata_files) > 0) {
#  stop("Missing app_metadata files:\n", paste(missing_app_metadata_files, collapse = "\n"))
#}
```

## Robust file-reading helper

Same delimiter-detection-with-fallback used elsewhere in the pipeline: auto
detect, retry with `;` if only 1 column results, fall back to plain CSV on
error.

```{r read-helper}
read_raw_file <- function(file_path) {
  message("Reading: ")
  df <- tryCatch({
    tmp <- read_delim(file_path, delim = NULL, show_col_types = FALSE, progress = FALSE)
    if (ncol(tmp) == 1) {
      tmp <- read_delim(file_path, delim = ";", show_col_types = FALSE, progress = FALSE)
    }
    tmp
  }, error = function(e) {
    read_csv(file_path, show_col_types = FALSE, progress = FALSE)
  })
  df %>% mutate(source_file = file_path)
}
```

## Isolating app visits from the mobile export

The mobile export mixes web visits (`domain`) and app visits (`app_id`) in
one file. "App visit" here means non-missing `app_id`, restricted to valid
panel participants immediately, so invalid `pid`s never carry further
downstream.

```{r isolate-app-visits, include=FALSE}
mobile_views_raw <- map_dfr(mobile_visit_paths, read_raw_file)

if ("p_id" %in% names(mobile_views_raw) && !"pid" %in% names(mobile_views_raw)) {
  mobile_views_raw <- mobile_views_raw %>% rename(pid = p_id)
}

required_cols <- c("pid", "app_id", "used_at", "duration")
missing_cols <- setdiff(required_cols, names(mobile_views_raw))

if (length(missing_cols) > 0) {
  stop(
    "mobile_views is missing required column(s): ", paste(missing_cols, collapse = ", "),
    "\nColumns found: ", paste(names(mobile_views_raw), collapse = ", ")
  )
}

app_visits_raw <- mobile_views_raw %>%
  mutate(pid = as.character(pid), app_id = as.character(app_id)) %>%
  filter(!is.na(app_id), app_id != "") %>%
  filter(pid %in% valid_pids) %>%
  select(pid, app_id, used_at, duration)

unique_app_ids_observed <- unique(app_visits_raw$app_id)
```

```{r}
cat("Rows in mobile_views (total):", nrow(mobile_views_raw), "\n")
cat("Rows identified as app visits (valid pids only):", nrow(app_visits_raw), "\n")
cat("Unique pids with >=1 app visit:", n_distinct(app_visits_raw$pid), "\n")
cat("Unique app_ids observed:", n_distinct(app_visits_raw$app_id), "\n")
```

## Attaching descriptive app metadata

Purely descriptive at this stage: `app_n` (name) and `app_cat` (Bilendi's
App/Play Store category), not a domain mapping. Two independent
inconsistency directions are resolved here, before `app_metadata_lookup`
is saved, since both conflicts already exist at the metadata level,
regardless of whether a given `app_id` ever had a visit:

- **Direction 1, one `app_id`, several competing metadata values** across
  export batches. Resolved first: keep only the most frequently observed
  `app_n`/`app_cat` combination per `app_id`.
- **Direction 2, several `app_id`s, one shared app name** (typically an
  iOS and an Android build). Resolved second: every `app_id` in such a
  group gets its `app_n`/`app_cat` overwritten with one shared,
  group-level value, chosen by preferring
  `"News, Media & Publications"` if any `app_id` in the group already
  carries that category, falling back to the alphanumerically first
  `app_id` otherwise.

Critically, `app_metadata_lookup` keeps **one row per original `app_id`**
throughout -- direction 2 aligns values across rows, it does not collapse
them into fewer rows. The join below (`app_visits_raw %>%
left_join(app_metadata_lookup, by = "app_id")`) must find a match for
every `app_id` that ever had a visit; collapsing rows here would silently
drop the metadata for every `app_id` other than the chosen representative.

```{r attach-metadata, include=FALSE}
app_metadata_raw <- map_dfr(app_metadata_paths, read_raw_file)

required_app_columns <- c("app_id", "app_n", "app_cat")
missing_app_columns <- setdiff(required_app_columns, names(app_metadata_raw))

if (length(missing_app_columns) > 0) {
  stop(
    "app_metadata is missing required column(s): ", paste(missing_app_columns, collapse = ", "),
    "\nColumns found: ", paste(names(app_metadata_raw), collapse = ", ")
  )
}

news_category_regex <- regex("^News,\\s*Media\\s*&\\s*Publications$", ignore_case = TRUE)

## Direction 1: one app_id, several competing metadata values across
## export batches -- keep only the most frequently observed combination.
## One row per app_id, unchanged in row count from app_metadata_raw's
## distinct app_ids.
app_metadata_by_id <- app_metadata_raw %>%
  mutate(
    app_id = as.character(app_id),
    app_n = str_squish(as.character(app_n)),
    app_cat = str_squish(as.character(app_cat))
  ) %>%
  filter(!is.na(app_id), app_id != "") %>%
  count(app_id, app_n, app_cat, name = "n_occurrences") %>%
  group_by(app_id) %>%
  slice_max(n_occurrences, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  select(app_id, app_n, app_cat)

n_app_ids_before_direction1 <- app_metadata_raw %>%
  mutate(app_id = as.character(app_id)) %>%
  filter(!is.na(app_id), app_id != "") %>%
  n_distinct()

cat("Unique app_ids before direction-1 resolution:", n_app_ids_before_direction1, "\n")
cat("Unique app_ids after direction-1 resolution:", nrow(app_metadata_by_id), "\n")
cat("Confirms exactly one row per app_id:",
    n_app_ids_before_direction1 == nrow(app_metadata_by_id), "\n")

## Direction 2: several app_ids, one shared name. Uses mutate(), not
## summarise(), within each group -- every original app_id keeps its own
## row, only app_n/app_cat are overwritten with the group's chosen value.
## Row count of app_metadata_lookup therefore still equals
## nrow(app_metadata_by_id).
app_metadata_lookup <- app_metadata_by_id %>%
  mutate(
    app_group_key = str_squish(str_to_lower(app_n)),
    is_news_cat = str_detect(app_cat, news_category_regex)
  ) %>%
  arrange(app_group_key, desc(is_news_cat), app_id) %>%
  group_by(app_group_key) %>%
  mutate(
    app_n = first(app_n),
    app_cat = first(app_cat),
    representative_app_id = first(app_id),
    n_app_ids_in_group = n_distinct(app_id),
    all_app_ids_in_group = paste(sort(unique(app_id)), collapse = "; "),
    any_news_cat_in_group = any(is_news_cat)
  ) %>%
  ungroup() %>%
  select(app_id, app_n, app_cat, representative_app_id,
         n_app_ids_in_group, all_app_ids_in_group, any_news_cat_in_group)

cat("Rows in app_metadata_lookup (should equal app_ids after direction 1):",
    nrow(app_metadata_lookup), "\n")
cat("Confirms row count unchanged by direction-2 alignment:",
    nrow(app_metadata_lookup) == nrow(app_metadata_by_id), "\n")
cat("app_ids belonging to a group of 2+ that got aligned:",
    sum(app_metadata_lookup$n_app_ids_in_group > 1), "\n")
cat("Of those, aligned via the News, Media & Publications preference:",
    sum(app_metadata_lookup$n_app_ids_in_group > 1 & app_metadata_lookup$any_news_cat_in_group), "\n")

## Diagnostic log: one row per group, not per app_id, for a compact
## audit of exactly which app_ids were aligned to which representative.
app_id_alignment_log <- app_metadata_lookup %>%
  filter(n_app_ids_in_group > 1) %>%
  distinct(app_n, representative_app_id, any_news_cat_in_group,
           n_app_ids_in_group, all_app_ids_in_group)

cat("Distinct groups with multiple app_ids aligned:", nrow(app_id_alignment_log), "\n")
print(app_id_alignment_log)

save_both(app_metadata_lookup, "app_metadata_lookup")
save_both(app_id_alignment_log, "app_id_alignment_log")
```

## Joining metadata onto app visits

Unchanged join, `by = "app_id"`: since `app_metadata_lookup` still has
exactly one row per original `app_id` (direction 2 only aligned values
within rows, never removed rows), every `app_id` observed in
`app_visits_raw` finds its match here, including the "other" app_id in
an aligned group -- it now simply carries the same, aligned `app_n`/
`app_cat` as its group's representative.

```{r join-metadata-onto-visits}
app_visits <- app_visits_raw %>%
  left_join(app_metadata_lookup, by = "app_id")

cat("App visits matched to app_n/app_cat:", sum(!is.na(app_visits$app_n)), "of", nrow(app_visits), "\n")
cat("App visits with no metadata match:", sum(is.na(app_visits$app_n)), "\n")
cat("Unique app_ids in app_visits:", n_distinct(app_visits$app_id), "\n")
cat("Unique app names in app_visits (post-alignment):", n_distinct(app_visits$app_n), "\n")
```

## Saving

```{r save-app-visits}
glimpse(app_visits)
save_both(app_visits, "app_visits")
```

# Part 2: Preparing the News-App-to-Domain Mapping Workbook

Does not modify `app_visits` or any other visit-level data. Only output: an
editable Excel workbook, filled in by hand afterwards. Depends on
`mobile_views_raw` and `output_dir` from Part 1.

## Why manual mapping

| Issue | Consequence |
|---|---|
| App category (e.g. "News, Media & Publications") only signals "plausibly a news app" | Not which publisher domain, if any, is behind it |
| Some apps in that category are genuine single-publisher news apps | e.g. a broadcaster's own app, clear domain mapping |
| Others are readers, aggregators, browsers, platforms | No single editorial publisher; forcing a domain would misclassify them |
| Decision | Export only the candidate apps observed in visit data; decide app by app, by hand |

## Restricting to apps observed in visit data

Data minimisation: build a mapping workbook only for apps actually seen in
mobile visit data, not for every app that theoretically exists in the
metadata export. `app_metadata_lookup` from Part 1 already has both
inconsistency directions resolved, so no re-reading or re-cleaning of
`app_metadata_raw` is needed here.

```{r observed-app-ids}
mobile_app_ids_observed <- app_visits_raw %>%
  distinct(app_id)
```

## Identifying news-app candidates

Restricted to the exact category `"News, Media & Publications"`, matched
case-insensitively with `^`/`$` anchors so the whole field must match.
This avoids picking up unrelated categories that merely contain the word
"media." Built directly from `app_metadata_lookup`, which already has one
row per `app_id`, with both inconsistency directions resolved -- so this
candidate list is automatically consistent, without needing its own
deduplication logic.

```{r news-app-candidates}
app_news_lookup_needs_domain_mapping <- app_metadata_lookup %>%
  mutate(
    is_news_app_candidate = str_detect(app_cat, news_category_regex)
  ) %>%
  semi_join(mobile_app_ids_observed, by = "app_id") %>%
  filter(is_news_app_candidate) %>%
  arrange(app_n, app_id) %>%
  transmute(
    app_id,
    app_n,
    app_cat,
    is_news_app_candidate,
    n_app_ids_in_group,
    all_app_ids_in_group,

    # Filled in manually in Excel, only for genuine editorial publisher
    # apps. Bare registrable domain, e.g. "tagesschau.de", never a full
    # URL, path, protocol prefix, or "www.". Rows sharing
    # all_app_ids_in_group are the same app under different app_ids and
    # should get the same domain.
    domain = NA_character_,

    # Coding convention:
    # mapped: clear editorial publisher-domain mapping
    # no_editorial_domain: reader, browser, aggregator, platform, etc.
    # uncertain: needs additional review
    mapping_status = "uncertain",

    # Short justification, especially for uncertain or excluded apps.
    mapping_note = NA_character_
  )

cat("Unique app IDs observed in mobile visits:", nrow(mobile_app_ids_observed), "\n")
cat("Candidate news/media apps requiring manual domain mapping:",
    nrow(app_news_lookup_needs_domain_mapping), "\n")
cat("Of those, part of a multi-app_id group (already aligned in Part 1):",
    sum(app_news_lookup_needs_domain_mapping$n_app_ids_in_group > 1), "\n")
```

## Exporting the editable Excel workbook

Excel, not `.Rds`, on purpose. The whole point is filling in `domain`,
`mapping_status`, `mapping_note` by hand before any of this re-enters the
pipeline.

```{r export-workbook}
app_lookup_xlsx_path <- file.path(
  output_dir,
  "app_news_lookup_needs_domain_mapping.xlsx"
)

mapping_instructions <- tibble(
  field = c(
    "domain",
    "mapping_status",
    "mapping_note",
    "n_app_ids_in_group / all_app_ids_in_group",
    "General rule"
  ),
  instruction = c(
    "Enter the publisher's bare registrable domain, for example tagesschau.de. Do not enter https://, www., URL paths, or query parameters.",
    "Use mapped for a clear editorial publisher mapping; use no_editorial_domain for readers, browsers, aggregators, platforms, and non-journalistic apps; use uncertain when review is needed.",
    "Briefly document the reason for uncertain or excluded apps, particularly for ambiguous cases.",
    "If n_app_ids_in_group > 1, this app_id shares a name with other app_ids listed in all_app_ids_in_group (same app, different platform/store variant). All of them were already aligned to the same app_n/app_cat in app_metadata_lookup.",
    "Only rows with mapping_status = mapped and a non-missing domain will later be used to create publisher-domain proxy visits."
  )
)

openxlsx::write.xlsx(
  x = list(
    app_domain_mapping = app_news_lookup_needs_domain_mapping,
    instructions = mapping_instructions
  ),
  file = app_lookup_xlsx_path,
  overwrite = TRUE,
  asTable = TRUE
)

message(
  "Saved editable app-domain mapping workbook."
)
```

This workbook is the input to a manual coding task, already finished, can
be found under apps_websites_corrected.rds and
apps_websites_corrected_with_pc1.xlsx; merging happens later in 01d, when
`content_id` is remapped from app names to publisher domains.

# Part 3: Top-N Apps by Traffic, Independent of App-Store Category

Part 2 only ever considers apps already labelled `"News, Media &
Publications"` by the app store. That label is Bilendi's category, not a
ground truth, so an app like AOL -- which bundles mail, news, and weather
and may well be filed under a different store category (e.g.
"Productivity") -- could in principle never enter the mapping workbook,
regardless of how much traffic it has.

This section flips the logic: instead of starting from the category
label, start from traffic. The `n_top_apps` most-visited apps overall are
checked directly, regardless of `app_cat`, so a high-traffic app that was
missed by the category filter still gets a chance at manual domain
mapping. Since `app_visits` already has both metadata-inconsistency
directions resolved (Part 1), this ranking is not distorted by the same
app's traffic being split across multiple `app_id`s.

## Ranking apps by total visits

```{r topn-apps-by-traffic}
n_top_apps <- 300

app_visit_counts <- app_visits %>%
  count(app_id, app_n, app_cat, name = "n_visits") %>%
  arrange(desc(n_visits))

top_apps_by_traffic <- app_visit_counts %>%
  slice_head(n = n_top_apps)

cat("Top", n_top_apps, "apps by traffic cover",
    round(100 * sum(top_apps_by_traffic$n_visits) / sum(app_visit_counts$n_visits), 1),
    "% of all app visits\n")
```

## Which of these already went through the category-based mapping step

```{r topn-apps-already-covered}
top_apps_by_traffic <- top_apps_by_traffic %>%
  mutate(
    already_in_category_candidates = app_id %in% app_news_lookup_needs_domain_mapping$app_id
  )

cat("Of the top", n_top_apps, "apps by traffic:\n")
cat(" - already covered by the category-based candidate list:",
    sum(top_apps_by_traffic$already_in_category_candidates), "\n")
cat(" - missed by the category filter, needs a look:",
    sum(!top_apps_by_traffic$already_in_category_candidates), "\n")

top_apps_missed_by_category <- top_apps_by_traffic %>%
  filter(!already_in_category_candidates) %>%
  select(app_id, app_n, app_cat, n_visits)

print(top_apps_missed_by_category)
```

## Conclusion

Manual inspection of the top `r n_top_apps` apps by traffic (covering the
percentage of total app visits printed above) confirmed that every
plausible news-app candidate is already captured by the category-based
mapping workbook from Part 2. No further manual additions to
`app_news_lookup_needs_domain_mapping.xlsx` were necessary based on this
check.
