---
title: "Visits Raw: Combining Web, Mobile Web, and App Visits"
author: "Master's Thesis -- Media Quality / Media Diet"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = FALSE, message = TRUE)
```

# Overview

Builds one long-format `visits_raw` table by stacking three visit sources,
web visits, mobile web visits, and app visits, into a single structure with
unified columns. Kept separate from the app-visit and news-app-mapping
document because this step is narrower and more mechanical: it only
*combines* already-prepared sources, building web and mobile web visits
from scratch but reusing app visits as-is.

This is a **reduced first pass**. No timestamp parsing, no wave/group/period
variables, and no domain categories yet, those come back in a later step,
once re-evaluated on this cleaner base table.

## Outputs

| Object | Type | Role |
|---|---|---|
| `web_visits_raw.Rds` / `.RData` | Intermediate | Raw web-visit rows, pid-filtered |
| `mobile_visits_raw.Rds` / `.RData` | Intermediate | Raw mobile-web-visit rows, pid-filtered |
| `visits_raw.Rds` / `.RData` | Final | One long table stacking web, mobile web, and app visits, with a unified `content_id` key |

## The `visit_type` and `content_id` design

One generic key, `content_id`, instead of two mostly-empty columns
(`domain` for web/mobile, `app_id` for apps). Its meaning depends on
`visit_type`.

| `visit_type` | Meaning | `content_id` holds |
|---:|---|---|
| `0` | Web visit | The visited `domain` |
| `1` | Mobile web visit | The visited `domain` |
| `2` | App visit | The `app_id` |

`pageviews` (click count per view) exists only for web and mobile web
visits. It is `NA` for `visit_type == 2` by construction, not a missing-data
problem.

# Part 1: Setup

`data.table::fread()` instead of the `readr`-based helper used for app
visits: auto-detects the delimiter and is far more memory-efficient at this
table size. Filtering uses `data.table`'s `%in%` row filter rather than
`dplyr::semi_join()`, which is more memory-hungry at this scale.

```{r libraries}
library(data.table)
library(dplyr)
```

```{r paths-and-helper, include=TRUE}

project_root <- "~/Desktop/GitHub/DoesMediaQualityMatter"
code_dir <- file.path(project_root, "Code", "prep")
pid_dir <- file.path(project_root, "Output", "00_setup")
output_dir <- file.path(project_root, "Output", "01_visits")
dir.create(output_dir, showWarnings = FALSE, recursive = TRUE)
#data_dir <- ""

# Saves as .Rds (readRDS() reuse) and .RData (load(), object under its own
# name, matching how df1/df2/df3 are loaded elsewhere).
save_both <- function(obj, name, dir = output_dir) {
  assign(name, obj)
  saveRDS(obj, file.path(dir, paste0(name, ".Rds")))
  save(list = name, file = file.path(dir, paste0(name, ".RData")))
  message("Saved ", name)
}
kept_cols <- c("pid", "visit_type", "content_id", "used_at", "duration", "pageviews")
```

```{r paths-and-helper-invis, include=FALSE}

data_dir <- "~/Desktop/Masterarbeit/Data/download-2"




```

Valid-participant reference loaded once, up front, so every source is
restricted right after import rather than only at the end.

```{r valid-pids, include=TRUE}
pid_lookup_february <- readRDS(file.path(pid_dir, "pid_lookup_february.Rds"))
valid_pids <- as.character(pid_lookup_february$pid)
```

# Part 2: Raw File Paths

Same 1 April 2023 onward restriction as the app-visit document, for
consistency across the whole visits pipeline stage.

```{r file-paths, include=TRUE}
web_visit_paths <- c(
  file.path(data_dir, "original/2023-04-01-to-2023-04-15-exports/web_visits.csv"),
  file.path(data_dir, "fixed/2023-04-15-to-2023-05-01-exports/web_visits.csv"),
  file.path(data_dir, "original/2023-05-01-to-2023-05-15-exports/web_visits.csv"),
  file.path(data_dir, "original/2023-05-15-to-2023-06-01-exports/web_visits.csv"),
  file.path(data_dir, "original/2023-06-01-to-2023-06-15-exports/web_visits.csv"),
  file.path(data_dir, "original/2023-06-15-to-2023-07-01-exports/web_visits.csv"),
  file.path(data_dir, "original/2023-07-01-to-2023-07-15-exports/web_visits.csv"),
  file.path(data_dir, "original/2023-07-15-to-2023-08-01-exports/web_visits.csv")
) |> unique()

mobile_visit_paths <- c(
  file.path(data_dir, "original/2023-04-01-to-2023-04-15-exports/mobile_visits.csv"),
  file.path(data_dir, "fixed/2023-04-15-to-2023-05-01-exports/mobile_visits.csv"),
  file.path(data_dir, "original/2023-05-01-to-2023-05-15-exports/mobile_visits.csv"),
  file.path(data_dir, "original/2023-05-15-to-2023-06-01-exports/mobile_visits.csv"),
  file.path(data_dir, "original/2023-06-01-to-2023-06-15-exports/mobile_visits.csv"),
  file.path(data_dir, "original/2023-06-15-to-2023-07-01-exports/mobile_visits.csv"),
  file.path(data_dir, "original/2023-07-01-to-2023-07-15-exports/mobile_visits.csv"),
  file.path(data_dir, "original/2023-07-15-to-2023-08-01-exports/mobile_visits.csv")
) |> unique()
```

## A leaner, `data.table`-based file reader

Each file is trimmed to only the needed columns
(`pid`/`domain`/`used_at`/`duration`, plus `pageviews` when present) right
at read time, so a full-width raw table is never materialised in memory.

```{r read-helper}
read_visit_files <- function(file_paths, extra_cols = character(0)) {
  rbindlist(lapply(file_paths, function(fp) {
    message("Reading: ", fp)
    dt <- fread(fp, showProgress = FALSE)
    if ("p_id" %in% names(dt) && !"pid" %in% names(dt)) setnames(dt, "p_id", "pid")
    if (!"pid" %in% names(dt)) {
      stop("No pid column found in file: ", fp, "\nColumns detected: ", paste(names(dt), collapse = ", "))
    }
    # pid can be read as integer64 for large PIDs. Converting here, right
    # after read, guarantees every downstream %in% filter compares character
    # against character, regardless of which source file this came from.
    dt[, pid := as.character(pid)]
    want <- intersect(c("pid", "domain", "used_at", "duration", extra_cols), names(dt))
    dt[, ..want]
  }), fill = TRUE)
}
```

# Part 3: Reading Web Visits

Restricted to valid participants right after import; the pid-filtered raw
table is saved for transparency and auditing, then its memory is freed as
soon as the trimmed `web_visits` table exists.

```{r web-visits, include=FALSE}
web_visits_raw <- read_visit_files(web_visit_paths, extra_cols = "pageviews")
web_visits_raw <- web_visits_raw[pid %in% valid_pids]
save_both(web_visits_raw, "web_visits_raw")

web_visits <- web_visits_raw %>%
  mutate(pid = as.character(pid), visit_type = 0L, content_id = as.character(domain)) %>%
  select(all_of(kept_cols))



rm(web_visits_raw); gc()
```

# Part 4: Reading Mobile Web Visits

`mobile_visits.csv` holds only domain-based mobile *web* visits. App
visits are a separate source, loaded from the already-built `app_visits`
table in Part 5, not read again from raw files here.

```{r mobile-visits, include=FALSE}
mobile_visits_raw <- read_visit_files(mobile_visit_paths, extra_cols = "pageviews")
mobile_visits_raw <- mobile_visits_raw[pid %in% valid_pids]
save_both(mobile_visits_raw, "mobile_visits_raw")

mobile_visits <- mobile_visits_raw %>%
  mutate(pid = as.character(pid), visit_type = 1L, content_id = as.character(domain)) %>%
  select(all_of(kept_cols))


rm(mobile_visits_raw); gc()
```

# Part 5: Loading App Visits

`app_visits` was already built and pid-filtered in the app-visits step, so
no further pid filtering is needed here. Only reshaped to match the same
`kept_cols` structure as the web and mobile web tables.

```{r app-visits, include=FALSE}
app_visits_path <- file.path(output_dir, "app_visits.Rds")
```

```{r app-visits-load}
app_visits <- readRDS(app_visits_path) %>%
  mutate(pid = as.character(pid), visit_type = 2L, content_id = as.character(app_id), pageviews = NA) %>%
  select(all_of(kept_cols))
```

# Part 6: Combining All Three Sources

All three tables are already trimmed to identical `kept_cols`, so combining
is a pure row-stack with no further column selection.

```{r combine}
visits_raw <- bind_rows(web_visits, mobile_visits, app_visits)
```

## Basic import diagnostics

```{r import-diagnostics}
cat("Rows (web):", nrow(web_visits),
    "| Rows (mobile web):", nrow(mobile_visits),
    "| Rows (app):", nrow(app_visits),
    "| Rows (combined):", nrow(visits_raw), "\n")
cat("Unique pids (combined):", n_distinct(visits_raw$pid), "\n")
print(table(visits_raw$visit_type, useNA = "ifany"))
cat("Missing content_id:", sum(is.na(visits_raw$content_id) | visits_raw$content_id == ""), "\n")
cat("Missing pageviews (expected: all visit_type == 2):", sum(is.na(visits_raw$pageviews)), "\n")
```

## Diagnostic: restricting to `in_experiment`

Pure diagnostic, `visits_raw` itself is not modified. Checks how many
participants and rows would remain under an additional
`in_experiment == TRUE` filter (experimental-wave participants, not just
the February baseline population). Printed as a comparison rather than
applied, since different downstream analyses may legitimately want either
population.

```{r experiment-diagnostic}
experiment_pids <- pid_lookup_february$pid[pid_lookup_february$in_experiment == TRUE]

n_pids_february   <- n_distinct(visits_raw$pid)
n_pids_experiment <- length(intersect(unique(visits_raw$pid), experiment_pids))

n_rows_february   <- nrow(visits_raw)
n_rows_experiment <- sum(visits_raw$pid %in% experiment_pids)

cat("Pids, February filter (current):", n_pids_february, "\n")
cat("Pids, additionally in_experiment == TRUE:", n_pids_experiment, "\n")
cat("Rows, February filter (current):", n_rows_february, "\n")
cat("Rows, additionally in_experiment == TRUE:", n_rows_experiment, "\n")
```

# Part 7: Saving

```{r save-final}
glimpse(visits_raw)
save_both(visits_raw, "visits_raw")
```

## Comment

`visits_raw` at this stage has no parsed timestamp, no wave/period
variable, and no domain category. Do not expect to filter by wave or
category directly on `visits_raw`. Those variables are added in the next
pipeline stage, which reads this exact `visits_raw` object as its starting
point.


# Part 8: Flagging Overall Tracking Activity

`df1`/`df2`/`df3` have similar activity flags (`activity_visits_yn`,
`bilendi_visits_yn`), but only for the 791 experiment participants, and
only within each wave's own surveillance/intervention windows, not across
the full tracking period. No ready-made flag exists for the complete
February baseline.

`was_active` fills that gap: TRUE if a participant has at least one
tracked web, mobile web, or app visit anywhere in the tracking period,
built directly from the pid sets computed in the pre-merge crosstab
(Part 6) and joined onto `panelist_metadata_final`.

```{r load panelist_metadata, include=FALSE}

panelist_metadata_final <- readRDS(
  "~/Desktop/Masterarbeit/MA_FINAL/Output/00_setup/panelist_metadata_final.rds"
)
```


```{r was-active}
pids_web    <- unique(web_visits$pid)
pids_mobile <- unique(mobile_visits$pid)
pids_app    <- unique(app_visits$pid)

pids_with_any_activity <- union(union(pids_web, pids_mobile), pids_app)



panelist_metadata_final <- panelist_metadata_final %>%
  mutate(was_active = pid %in% pids_with_any_activity)

cat("was_active == TRUE:", sum(panelist_metadata_final$was_active), "\n")
cat("was_active == FALSE:", sum(!panelist_metadata_final$was_active), "\n")
```

Cross-check against experiment participation: experiment participation
required an internet connection and working tracking, so `was_active`
should be a superset of `in_experiment`. Any `in_experiment == TRUE` with
`was_active == FALSE` would flag a data problem (e.g. a pid type mismatch
like the earlier `integer64` issue) rather than a genuine case.

```{r was-active-crosscheck}
activity_vs_experiment <- table(
  was_active = panelist_metadata_final$was_active,
  in_experiment = panelist_metadata_final$in_experiment
)
print(activity_vs_experiment)
```