---
title: "Visit Periods, Treatment Group, and Domain Categories"
author: "Master's Thesis -- Media Quality / Media Diet"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = FALSE, message = TRUE)
```

# Overview

One continuous transformation of the reduced `visits_raw` table: first
adding a parsed timestamp, treatment group, and person-specific period
label (Part 1), then domain/app categories plus a unified `is_news` flag
(Part 2). Part 2 requires the exact columns Part 1 produces, so the two are
not useful read in isolation.

## Outputs

| Object | New columns |
|---|---|
| `visits_raw_period.Rds` / `.RData` | `used_at_dt`, `used_date`, `group`, `period` |
| `visits_raw_period_categories.Rds` / `.RData` | `category_1`, `category_2`, `category_3`, `app_cat`, `is_news` |

## Why period is person-specific, not calendar-fixed

A shared calendar boundary for all participants would mislabel `pre`,
`during`, or `post` for many people, since they joined the study at
different points and some skipped a wave entirely. `period` is therefore
defined relative to *that specific person's own* `survey_start`/
`survey_end` in each wave they took part in.

| Period label | Meaning |
|---|---|
| `pre` | Before this person's first `survey_start`, across all waves they joined |
| `during_w1` / `during_w2` / `during_w3` | Within that wave's `[survey_start, survey_end]` window |
| `between_1_2` / `between_2_3` | Gap between two consecutive waves this person took part in |
| `between_1_3` | Gap between Wave 1 and Wave 3, for someone who skipped Wave 2 |
| `post` | After this person's last `survey_end`, across all waves they joined |
| `NA` | No wave participation at all (February-only baseline participant) |

# Part 1: Adding Group and Period

## Setup

```{r libraries}
library(dplyr)
library(tidyr)
library(lubridate)
library(readr)
library(stringr)
library(purrr)
```

```{r paths-and-helper, include=FALSE}
project_root <- "~/Desktop/GitHub/DoesMediaQualityMatter"
data_dir <- "~/Desktop/Masterarbeit/Data"

save_both <- function(obj, name, dir = output_dir) {
  assign(name, obj)
  saveRDS(obj, file.path(dir, paste0(name, ".Rds")))
  save(list = name, file = file.path(dir, paste0(name, ".RData")))
  message("Saved ", name)
}
```


```{r}
#project_root <- "DoesMediaQualityMatter"
code_dir <- file.path(project_root, "Code", "prep")
pid_dir <- file.path(project_root, "Output", "00_setup")
output_dir <- file.path(project_root, "Output", "01_visits")
#data_dir <- ""

# Saves as .Rds (readRDS() reuse) and .RData (load()
save_both <- function(obj, name, dir = output_dir) {
  assign(name, obj)
  saveRDS(obj, file.path(dir, paste0(name, ".Rds")))
  save(list = name, file = file.path(dir, paste0(name, ".RData")))
  message("Saved ", name)
}

```

## Loading inputs

Loads `visits_raw`, the participant lookup, and the three wave-level
dataframes, needed here purely to recover each person's survey timing.

```{r load-inputs, include=FALSE}
visits_raw <- readRDS(file.path(output_dir, "visits_raw.Rds"))
pid_lookup_february <- readRDS(file.path(pid_dir, "pid_lookup_february.Rds")) %>%
  mutate(pid = as.character(pid))

if (!"group" %in% names(pid_lookup_february)) {
  stop("pid_lookup_february is missing the 'group' column. Add it first.")
}

load(file.path(data_dir, "df1_final_ac.Rdata")) # creates df1
load(file.path(data_dir, "df2_final_ac.Rdata")) # creates df2
load(file.path(data_dir, "df3_final_ac.Rdata")) # creates df3

df1 <- df1 %>% mutate(pid = as.character(pid))
df2 <- df2 %>% mutate(pid = as.character(pid))
df3 <- df3 %>% mutate(pid = as.character(pid))
```

## Parsing `used_at` into a proper local timestamp

`used_at` is already local (Europe/Berlin) clock time as a plain character
string, so it is parsed directly with `tz = "Europe/Berlin"`, no
timezone-shift correction needed.

```{r parse-used-at}
visits_raw <- visits_raw %>%
  mutate(
    used_at_dt = as.POSIXct(used_at, format = "%Y-%m-%d %H:%M:%S", tz = "Europe/Berlin"),
    used_date = as.Date(used_at_dt)
  )
```

## Handling the daylight-saving-time gap

Clocks jumped forward on 26 March 2023, so any timestamp in the
non-existent 02:00 to 03:00 window fails to parse and becomes `NA`. Those
rows are snapped to the moment clocks resumed (03:00:00), consistent with
earlier handling in the pipeline, rather than dropped outright.

```{r dst-fix}
visits_raw <- visits_raw %>%
  mutate(
    dst_problem = is.na(used_at_dt) & grepl("^2023-03-26", used_at),
    used_at_dt = case_when(
      dst_problem ~ as.POSIXct("2023-03-26 03:00:00", tz = "Europe/Berlin"),
      TRUE ~ used_at_dt
    ),
    used_date = case_when(
      dst_problem ~ as.Date("2023-03-26"),
      TRUE ~ used_date
    )
  )

cat("Rows with unparseable used_at (dropped):", sum(is.na(visits_raw$used_at_dt)), "\n")
visits_raw <- visits_raw %>% filter(!is.na(used_at_dt))
```

## Parsing each wave's survey window

Waves 1 and 3 store `start_date`/`final_date` as character timestamps. Wave 2 stores them as Excel-style numeric day counts, needing a separate numeric-to-POSIXct conversion via the Excel epoch (`"1899-12-30"`). Here I need to use the wave specific files, because they contain the survey start and end times.

```{r parse-survey-windows}
df1 <- df1 %>%
  mutate(
    survey_start = as.POSIXct(start_date, format = "%Y-%m-%d %H:%M:%S", tz = "Europe/Berlin"),
    survey_end   = as.POSIXct(final_date, format = "%Y-%m-%d %H:%M:%S", tz = "Europe/Berlin")
  )

df2 <- df2 %>%
  mutate(
    start_date_num = as.numeric(start_date),
    final_date_num = as.numeric(final_date),
    survey_start = as.POSIXct(start_date_num * 86400, origin = "1899-12-30", tz = "Europe/Berlin"),
    survey_end   = as.POSIXct(final_date_num * 86400, origin = "1899-12-30", tz = "Europe/Berlin")
  ) %>%
  select(-start_date_num, -final_date_num)

df3 <- df3 %>%
  mutate(
    survey_start = as.POSIXct(start_date, format = "%Y-%m-%d %H:%M:%S", tz = "Europe/Berlin"),
    survey_end   = as.POSIXct(final_date, format = "%Y-%m-%d %H:%M:%S", tz = "Europe/Berlin")
  )
```

## Building per-participant, per-wave survey windows

All three waves' windows are stacked into one long table first, checked
for logically invalid windows (`survey_start > survey_end`, which should
never happen), then reshaped to wide (one row per participant) before
joining to `visits_raw`. Reshaping to wide first keeps the later join to
the much larger visits table strictly one-to-one, so no visit row can be
duplicated by a many-to-many join on `pid`.

```{r build-windows}
pid_wave_windows <- bind_rows(
  df1 %>% distinct(pid, survey_start, survey_end) %>% mutate(wave = 1L),
  df2 %>% distinct(pid, survey_start, survey_end) %>% mutate(wave = 2L),
  df3 %>% distinct(pid, survey_start, survey_end) %>% mutate(wave = 3L)
) %>%
  filter(!is.na(survey_start), !is.na(survey_end)) %>%
  arrange(pid, survey_start)

cat("Rows in pid_wave_windows:", nrow(pid_wave_windows), "\n")
cat("Unique pids with at least one survey window:", n_distinct(pid_wave_windows$pid), "\n")

invalid_windows <- pid_wave_windows %>% filter(survey_start > survey_end)
cat("Rows with survey_start > survey_end (should be 0):", nrow(invalid_windows), "\n")

pid_period_boundaries <- pid_wave_windows %>%
  group_by(pid) %>%
  summarise(
    first_survey_start = min(survey_start),
    last_survey_end = max(survey_end),
    .groups = "drop"
  )

pid_wave_wide <- pid_wave_windows %>%
  select(pid, wave, survey_start, survey_end) %>%
  pivot_wider(
    id_cols = pid,
    names_from = wave,
    values_from = c(survey_start, survey_end),
    names_glue = "w{wave}_{.value}"
  )
```

## Adding group and classifying each visit into a period

```{r add-group-and-period}
n_before <- nrow(visits_raw)

visits_raw <- visits_raw %>%
  left_join(pid_lookup_february %>% select(pid, group), by = "pid") %>%
  left_join(pid_period_boundaries, by = "pid") %>%
  left_join(pid_wave_wide, by = "pid") %>%
  mutate(
    period = case_when(
      is.na(first_survey_start) ~ NA_character_,

      used_at_dt < first_survey_start ~ "pre",

      !is.na(w1_survey_start) & used_at_dt >= w1_survey_start & used_at_dt <= w1_survey_end ~ "during_w1",
      !is.na(w2_survey_start) & used_at_dt >= w2_survey_start & used_at_dt <= w2_survey_end ~ "during_w2",
      !is.na(w3_survey_start) & used_at_dt >= w3_survey_start & used_at_dt <= w3_survey_end ~ "during_w3",

      !is.na(w1_survey_end) & !is.na(w2_survey_start) &
        used_at_dt > w1_survey_end & used_at_dt < w2_survey_start ~ "between_1_2",
      !is.na(w2_survey_end) & !is.na(w3_survey_start) &
        used_at_dt > w2_survey_end & used_at_dt < w3_survey_start ~ "between_2_3",
      !is.na(w1_survey_end) & is.na(w2_survey_start) & !is.na(w3_survey_start) &
        used_at_dt > w1_survey_end & used_at_dt < w3_survey_start ~ "between_1_3",

      used_at_dt > last_survey_end ~ "post",
      TRUE ~ NA_character_
    )
  ) %>%
  select(-starts_with("w1_"), -starts_with("w2_"), -starts_with("w3_"),
         -first_survey_start, -last_survey_end, -dst_problem)

cat("Rows before vs. after period/group join (should match):", n_before, "vs.", nrow(visits_raw), "\n")
cat("Distribution of period:\n")
print(table(visits_raw$period, useNA = "ifany"))
cat("Distribution of group:\n")
print(table(visits_raw$group, useNA = "ifany"))
```

## Saving

```{r save-period , eval=FALSE }
glimpse(visits_raw)
save_both(visits_raw, "visits_raw_period")
```

# Part 2: Adding Domain and App Categories

```{r}
visits_raw_period <- visits_raw
```

## Reading and cleaning domain categories

Category files can list up to three comma-separated category labels per
domain, split here into three separate columns, with a small set of known
label corrections (typos and inconsistent naming across export batches).

```{r read-categories, include=FALSE}
category_paths <- c(
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-04-01-to-2023-04-15-exports/categories.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/fixed/2023-04-15-to-2023-05-01-exports/categories.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-05-01-to-2023-05-15-exports/categories.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-05-15-to-2023-06-01-exports/categories.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-06-01-to-2023-06-15-exports/categories.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-06-15-to-2023-07-01-exports/categories.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-07-01-to-2023-07-15-exports/categories.csv",
  "/Users/e/Desktop/Masterarbeit/Data/download-2/original/2023-07-15-to-2023-08-01-exports/categories.csv"
) |> unique()
```

```{r read-categories-fn, include=FALSE}
read_category_file <- function(path) {
  message("Reading category file.")
  tryCatch({
    tmp <- read_delim(path, delim = ",", col_names = c("domain", "category"),
                       show_col_types = FALSE, progress = FALSE)
    if (ncol(tmp) == 1) {
      tmp <- read_delim(path, delim = ";", col_names = c("domain", "category"),
                         show_col_types = FALSE, progress = FALSE)
    }
    tmp
  }, error = function(e) {
    read_delim(path, delim = ";", col_names = c("domain", "category"),
               show_col_types = FALSE, progress = FALSE)
  })
}

categories_raw <- map_dfr(category_paths, read_category_file)

categories_final <- categories_raw %>%
  mutate(domain = as.character(domain), category = as.character(category)) %>%
  filter(!is.na(domain), domain != "") %>%
  distinct(domain, category, .keep_all = TRUE) %>%
  separate(category, into = c("category_1", "category_2", "category_3"),
           sep = ",", extra = "drop", fill = "right") %>%
  mutate(across(starts_with("category_"), str_trim))

category_corrections <- c(
  "sport" = "sports",
  "newsandmedi" = "newsandmedia",
  "food" = "foodandrecipes",
  "foodfoodandrecipes" = "foodandrecipes"
)

recode_category <- function(x) {
  recoded <- category_corrections[x]
  ifelse(is.na(recoded), x, recoded)
}

categories_final <- categories_final %>%
  mutate(
    category_1 = recode_category(category_1),
    category_2 = recode_category(category_2),
    category_3 = recode_category(category_3)
  )

cat("Rows in categories_final (unique domains):", nrow(categories_final), "\n")
```

## Merging domain categories

Join key is `content_id = domain`, so this only affects `visit_type` 0
(web) and 1 (mobile web) rows. App visits (`visit_type == 2`) get their
categories from a separate lookup next.

```{r merge-domain-categories}
n_before <- nrow(visits_raw_period)

visits_raw_period <- visits_raw_period %>%
  left_join(
    categories_final %>% select(domain, category_1, category_2, category_3),
    by = c("content_id" = "domain")
  )

cat("Rows before vs. after domain category join (should match):", n_before, "vs.", nrow(visits_raw_period), "\n")
cat("visit_type 0/1 rows with no category match:",
    sum(visits_raw_period$visit_type %in% c(0L, 1L) & is.na(visits_raw_period$category_1)), "\n")
```

## Merging app categories

`app_cat` already exists inside the `app_visits` table. A small distinct
lookup is re-derived from it here rather than depending on that object
still being loaded in the current session, keeping this step runnable on
its own as long as `app_visits.Rds` exists on disk.

```{r merge-app-categories, include=FALSE}
app_visits_path <- file.path(output_dir, "app_visits.Rds")
if (!file.exists(app_visits_path)) {
  stop("app_visits.Rds not found at ", app_visits_path, ". Build it first.")
}
```

```{r merge-app-categories-run}
app_cat_lookup <- readRDS(app_visits_path) %>%
  mutate(app_id = as.character(app_id)) %>%
  distinct(app_id, app_cat)

visits_raw_period <- visits_raw_period %>%
  left_join(app_cat_lookup, by = c("content_id" = "app_id"))

cat("visit_type == 2 rows with no app_cat match:",
    sum(visits_raw_period$visit_type == 2L & is.na(visits_raw_period$app_cat)), "\n")
```

## Building a unified `is_news` flag

Bridges two structurally different category vocabularies, Webshrinker's
domain categories and the app-store category labels, but only for this
single boolean, not for the underlying category systems themselves.
`category_1`/`category_2`/`category_3` and `app_cat` stay as two separate,
un-harmonised vocabularies; `is_news` is the only variable meant to be
comparable across all three `visit_type` values.

```{r is-news-flag}
visits_raw_period <- visits_raw_period %>%
  mutate(
    is_news_domain = visit_type %in% c(0L, 1L) & (
      category_1 == "newsandmedia" |
      category_2 == "newsandmedia" |
      category_3 == "newsandmedia"
    ),
    is_news_app = visit_type == 2L & str_detect(
      app_cat,
      regex("^News,\\s*Media\\s*&\\s*Publications$", ignore_case = TRUE)
    ),
    is_news = coalesce(is_news_domain, FALSE) | coalesce(is_news_app, FALSE)
  ) %>%
  select(-is_news_domain, -is_news_app)

cat("Distribution of is_news by visit_type:\n")
print(table(visits_raw_period$visit_type, visits_raw_period$is_news, useNA = "ifany"))
```


## Saving

```{r save-categories}
glimpse(visits_raw_period)
save_both(visits_raw_period, "visits_raw_period_categories")
```

