---
title: "Manual Review Export: Domain-Level is_news Flag"
author: "Master's Thesis -- Media Quality / Media Diet"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = TRUE, message = TRUE)
```

# Overview

Builds the domain-level base table used for manual `is_news` reclassification.
Four things, in this order:

1. Replace app identifiers in `content_id` with readable app names
2. Replace those app names with their mapped publisher domain, where the
   manual review found one
3. Attach the external PC1 quality score, with integrity checks on the lookup
4. Collapse to one row per domain and add the pre- vs. experiment-window
   visit counts

`is_news` itself is never changed here. This script only produces the base
table that `01e` reads back in, reviews, and turns into `is_news_corrected`.

## Why app traffic is folded into domains first

`content_id` holds three different kinds of value depending on `visit_type`:
a domain for web rows, an `app_id` for app rows as delivered, and after the
two remaps below, a publisher domain for those app rows that have one. Folding
apps into their publisher domain before any aggregation is what allows a
domain's app traffic and web traffic to count toward the same row. Without it,
a newspaper read mostly through its app would rank far below its true traffic
in the Top-N cutoff that drives the manual review.

`visit_type` is never modified by either remap. A row that arrived as
`visit_type == 2` stays `visit_type == 2` even after `content_id` becomes a
domain, so the channel a domain's traffic came through is never lost. It is
preserved per domain as `visit_types_observed`.

| Step | `content_id` before | `content_id` after | Lookup | Key |
|---|---|---|---|---|
| 1 | `app_id` | `app_n` (readable name) | `app_metadata_lookup` | `app_id`, exact |
| 2 | `app_n` | publisher domain | `apps_websites_corrected_with_pc1.xlsx` | `app_n`, case- and whitespace-normalised |

Step 2 resolves by normalised name rather than by `app_id` on purpose. Several
apps ship as more than one `app_id` (typically an iOS and an Android build).
If the reviewer coded only one of the two, resolving by `app_id` would leave
the other unmapped even though the same app is already mapped under its
sibling identifier. Resolving by name lets every `app_id` sharing a name
inherit the same single domain. Apps coded `no_editorial_domain` or
`uncertain` are deliberately left as `app_n`, never force-mapped.

## Outputs

| Object | Level | Role |
|---|---|---|
| `visits_with_apps_as_domains.Rds` / `.RData` | Visit | `visits_raw_period` with app rows folded into their publisher domain |
| `all_unique_domains_visited.csv` | Domain | One row per domain: traffic totals, channels, category, `is_news`, PC1 |
| `domain_reclass_base_with_apps_as_domains.Rds` / `.RData` | Domain | The above plus pre- and experiment-window visit counts; consumed by `01e` |
| `pc1_lookup_conflicts.csv` | Domain | Domains carrying more than one PC1 value in the source file, if any |
| `domains_mixed_is_news.csv` | Domain | Domains whose visit rows disagree on `is_news`, if any |

The Top-N review workbook is exported in `01e`, not here.

# Part 1: Setup

```{r libraries}
library(dplyr)
library(readr)
library(stringr)
library(tidyr)
library(readxl)
```

```{r paths-config-data, include=FALSE}

data_dir     <- "~/Desktop/Masterarbeit/Data"

```


```{r paths-config, include=TRUE}
#data_dir     <- ""
project_root <- "~/Desktop/GitHub/DoesMediaQualityMatter"
output_dir <- file.path(project_root, "Output", "01_visits")

visits_path       <- file.path(output_dir, "visits_raw_period_categories.Rds")
app_metadata_path <- file.path(output_dir, "app_metadata_lookup.Rds")
app_mapping_path  <- file.path(output_dir, "apps_websites_corrected_with_pc1.xlsx")
pc1_path          <- file.path(data_dir, "domain-pc1_with_de.csv")
```



```{r helpers}
# .Rds for readRDS() reuse, .RData so the object loads under its own name,
# matching how df1/df2/df3 are loaded elsewhere in the pipeline.
save_both <- function(obj, name, dir = output_dir) {
  assign(name, obj)
  saveRDS(obj, file.path(dir, paste0(name, ".Rds")))
  save(list = name, file = file.path(dir, paste0(name, ".RData")))
}

# Both remap steps do the same thing: for app rows only, look up the current
# content_id in a named vector and overwrite it where a match exists. Rows
# without a match keep what they have rather than becoming NA.
remap_app_content_id <- function(visits, map, label, normalise = FALSE) {
  is_app <- visits$visit_type == 2L
  key <- if (normalise) str_squish(str_to_lower(visits$content_id)) else visits$content_id
  hit <- is_app & key %in% names(map)

  visits$content_id[hit] <- unname(map[key[hit]])

  cat(label, "\n  app rows:", sum(is_app),
      "| remapped:", sum(hit),
      "| left unchanged:", sum(is_app) - sum(hit), "\n")
  visits
}
```

```{r load-visits}
visits <- readRDS(visits_path)
cat("Visit rows:", nrow(visits), "| distinct content_id:", n_distinct(visits$content_id), "\n")
```

# Part 2: App Identifiers to App Names

```{r remap-app-id}
app_name_map <- readRDS(app_metadata_path) %>%
  mutate(across(c(app_id, app_n), as.character)) %>%
  distinct(app_id, .keep_all = TRUE) %>%
  { setNames(.$app_n, .$app_id) }

visits <- remap_app_content_id(visits, app_name_map, "Step 1: app_id -> app_n")
```

# Part 3: App Names to Publisher Domains

Only rows with `mapping_status == "checked"` and a non-missing `news_domain`
are applied. Names are normalised for whitespace and case only, so that "AOL"
and "AOL " are treated as one name; this is formatting cleanup, not a semantic
rewrite.

If the same normalised name carries two different `news_domain` values across
its `app_id` rows, that is a coding conflict in the workbook, not something to
resolve silently. The script stops and names the offending entries.

```{r read-app-mapping}
app_mapping <- read_excel(app_mapping_path) %>%
  mutate(across(c(app_id, app_n, news_domain, mapping_status), as.character),
         app_n_key = str_squish(str_to_lower(app_n)))

cat("Rows in mapping workbook:", nrow(app_mapping), "\n")
print(table(app_mapping$mapping_status, useNA = "ifany"))

checked <- app_mapping %>%
  filter(mapping_status == "checked", !is.na(news_domain), news_domain != "")

conflicts <- checked %>%
  distinct(app_n_key, news_domain) %>%
  count(app_n_key) %>%
  filter(n > 1)

if (nrow(conflicts) > 0) {
  stop(nrow(conflicts), " app name(s) map to more than one news_domain: ",
       paste(conflicts$app_n_key, collapse = ", "),
       ". Resolve these in the workbook before proceeding.")
}

app_domain_map <- checked %>%
  distinct(app_n_key, .keep_all = TRUE) %>%
  { setNames(.$news_domain, .$app_n_key) }

cat("Distinct app names with a usable checked domain:", length(app_domain_map),
    "| app_ids directly checked:", n_distinct(checked$app_id),
    "| app_ids covered once aligned by name:",
    n_distinct(app_mapping$app_id[app_mapping$app_n_key %in% names(app_domain_map)]), "\n")
```

```{r remap-app-domain}
visits_with_apps_as_domains <- remap_app_content_id(
  visits, app_domain_map, "Step 2: app_n -> publisher domain", normalise = TRUE
)

save_both(visits_with_apps_as_domains, "visits_with_apps_as_domains")
```

# Part 4: PC1 Domain Quality Scores

Loaded once and joined onto the domain table below, so the manual review in
`01e` can already see which domains carry an external score.

Two integrity checks before the join. Both matter because a domain-level
lookup that is not one row per domain fans out the join and silently
duplicates domains in every downstream table.

```{r load-pc1}
pc1_raw <- read_csv2(pc1_path, show_col_types = FALSE) %>%
  mutate(domain = as.character(domain), pc1 = as.numeric(pc1)) %>%
  filter(!is.na(domain), domain != "")

# Check 1: does any domain carry more than one distinct PC1 value?
pc1_conflicts <- pc1_raw %>%
  distinct(domain, pc1) %>%
  count(domain) %>%
  filter(n > 1)

if (nrow(pc1_conflicts) > 0) {
  write_csv(pc1_raw %>% semi_join(pc1_conflicts, by = "domain") %>% arrange(domain),
            file.path(output_dir, "pc1_lookup_conflicts.csv"))
  stop(nrow(pc1_conflicts), " domain(s) carry more than one PC1 value in ",
       basename(pc1_path), ". Written to pc1_lookup_conflicts.csv; resolve before proceeding.")
}

domain_pc1 <- pc1_raw %>% distinct(domain, .keep_all = TRUE) %>% dplyr::select(domain, pc1)

cat("Domains with a PC1 score:", nrow(domain_pc1), "\n")
```

Suffix composition of the lookup, so the manually added German-domain entries
are visible as a count rather than an assumption. Any change to the coverage of
`.de` domains propagates directly into how much of German news consumption
carries a quality score at all.

```{r pc1-suffix-profile}
domain_pc1 %>%
  mutate(suffix = str_extract(domain, "\\.[a-z]+$")) %>%
  count(suffix, sort = TRUE) %>%
  slice_head(n = 12)
```

# Part 5: Domain-Level Totals, One Row per Domain

Grouped by `content_id` alone, not by `visit_type` as well, so a domain
reached through more than one channel sums to a single row with its full
traffic instead of splitting across rows and distorting the traffic ranking
that drives the Top-N cutoff.

`visit_type` survives as a comma-joined `visit_types_observed` column, computed
separately from the totals. `category_1/2/3`, `app_cat` and `is_news` can
differ across rows for the same `content_id` — across export batches, and now
also because a remapped app row and a web row for the same domain may disagree.
Each is resolved to its most frequently observed value, which keeps the table
one row per domain without a second many-to-many join.

```{r mixed-is-news-check}
# is_news disagreement within a domain is worth seeing rather than silently
# majority-voting away, since it is a direct consequence of folding app traffic
# into web domains.
mixed_is_news <- visits_with_apps_as_domains %>%
  distinct(content_id, is_news) %>%
  count(content_id) %>%
  filter(n > 1)

cat("Domains whose visit rows disagree on is_news:", nrow(mixed_is_news), "\n")

if (nrow(mixed_is_news) > 0) {
  write_csv(
    visits_with_apps_as_domains %>%
      semi_join(mixed_is_news, by = "content_id") %>%
      count(content_id, visit_type, is_news, name = "n_rows") %>%
      arrange(content_id),
    file.path(output_dir, "domains_mixed_is_news.csv")
  )
}
```

```{r domain-level-totals}
# One helper for the three "most frequent value per domain" resolutions.
modal_by_domain <- function(df, cols) {
  df %>%
    count(across(all_of(c("content_id", cols))), name = "n_occurrences") %>%
    group_by(content_id) %>%
    slice_max(n_occurrences, n = 1, with_ties = FALSE) %>%
    ungroup() %>%
    dplyr::select(all_of(c("content_id", cols)))
}

all_unique_domains_visited <- visits_with_apps_as_domains %>%
  count(content_id, name = "n_visits_total") %>%
  left_join(
    visits_with_apps_as_domains %>%
      filter(visit_type %in% c(0L, 1L)) %>%
      count(content_id, name = "n_visits_excl_app"),
    by = "content_id") %>%
  left_join(modal_by_domain(visits_with_apps_as_domains, "is_news"), by = "content_id") %>%
  left_join(modal_by_domain(visits_with_apps_as_domains,
                            c("category_1", "category_2", "category_3", "app_cat")),
            by = "content_id") %>%
  left_join(
    visits_with_apps_as_domains %>%
      group_by(content_id) %>%
      summarise(visit_types_observed = paste(sort(unique(visit_type)), collapse = ", "),
                .groups = "drop"),
    by = "content_id") %>%
  mutate(n_visits_excl_app = replace_na(n_visits_excl_app, 0L)) %>%
  rename(domain = content_id) %>%
  left_join(domain_pc1, by = "domain", relationship = "many-to-one") %>%
  dplyr::select(domain, category_1, category_2, category_3, app_cat, is_news,
                n_visits_total, n_visits_excl_app, visit_types_observed, pc1) %>%
  arrange(desc(n_visits_total))

# One row per domain is what every downstream join assumes. Assert it.
stopifnot(n_distinct(all_unique_domains_visited$domain) == nrow(all_unique_domains_visited))

write_csv(all_unique_domains_visited, file.path(output_dir, "all_unique_domains_visited.csv"))

tibble(
  domains          = nrow(all_unique_domains_visited),
  with_app_traffic = sum(all_unique_domains_visited$n_visits_total >
                         all_unique_domains_visited$n_visits_excl_app),
  with_pc1         = sum(!is.na(all_unique_domains_visited$pc1)),
  flagged_is_news  = sum(all_unique_domains_visited$is_news, na.rm = TRUE)
)
```

# Part 6: Reclassification Base Table

`experiment_visits` sums every `during_w1` / `during_w2` / `during_w3` row;
`pre_visits` is the `pre` period alone. `between_*` and `post` visits belong to
neither window and are excluded from both counts, though they still count
toward `n_visits_total`.

```{r reclassification-base-table}
period_window_counts <- visits_with_apps_as_domains %>%
  filter(!is.na(period)) %>%
  mutate(window = case_when(
    period %in% c("during_w1", "during_w2", "during_w3") ~ "experiment_visits",
    period == "pre" ~ "pre_visits",
    TRUE ~ "other"
  )) %>%
  count(content_id, window) %>%
  pivot_wider(names_from = window, values_from = n, values_fill = 0L) %>%
  rename(domain = content_id) %>%
  dplyr::select(-any_of("other"))

domain_reclass_base <- all_unique_domains_visited %>%
  left_join(period_window_counts, by = "domain", relationship = "one-to-one") %>%
  mutate(
    across(c(experiment_visits, pre_visits), ~ replace_na(.x, 0L)),
    reclassification_note   = NA_character_,
    reclassification_status = "uncertain"
  )

save_both(domain_reclass_base, "domain_reclass_base_with_apps_as_domains")

cat("Rows in domain_reclass_base:", nrow(domain_reclass_base),
    "| with any experiment-window traffic:", sum(domain_reclass_base$experiment_visits > 0), "\n")
```
