---
title: "News Population Correction: Top-N Review, PC1 Long Tail, and Final Visits"
author: "Master's Thesis -- Media Quality / Media Diet"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = TRUE, message = TRUE)
```

# Overview

Corrects the automated `is_news` classification through two complementary
manual reviews and writes the corrected flag back onto the visit-level data.
Four things, in this order:

1. Export the Top-N most-visited domains for manual review, with a coverage
   figure that makes the cutoff auditable
2. Export the complementary case: PC1-carrying domains that fall outside the
   cutoff purely on traffic
3. Read both completed reviews back and merge them into one
   `is_news_corrected` per domain
4. Join that lookup onto the visits table and save `visits_final`

## This script runs in two passes

Steps 1--2 write workbooks that a human then fills in. Steps 3--4 read those
completed workbooks back. On a first run the review files do not exist yet, so
Part 4 onward is skipped with a message rather than failing. Rerun after the
review is saved.

The manual step between the passes is: open the exported `.xlsx`, fill in
`is_news_corrected_status`, and save the candidate sheet as a semicolon-
separated `.csv` at the path configured below.

## Why a Top-N cutoff rather than a full census

Manually reviewing every observed domain is neither standard practice nor
necessary. Traffic in web-tracking data is heavily right-skewed: a small number
of domains account for most visits, while the long tail consists of domains
with a handful of visits each, contributing negligibly to aggregated media-diet
measures. Web-tracking studies that classify domains by hand therefore restrict
coding to the most-visited domains (e.g. Stier et al., 2020, who coded the top
5,000 domains per country).

The cutoff is reported as a share of total traffic, separately for the `pre`
window, the experimental window, and overall, so the coverage claim is
auditable rather than assumed.

## The two reviews are complementary, not redundant

| Review | Candidate pool | Catches |
|---|---|---|
| Top-N | The `n_top` most-visited domains, any `is_news` status | False positives and false negatives among domains that actually carry weight |
| PC1 long tail | Domains with a PC1 score that fall outside the cutoff | Domains an external quality dataset already treats as news, missed by traffic rank alone |

One candidate pool per review rather than separate news / non-news lists: the
cutoff already spans both currently-flagged domains that may be wrong and
unflagged domains that may have been missed.

## Outputs

| Object | Role |
|---|---|
| `news_correction_candidates.xlsx` | Top-N review workbook, with coverage and coding instructions |
| `pc1_longtail_candidates_for_reclassification.xlsx` | Long-tail review workbook |
| `is_news_corrected_lookup.csv` | One row per domain: `is_news`, `is_news_corrected`, `pc1` |
| `domains_newly_classified_as_news.csv` | Domains the review added to the news population |
| `visits_final.Rds` / `.RData` | Visit-level data with `is_news_corrected` and `pc1` attached |

# Part 1: Setup

```{r libraries}
library(dplyr)
library(readr)
library(tidyr)
library(openxlsx)
library(purrr)
```

```{r paths-config, include=FALSE}
project_root <- "~/Desktop/GitHub/DoesMediaQualityMatter"
output_dir <- file.path(project_root, "Output", "01_visits")

base_path   <- file.path(output_dir, "domain_reclass_base_with_apps_as_domains.Rds")
visits_path <- file.path(output_dir, "visits_with_apps_as_domains.Rds")

# Completed review files, saved by hand out of the exported workbooks.
reviewed_paths <- c(
  topn     = file.path(output_dir, "news_correction_candidates", "candidates-Tabelle 1.csv"),
  longtail = file.path(output_dir, "pc1_longtail_candidates_for_reclassification",
                       "pc1_longtail_candidates-Tabelle 1.csv")
)
```




```{r constants-and-helpers}
n_top <- 500

save_both <- function(obj, name, dir = output_dir) {
  assign(name, obj)
  saveRDS(obj, file.path(dir, paste0(name, ".Rds")))
  save(list = name, file = file.path(dir, paste0(name, ".RData")))
}

# Coding conventions shipped with both workbooks, so the reviewer sees the same
# rules regardless of which file they open.
correction_instructions <- tibble(
  field = c("is_news_corrected_status", "correction_note", "visit_types_observed"),
  instruction = c(
    "
    If the homepage displays news, not just on a specific topic, but also on a wider range of events from around the world, whether local or national, without requiring users to navigate to a subpage, it should be classified as a news website. One of: confirmed_news, confirmed_non_news, uncertain. Leave uncertain if unsure.",
    "Short justification, e.g. 'regional newspaper, missed by the classifier' or 'shopping platform, correctly excluded'.",
    "Observation channels only: 0 = web, 1 = mobile web, 2 = app. Descriptive; do not change."
  )
)

export_review_workbook <- function(candidates, file, sheet_name, extra_sheets = list()) {
  sheets <- c(setNames(list(candidates), sheet_name), extra_sheets,
              list(instructions = correction_instructions))
  write.xlsx(sheets, file = file.path(output_dir, file), overwrite = TRUE, asTable = TRUE)
}
```

```{r load-inputs}
domain_reclass_base <- readRDS(base_path)
visits_with_apps_as_domains <- readRDS(visits_path)

cat("Domains in reclassification base:", nrow(domain_reclass_base),
    "| with a PC1 score:", sum(!is.na(domain_reclass_base$pc1)), "\n")
```

# Part 2: Top-N Review

## Coverage of the cutoff

Computed per window, since a ranking by total traffic does not necessarily
produce the same coverage within `pre` alone or the experimental window alone.
Adjust `n_top` and rerun if coverage is lower than the methods write-up needs.

```{r coverage-check}
top_n_domains <- domain_reclass_base %>%
  arrange(desc(n_visits_total)) %>%
  slice_head(n = n_top)

coverage_summary <- tibble(
  window = c("total", "pre", "experiment"),
  visits_in_top_n = c(sum(top_n_domains$n_visits_total),
                      sum(top_n_domains$pre_visits),
                      sum(top_n_domains$experiment_visits)),
  visits_overall  = c(sum(domain_reclass_base$n_visits_total),
                      sum(domain_reclass_base$pre_visits),
                      sum(domain_reclass_base$experiment_visits))
) %>%
  mutate(pct_covered = if_else(visits_overall > 0,
                               round(100 * visits_in_top_n / visits_overall, 1), NA_real_))

coverage_summary
```

## Candidate pool and export

Domains carrying a PC1 score despite `is_news == FALSE` are pre-filled as
`confirmed_news` and sorted first: an external quality dataset already treats
them as a news or opinion source, which makes them the highest-information
candidates. Everything else follows by traffic.

`visit_types_observed` is a one-row-per-domain summary of the channels a domain
was seen through (`0` web, `1` mobile web, `2` app), so `"0, 2"` means the same
publisher domain was reached both through web tracking and through an app
mapped to it.

```{r topn-candidates-export}
news_correction_candidates <- top_n_domains %>%
  mutate(
    pc1_backed_miss = !is_news & !is.na(pc1),
    is_news_corrected_status = if_else(pc1_backed_miss, "confirmed_news", "uncertain"),
    correction_note = if_else(
      pc1_backed_miss,
      "has a PC1 score despite not being flagged is_news; review whether this is a missed news source",
      NA_character_)
  ) %>%
  arrange(desc(pc1_backed_miss), desc(n_visits_total)) %>%
  dplyr::select(domain, category_1, category_2, category_3, app_cat, is_news, pc1,
                n_visits_total, pre_visits, experiment_visits, visit_types_observed,
                is_news_corrected_status, correction_note)

export_review_workbook(
  news_correction_candidates, "news_correction_candidates.xlsx", "candidates",
  extra_sheets = list(coverage = coverage_summary %>%
                        dplyr::select(window, pct_of_visits_covered_by_top_n = pct_covered)))

cat("Top-N candidates:", nrow(news_correction_candidates),
    "| pre-filled as confirmed_news via PC1 signal:",
    sum(news_correction_candidates$is_news_corrected_status == "confirmed_news"), "\n")
```

# Part 3: PC1 Long-Tail Review

The complementary case: domains carrying a PC1 score that fall outside the
cutoff purely because they have too little traffic to rank. Individually
low-weight, but a wrong `is_news` on a PC1-carrying domain leaves an
unexplained gap in any composite quality score.

Only the `is_news == FALSE` rows need an actual look. The `is_news == TRUE`
rows already agree across both signals and are kept in the export for
documentation only.

```{r longtail-candidates-export}
pc1_longtail_candidates <- domain_reclass_base %>%
  filter(!is.na(pc1)) %>%
  anti_join(top_n_domains %>% dplyr::select(domain), by = "domain") %>%
  arrange(is_news, desc(n_visits_total)) %>%
  mutate(
    is_news_corrected_status = if_else(is_news, "confirmed_news", "uncertain"),
    correction_note = if_else(
      is_news,
      "PC1 and is_news agree; documentation only, no review needed",
      "has a PC1 score despite not being flagged is_news, and falls outside the Top-N traffic cutoff")
  ) %>%
  dplyr::select(domain, is_news, pc1, n_visits_total, pre_visits, experiment_visits,
                visit_types_observed, category_1, category_2, category_3, app_cat,
                is_news_corrected_status, correction_note)

export_review_workbook(pc1_longtail_candidates,
                       "pc1_longtail_candidates_for_reclassification.xlsx",
                       "pc1_longtail_candidates")

cat("PC1-carrying domains outside the Top-", n_top, " cutoff: ", nrow(pc1_longtail_candidates),
    " | already is_news: ", sum(pc1_longtail_candidates$is_news),
    " | actually needing review: ", sum(!pc1_longtail_candidates$is_news), "\n", sep = "")
```

# Part 4: Merging Both Reviews

Everything below requires the completed review files. If they are missing, this
is a first pass: do the manual review, then rerun.

```{r review-files-present}
reviews_complete <- all(file.exists(reviewed_paths))

if (!reviews_complete) {
  message("Review files not found:\n  ",
          paste(reviewed_paths[!file.exists(reviewed_paths)], collapse = "\n  "),
          "\nWorkbooks have been exported. Complete the review, save the candidate ",
          "sheet as semicolon-separated CSV at those paths, then rerun.")
}

knitr::opts_chunk$set(eval = reviews_complete)
```

Both review files feed the same lookup. The Top-N review is bound first, so it
takes precedence if a domain happens to appear in both.

```{r read-reviews}
all_reviewed <- imap_dfr(reviewed_paths, function(path, id) {
  read_csv2(path, show_col_types = FALSE) %>%
    mutate(domain = as.character(domain), pc1 = as.numeric(pc1), review = id) %>%
    dplyr::select(domain, is_news_corrected_status, pc1, review)
}) %>%
  filter(!is.na(domain), domain != "") %>%
  distinct(domain, .keep_all = TRUE)

count(all_reviewed, review, is_news_corrected_status)
```

The PC1 column in the review files is descriptive; reviewers are not asked to
change it. A disagreement with the base table means a review file was edited in
a column it should not have been, or was exported with a different decimal
convention. Worth seeing before it silently overwrites a score.

```{r pc1-consistency-check}
pc1_disagreements <- domain_reclass_base %>%
  dplyr::select(domain, pc1_base = pc1) %>%
  inner_join(all_reviewed %>% dplyr::select(domain, pc1_reviewed = pc1), by = "domain") %>%
  filter(!is.na(pc1_base), !is.na(pc1_reviewed), abs(pc1_base - pc1_reviewed) > 1e-6)

cat("Domains where the review file's PC1 differs from the base table:",
    nrow(pc1_disagreements), "\n")
if (nrow(pc1_disagreements) > 0) print(head(pc1_disagreements, 20))
```

The base score is authoritative; a score from a review file is used only where
the base is missing. Domains never reviewed keep the automated `is_news`, so
the correction can only ever move a domain that a human actually looked at.

```{r build-lookup}
is_news_corrected_lookup <- domain_reclass_base %>%
  dplyr::select(domain, is_news, pc1_base = pc1) %>%
  left_join(all_reviewed %>% dplyr::select(domain, is_news_corrected_status, pc1),
            by = "domain") %>%
  mutate(
    pc1 = coalesce(pc1_base, pc1),
    is_news_corrected = case_when(
      is_news_corrected_status == "confirmed_news"     ~ TRUE,
      is_news_corrected_status == "confirmed_non_news" ~ FALSE,
      TRUE ~ is_news
    )
  ) %>%
  dplyr::select(domain, is_news, is_news_corrected, pc1) %>%
  distinct(domain, .keep_all = TRUE)

# Every downstream join assumes one row per domain.
stopifnot(n_distinct(is_news_corrected_lookup$domain) == nrow(is_news_corrected_lookup))

write_csv(is_news_corrected_lookup, file.path(output_dir, "is_news_corrected_lookup.csv"))

tibble(
  domains        = nrow(is_news_corrected_lookup),
  added_to_news  = sum(is_news_corrected_lookup$is_news_corrected & !is_news_corrected_lookup$is_news),
  removed        = sum(!is_news_corrected_lookup$is_news_corrected & is_news_corrected_lookup$is_news),
  news_after     = sum(is_news_corrected_lookup$is_news_corrected)
)
```

```{r newly-news-domains}
domains_newly_news <- is_news_corrected_lookup %>%
  filter(is_news_corrected, !is_news) %>%
  arrange(domain)

print(domains_newly_news$domain)


```

# Part 5: Writing the Corrected Flag Back onto the Visits

`is_news` from the automated classification is kept untouched alongside the
corrected flag, so any downstream comparison between the two definitions is
possible without rebuilding either. Content IDs outside the lookup retain the
automated classification rather than becoming `NA`. PC1 stays `NA` for domains
without a score and for app names that were never mapped to a publisher domain.

```{r join-onto-visits}
n_before <- nrow(visits_with_apps_as_domains)

visits_final <- visits_with_apps_as_domains %>%
  mutate(content_id = as.character(content_id), is_news = as.logical(is_news)) %>%
  left_join(is_news_corrected_lookup %>% dplyr::select(domain, is_news_corrected, pc1),
            by = c("content_id" = "domain"), relationship = "many-to-one") %>%
  mutate(is_news_corrected = coalesce(is_news_corrected, is_news))

stopifnot(nrow(visits_final) == n_before)

tibble(
  visit_rows        = nrow(visits_final),
  is_news           = sum(visits_final$is_news, na.rm = TRUE),
  is_news_corrected = sum(visits_final$is_news_corrected, na.rm = TRUE),
  newly_news_rows   = sum(!visits_final$is_news & visits_final$is_news_corrected, na.rm = TRUE),
  with_pc1          = sum(!is.na(visits_final$pc1))
)

save_both(visits_final, "visits_final")
```
