---
title: "Habitual Media Diet: Level and Diversity Across Diet Definitions and Tracking Channels"
author: "Master's Thesis -- Media Quality / Media Diet"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = FALSE, message = TRUE)
```

# Overview

Builds pre-treatment measures of habitual media-diet quality and
diversity. Every construction step and every diagnostic runs once per
combination of **tracking channel** and **diet definition**, so no logic
is duplicated across variants and any difference between them reflects
the data rather than an inconsistency between copy-pasted blocks.

Five things, in this order:

1.  Fix a participant-specific reference date and a 30-day baseline
    window
2.  Build level and diversity for every channel x diet combination
3.  Add descriptive median splits, computed within each combination
4.  Produce faceted plots and five design diagnostics across all
    combinations
5.  Compare the diet definitions on coverage, variance, stability and
    sparsity

## Two registries define everything below

**Tracking channel.** This replaces the previous second script, which
was a full copy of this one differing in a single filter.

| Channel key | Rule | Purpose |
|------------------------|------------------------|------------------------|
| `with_apps` | All visit types | Primary measure; app traffic folded into publisher domains in `01d` |
| `without_apps` | `visit_type != 2` | Robustness: does app-derived traffic drive the picture |

**Diet definition.** The original `is_news` is never overwritten;
`is_news_corrected` reflects the manual domain review from `01e`.

| Variant key | Visit filter | Main use |
|------------------------|------------------------|------------------------|
| `overall` | `pc1` available, no news restriction | Broad information-diet description |
| `news` | `is_news == TRUE` | Sensitivity check on the automated classification |
| `news_corrected` | `is_news_corrected == TRUE` | Primary news-specific measure |

All six combinations share the same reference date, window, activity
rule and weighting logic. Only the visit-level filter differs.

## Level and diversity

Level is the duration-weighted mean PC1 score: the average quality of a
participant's scored sources. Diversity is the duration-weighted
standard deviation: how heterogeneous those sources are in quality. Two
people can share an average and differ sharply in diversity, one using
mid-quality sources consistently, the other alternating between high and
low. The distinction follows media-diet work that treats the average
position of a diet and its internal heterogeneity as separate constructs
(Padro-Solanet & Balcells, 2022).

## Design choices

| Choice | Rule | Reason |
|------------------------|------------------------|------------------------|
| Reference date | Day before each participant's earliest search task | Guarantees the baseline precedes that participant's first exposure |
| Baseline window | 30 calendar days | Recent and comparable; checked against full history in Diagnostic B |
| Activity threshold | At least 7 active days, counted on *all* baseline visits | Avoids treating sparse observation as habitual behaviour; the threshold describes overall browsing, not diet-specific browsing |
| Weighting | Visit duration | Longer visits contribute more |
| Diversity requirement | At least 2 distinct PC1 values | A spread statistic is not meaningful for a single score |
| Median splits | Computed within each channel x variant | The combinations have different distributions and different available samples |

## Outputs

| Output | Level | Purpose |
|------------------------|------------------------|------------------------|
| `<channel_dir>/habitual_media_diet_FINAL.csv` | Participant (wide) | Variant-prefixed columns, one file per channel, read by `03b`--`03e` |
| `habitual_media_diet_long.csv` | Participant x channel x variant | Long format for plots and comparison |
| `MAIN_plot_*.png` | Faceted channel x variant | Core descriptive plots |
| `diagnostics/diagnostic_*.csv`, `diag*.png` | Participant / visit | Design checks A--E |
| `habitual_media_diet_variant_comparison.csv` | Channel x variant | Side-by-side comparison table |

In the wide file every measure carries a `hab_` prefix and its variant
key, for example `hab_news_corrected_dw_pc1`. The prefix marks the
measurement period: `hab_` for pre-treatment habitual measures built
here, `exp_` for experimental-period exposures built in `03a`. Keeping
the two families disjoint is what prevents the join collision documented
in Appendix G. In the long file the names stay generic, with `channel`
and `variant` columns carrying the keys.

# Part 1: Setup

```{r libraries}
library(dplyr)
library(tidyr)
library(purrr)
library(ggplot2)
library(readr)
library(tibble)
```


```{r paths-config-data, include = FALSE}

data_dir     <- "~/Desktop/Masterarbeit/Data"
project_root <- "~/Desktop/GitHub/DoesMediaQualityMatter"

```

```{r paths-config}
#project_root <- "DoesMediaQualityMatter"
#data_dir     <- ""
input_dir  <- file.path(project_root, "Output", "01_visits")
output_dir <- file.path(project_root, "Output", "02_media_quality")

# One directory per tracking channel, matching the existing folder names so
# downstream paths stay valid.
channel_dirs <- c(
  with_apps    = file.path(output_dir, "habitual_media_diet_baseline"),
  without_apps = file.path(output_dir, "habitual_media_diet_baseline_without_apps")
)
diagnostics_dir <- file.path(channel_dirs[["with_apps"]], "diagnostics")

walk(c(channel_dirs, diagnostics_dir), dir.create, showWarnings = FALSE, recursive = TRUE)

attitude_paths <- file.path(data_dir,
                            c("df1_final_ac.Rdata", "df2_final_ac.Rdata", "df3_final_ac.Rdata"))
```

```{r constants}
BASELINE_WINDOW_DAYS    <- 30
MIN_ACTIVE_DAYS         <- 7
MIN_ACTIVE_DAYS_FULL    <- 20
MIN_DISTINCT_PC1_FOR_SD <- 2

DATA_COLLECTION_START <- as.Date("2023-04-01")
WAVE1_START_FIXED     <- as.Date("2023-06-12")
```

## Inputs

| Input | Level | Required variables |
|------------------------|------------------------|------------------------|
| `visits_final.Rds` | Visit | `pid`, `used_date`, `content_id`, `duration`, `visit_type`, `pc1`, `is_news`, `is_news_corrected` |
| `df1`--`df3_final_ac.Rdata` | Wave | `pid`, `start_time`, `sources_used` |

```{r load-inputs}
visits <- readRDS(file.path(input_dir, "visits_final.Rds")) %>%
  mutate(
    pid = as.character(pid),
    used_date = as.Date(used_date),
    content_id = as.character(content_id),
    duration = as.numeric(duration),
    pc1 = as.numeric(pc1),
    is_news = as.logical(is_news),
    is_news_corrected = as.logical(is_news_corrected)
  )

waves <- map(attitude_paths, function(p) {
  e <- new.env(); load(p, envir = e)
  get(ls(e)[1], envir = e) %>%
    mutate(pid = as.character(as.numeric(pid)),
           search_start = as.POSIXct(start_time, format = "%Y-%m-%d %H:%M:%S", tz = "Europe/Berlin"))
})

tibble(
  visit_rows        = nrow(visits),
  participants      = n_distinct(visits$pid),
  with_pc1          = sum(!is.na(visits$pc1)),
  is_news           = sum(visits$is_news, na.rm = TRUE),
  is_news_corrected = sum(visits$is_news_corrected, na.rm = TRUE),
  app_rows          = sum(visits$visit_type == 2L, na.rm = TRUE)
)
```

## Registries

The single place where the six combinations are defined. Everything
below loops over `analysis_grid` rather than repeating code per
combination. `flag_col = NA` means no news filter.

```{r registries}
channel_variants <- tribble(
  ~channel,        ~channel_label,           ~keep_apps,
  "with_apps",     "All channels",           TRUE,
  "without_apps",  "Web and mobile web only", FALSE
)

diet_variants <- tribble(
  ~variant,         ~flag_col,           ~variant_label,
  "overall",        NA_character_,       "Overall scored diet",
  "news",           "is_news",           "Automated news diet",
  "news_corrected", "is_news_corrected", "Corrected news diet"
)

channel_levels <- channel_variants$channel
variant_levels <- diet_variants$variant

analysis_grid <- cross_join(channel_variants, diet_variants)

# Visit-level data split by channel, used by every builder below.
visits_by_channel <- set_names(
  map(channel_variants$keep_apps, function(keep)
    if (keep) visits else filter(visits, visit_type != 2L)),
  channel_variants$channel)

map_dfr(names(visits_by_channel), ~ tibble(channel = .x, visit_rows = nrow(visits_by_channel[[.x]])))
```

# Part 2: Reference Date and Baseline Window

Each participant's baseline ends the day before their earliest recorded
search task, which is what prevents post-treatment visits from entering
a pre-treatment measure. The rule does not depend on channel or diet
variant.

```{r reference-date}
pid_wave_search <- map_dfr(seq_along(waves), ~ waves[[.x]] %>%
                             transmute(pid, wave = .x, search_start)) %>%
  filter(!is.na(search_start)) %>%
  distinct(pid, wave, .keep_all = TRUE)

pid_windows <- pid_wave_search %>%
  group_by(pid) %>%
  summarise(reference_date = as.Date(min(search_start)) - 1, .groups = "drop") %>%
  mutate(window_start = reference_date - (BASELINE_WINDOW_DAYS - 1))

visits_baseline <- map(visits_by_channel, function(v)
  v %>% inner_join(pid_windows, by = "pid") %>%
    filter(used_date >= window_start, used_date <= reference_date))

map_dfr(names(visits_baseline), ~ tibble(
  channel = .x,
  baseline_rows = nrow(visits_baseline[[.x]]),
  participants = n_distinct(visits_baseline[[.x]]$pid)))
```

Descriptive only, used in no calculation: whether a participant reported
using any source during a search task.

```{r used-any-source}
pid_used_any_source <- map_dfr(seq_along(waves), ~ waves[[.x]] %>%
                                 transmute(pid, wave = .x, sources_used)) %>%
  distinct(pid, wave, .keep_all = TRUE) %>%
  group_by(pid) %>%
  summarise(used_any_source = if (all(is.na(sources_used))) NA
            else any(sources_used == 1, na.rm = TRUE), .groups = "drop")
```

# Part 3: Constructing the Diet Measures

```{r weighting-helpers}
weighted_mean_na <- function(x, w) {
  keep <- !is.na(x) & !is.na(w) & w > 0
  if (!any(keep)) return(NA_real_)
  sum(x[keep] * w[keep]) / sum(w[keep])
}

weighted_sd_na <- function(x, w) {
  keep <- !is.na(x) & !is.na(w) & w > 0
  x <- x[keep]; w <- w[keep]
  if (length(unique(x)) < MIN_DISTINCT_PC1_FOR_SD || sum(w) == 0) return(NA_real_)
  m <- sum(x * w) / sum(w)
  sqrt(sum(w * (x - m)^2) / sum(w))
}

# Subsets to a diet variant's visits and computes the five core statistics.
# Called once per grid row, so all six combinations share identical logic.
build_variant_activity <- function(flag_col, visits_df) {
  if (!is.na(flag_col)) visits_df <- visits_df[visits_df[[flag_col]] %in% TRUE, , drop = FALSE]

  visits_df %>%
    group_by(pid) %>%
    summarise(
      n_rows_with_pc1          = sum(!is.na(pc1)),
      n_distinct_pc1           = n_distinct(pc1[!is.na(pc1)]),
      pc1_duration             = sum(duration[!is.na(pc1)], na.rm = TRUE),
      duration_weighted_pc1    = weighted_mean_na(pc1, duration),
      duration_weighted_sd_pc1 = weighted_sd_na(pc1, duration),
      .groups = "drop"
    )
}
```

Active days, row counts and total duration describe overall baseline
browsing and so depend on the channel but not on the diet variant. They
gate every variant's availability through the activity threshold.

```{r general-activity}
general_activity <- map_dfr(names(visits_baseline), ~ visits_baseline[[.x]] %>%
  group_by(pid) %>%
  summarise(n_active_days = n_distinct(used_date), n_rows = n(),
            total_duration = sum(duration, na.rm = TRUE), .groups = "drop") %>%
  mutate(channel = .x))
```

A participant absent from a combination's activity table had zero
qualifying visits for that combination, not a missing observation. The
cross join below makes those structural zeros explicit before the
coalesce.

```{r build-all-combinations}
habitual_long <- analysis_grid %>%
  mutate(activity = map2(flag_col, channel,
                         ~ build_variant_activity(.x, visits_baseline[[.y]]))) %>%
  dplyr::select(channel, channel_label, variant, variant_label, activity) %>%
  unnest(activity)

habitual_long <- pid_windows %>%
  dplyr::select(pid) %>%
  cross_join(analysis_grid %>%
               dplyr::select(channel, channel_label, variant, variant_label)) %>%
  left_join(habitual_long, by = c("pid", "channel", "channel_label", "variant", "variant_label")) %>%
  left_join(general_activity, by = c("pid", "channel")) %>%
  left_join(pid_used_any_source, by = "pid") %>%
  mutate(
    across(c(n_active_days, n_rows, n_rows_with_pc1, n_distinct_pc1), ~ coalesce(.x, 0L)),
    across(c(total_duration, pc1_duration), ~ coalesce(.x, 0)),
    share_active_days = n_active_days / BASELINE_WINDOW_DAYS,
    meets_activity_threshold = n_active_days >= MIN_ACTIVE_DAYS,
    duration_weighted_pc1    = if_else(meets_activity_threshold, duration_weighted_pc1, NA_real_),
    duration_weighted_sd_pc1 = if_else(meets_activity_threshold, duration_weighted_sd_pc1, NA_real_),
    channel = factor(channel, levels = channel_levels),
    variant = factor(variant, levels = variant_levels)
  )

cat("Rows (participants x channels x variants):", nrow(habitual_long), "\n")
```

## Coverage across combinations

```{r measure-coverage}
measure_coverage <- habitual_long %>%
  group_by(channel, channel_label, variant, variant_label) %>%
  summarise(
    participants           = n(),
    meets_activity         = sum(meets_activity_threshold),
    level_available        = sum(!is.na(duration_weighted_pc1)),
    diversity_available    = sum(!is.na(duration_weighted_sd_pc1)),
    median_n_rows_with_pc1 = median(n_rows_with_pc1),
    .groups = "drop"
  )

measure_coverage
write_csv(measure_coverage, file.path(channel_dirs[["with_apps"]],
                                      "habitual_media_diet_measure_coverage.csv"))
```

# Part 4: Descriptive Median Splits

Median splits are descriptive only; the continuous level and diversity
measures remain the preferred variables for confirmatory models. Medians
are computed within each channel x variant, since the combinations
differ in both distribution and available sample.

```{r subgroup-splits}
habitual_long <- habitual_long %>%
  group_by(channel, variant) %>%
  mutate(
    median_duration_weighted_pc1    = median(duration_weighted_pc1, na.rm = TRUE),
    median_duration_weighted_sd_pc1 = median(duration_weighted_sd_pc1, na.rm = TRUE),
    habitual_diet = case_when(
      is.na(duration_weighted_pc1) ~ NA_character_,
      duration_weighted_pc1 <= median_duration_weighted_pc1 ~ "low",
      TRUE ~ "high"),
    habitual_diversity = case_when(
      is.na(duration_weighted_sd_pc1) ~ NA_character_,
      duration_weighted_sd_pc1 <= median_duration_weighted_sd_pc1 ~ "low",
      TRUE ~ "high"),
    habitual_diet_diversity_group = if_else(
      is.na(habitual_diet) | is.na(habitual_diversity), NA_character_,
      paste0(habitual_diet, "_level-", habitual_diversity, "_diversity"))
  ) %>%
  ungroup()

count(habitual_long, channel, variant, habitual_diet_diversity_group) %>%
  pivot_wider(names_from = habitual_diet_diversity_group, values_from = n, values_fill = 0L)
```

# Part 5: Saving

The long file carries both channels. The wide files are written one per
channel into that channel's own directory, keeping the variant-prefixed
column names that downstream scripts expect.

Column names carry the measurement period as a prefix. Every habitual
column starts with `hab_`, every experimental-period column built in
`03a` starts with `exp_`. This is not cosmetic: the two families
previously shared names, so a join produced silent `.x` / `.y` suffixes
and a pre-treatment measure could be used where an experimental-period
exposure was intended (Appendix G). With disjoint prefixes the collision
cannot occur, and a model formula is readable without tracing the join
history.

| Generic name in the long file | Wide name, e.g. variant `news_corrected` |
|------------------------------------|------------------------------------|
| `duration_weighted_pc1` | `hab_news_corrected_dw_pc1` |
| `duration_weighted_sd_pc1` | `hab_news_corrected_dw_sd_pc1` |
| `habitual_diet` | `hab_news_corrected_level_group` |
| `habitual_diversity` | `hab_news_corrected_diversity_group` |
| `habitual_diet_diversity_group` | `hab_news_corrected_level_diversity_group` |

```{r save-final}
write_csv(habitual_long, file.path(channel_dirs[["with_apps"]], "habitual_media_diet_long.csv"))

# Generic long-format name -> stem used in the wide file.
wide_stems <- c(
  duration_weighted_pc1           = "dw_pc1",
  duration_weighted_sd_pc1        = "dw_sd_pc1",
  habitual_diet                   = "level_group",
  habitual_diversity              = "diversity_group",
  habitual_diet_diversity_group   = "level_diversity_group",
  median_duration_weighted_pc1    = "median_dw_pc1",
  median_duration_weighted_sd_pc1 = "median_dw_sd_pc1",
  n_rows_with_pc1                 = "n_rows_with_pc1",
  n_distinct_pc1                  = "n_distinct_pc1",
  pc1_duration                    = "pc1_duration"
)

to_wide <- function(df) {
  pieces <- df %>%
    dplyr::select(pid, variant, all_of(names(wide_stems))) %>%
    split(.$variant) %>%
    imap(~ .x %>%
           dplyr::select(-variant) %>%
           rename_with(function(n) paste0("hab_", .y, "_", wide_stems[n]), -pid))

  reduce(pieces, left_join, by = "pid") %>%
    left_join(df %>% distinct(pid, n_active_days, n_rows, total_duration,
                              share_active_days, meets_activity_threshold, used_any_source),
              by = "pid")
}

walk(names(channel_dirs), function(ch) {
  wide <- habitual_long %>% filter(channel == ch) %>% to_wide()

  # Every measure column must carry the hab_ prefix. A column that does not is
  # a candidate for a name collision downstream.
  unprefixed <- setdiff(names(wide),
                        c("pid", "n_active_days", "n_rows", "total_duration",
                          "share_active_days", "meets_activity_threshold", "used_any_source"))
  unprefixed <- unprefixed[!startsWith(unprefixed, "hab_")]
  if (length(unprefixed) > 0) {
    stop("Wide file for channel '", ch, "' has unprefixed measure columns: ",
         paste(unprefixed, collapse = ", "))
  }

  write_csv(wide, file.path(channel_dirs[[ch]], "habitual_media_diet_FINAL.csv"))
  cat(ch, ": wide file with", ncol(wide), "columns and", nrow(wide), "rows\n")
})


```

# Part 6: Core Visualisations

One figure per tracking channel, saved into that channel's own
directory, with the three diet definitions faceted side by side inside
each figure. Comparing the two channels means comparing two files rather
than two rows of one grid, which keeps each figure at a size that can be
dropped into the thesis without shrinking the panels.

```{r plot-helper}
# Draws one plot per channel and writes it into that channel's directory.
# `plot_fun` receives the channel's subset of the data and its label.
plot_by_channel <- function(data, plot_fun, name, width = 11, height = 4.5) {
  for (ch in names(channel_dirs)) {
    p <- plot_fun(data %>% filter(channel == ch),
                  channel_variants$channel_label[channel_variants$channel == ch])
    print(p)
    ggsave(file.path(channel_dirs[[ch]], name), p, width = width, height = height)
  }
}

variant_facets <- function() facet_wrap(~ variant_label, nrow = 1)
```

## Activity days

Active days do not depend on the diet definition, so this plot is not
faceted. It is included because the activity threshold gates every
variant's availability.

```{r plot-active-days, fig.width=7, fig.height=5}
plot_by_channel(
  habitual_long %>% distinct(pid, channel, n_active_days),
  function(d, lab)
    ggplot(d, aes(x = n_active_days)) +
      geom_histogram(binwidth = 1, fill = "steelblue", alpha = 0.7) +
      geom_vline(xintercept = MIN_ACTIVE_DAYS, linetype = "dashed", colour = "firebrick") +
      labs(title = "Active days in the 30-day baseline window", subtitle = lab,
           x = "Active days", y = "Participants") +
      theme_minimal(),
  "MAIN_plot_active_days.png", width = 7, height = 5)
```

## Level density

```{r plot-level-density, fig.width=11, fig.height=4.5}
plot_by_channel(
  habitual_long %>% filter(!is.na(duration_weighted_pc1)),
  function(d, lab)
    ggplot(d, aes(x = duration_weighted_pc1, fill = variant_label)) +
      geom_density(alpha = 0.6, show.legend = FALSE) + variant_facets() +
      labs(title = "Habitual diet quality LEVEL", subtitle = lab,
           x = "Duration-weighted PC1", y = "Density") +
      theme_minimal(),
  "MAIN_plot_level_density.png")
```

## Diversity density

```{r plot-diversity-density, fig.width=11, fig.height=4.5}
plot_by_channel(
  habitual_long %>% filter(!is.na(duration_weighted_sd_pc1)),
  function(d, lab)
    ggplot(d, aes(x = duration_weighted_sd_pc1, fill = variant_label)) +
      geom_density(alpha = 0.6, show.legend = FALSE) + variant_facets() +
      labs(title = "Habitual diet quality DIVERSITY", subtitle = lab,
           x = "Duration-weighted PC1 standard deviation", y = "Density") +
      theme_minimal(),
  "MAIN_plot_diversity_density.png")
```

## Level versus diversity

```{r plot-level-vs-diversity, fig.width=12, fig.height=5}
plot_by_channel(
  habitual_long %>% filter(!is.na(duration_weighted_pc1), !is.na(duration_weighted_sd_pc1)),
  function(d, lab)
    ggplot(d, aes(x = duration_weighted_pc1, y = duration_weighted_sd_pc1,
                  colour = habitual_diet_diversity_group)) +
      geom_point(alpha = 0.5) +
      geom_vline(aes(xintercept = median_duration_weighted_pc1),
                 linetype = "dashed", colour = "grey40") +
      geom_hline(aes(yintercept = median_duration_weighted_sd_pc1),
                 linetype = "dashed", colour = "grey40") +
      variant_facets() +
      labs(title = "Level versus diversity", subtitle = lab,
           x = "Duration-weighted PC1 level", y = "Duration-weighted PC1 diversity",
           colour = "Descriptive 2x2 group") +
      theme_minimal() + theme(legend.position = "bottom"),
  "MAIN_plot_level_vs_diversity.png", width = 12, height = 5)
```

## 2x2 subgroup sizes

```{r plot-2x2-sizes, fig.width=12, fig.height=4.5}
plot_by_channel(
  habitual_long %>% filter(!is.na(habitual_diet_diversity_group)),
  function(d, lab)
    ggplot(d, aes(x = habitual_diet_diversity_group)) +
      geom_bar(fill = "steelblue") + variant_facets() +
      labs(title = "2x2 subgroup sizes", subtitle = lab, x = NULL, y = "Participants") +
      theme_minimal() + theme(axis.text.x = element_text(angle = 30, hjust = 1)),
  "MAIN_plot_2x2_group_sizes.png", width = 12, height = 4.5)
```

## Coverage per definition

Makes the missingness trade-off from the coverage table visible:
restricting to news, then to corrected news, shrinks the number of
participants with a usable score.

```{r plot-coverage, fig.width=8, fig.height=5}
plot_by_channel(
  measure_coverage %>%
    dplyr::select(channel, variant_label, level_available, diversity_available) %>%
    pivot_longer(c(level_available, diversity_available),
                 names_to = "measure", values_to = "n_participants") %>%
    mutate(measure = recode(measure, level_available = "Level",
                            diversity_available = "Diversity")),
  function(d, lab)
    ggplot(d, aes(x = variant_label, y = n_participants, fill = measure)) +
      geom_col(position = "dodge") +
      labs(title = "Participants with a usable score", subtitle = lab,
           x = NULL, y = "Participants", fill = NULL) +
      theme_minimal() + theme(axis.text.x = element_text(angle = 15, hjust = 1)),
  "MAIN_plot_coverage.png", width = 8, height = 5)
```

# Part 7: Diagnostics

Five design checks, each run for all six combinations rather than only
for the primary one. Running them generically is what makes a
combination-specific problem visible — for instance the news variants
having too few active days to support a stable diversity estimate —
instead of assumed away.

| Diagnostic | Question |
|------------------------------------|------------------------------------|
| A | Does the individual reference date matter versus a shared pre-Wave-1 date? |
| B | Does the 30-day window matter versus full history? |
| C | Does duration weighting matter versus an unweighted mean? |
| D | Is the level distribution skewed enough that median and mean diverge? |
| E | Do qualifying participants actually show repeated source use? |

## Generic builder

Takes the same `flag_col` argument as the main construction step, plus a
reference-date rule and a window rule, so A--C run once per combination
x rule rather than being hard-coded to one variant.

```{r diagnostics-builder}
pid_reference_A <- pid_wave_search %>%
  group_by(pid) %>%
  summarise(reference_date = as.Date(min(search_start)) - 1, .groups = "drop")

pid_reference_B <- tibble(pid = unique(pid_wave_search$pid),
                          reference_date = WAVE1_START_FIXED - 1)

pid_reference_lookup <- list(individual = pid_reference_A, fixed_pre_wave1 = pid_reference_B)

window_start_rules <- list(
  `30day` = function(ref) ref - (BASELINE_WINDOW_DAYS - 1),
  full    = function(ref) rep(DATA_COLLECTION_START, length(ref))
)

build_variant_baseline <- function(flag_col, visits_df, pid_reference,
                                   window_rule, min_active_days) {
  windows <- pid_reference %>%
    mutate(window_start = window_rule(reference_date),
           window_days = as.numeric(reference_date - window_start) + 1)

  visits_window <- visits_df %>%
    inner_join(windows, by = "pid") %>%
    filter(used_date >= window_start, used_date <= reference_date)

  subset <- if (is.na(flag_col)) visits_window
            else visits_window[visits_window[[flag_col]] %in% TRUE, , drop = FALSE]

  activity <- subset %>%
    group_by(pid) %>%
    summarise(n_rows_with_pc1 = sum(!is.na(pc1)),
              n_distinct_pc1 = n_distinct(pc1[!is.na(pc1)]),
              duration_weighted_pc1 = weighted_mean_na(pc1, duration),
              duration_weighted_sd_pc1 = weighted_sd_na(pc1, duration),
              unweighted_pc1 = mean(pc1, na.rm = TRUE),
              .groups = "drop")

  # The threshold always counts ALL visits in the window, not the
  # variant-filtered subset, consistent with the main construction step:
  # "habitual" is defined by overall browsing activity.
  all_active <- visits_window %>%
    group_by(pid) %>% summarise(n_active_days = n_distinct(used_date), .groups = "drop")

  windows %>%
    dplyr::select(pid, window_days) %>%
    left_join(all_active, by = "pid") %>%
    left_join(activity, by = "pid") %>%
    mutate(
      across(c(n_active_days, n_rows_with_pc1, n_distinct_pc1), ~ coalesce(.x, 0L)),
      meets_activity_threshold = n_active_days >= min_active_days,
      across(c(duration_weighted_pc1, duration_weighted_sd_pc1, unweighted_pc1),
             ~ if_else(meets_activity_threshold, .x, NA_real_))
    )
}
```

```{r diagnostics-build-grid}
diag_rules <- tribble(
  ~baseline_version,  ~window_type,  ~min_active_days,
  "individual",       "30day",       MIN_ACTIVE_DAYS,
  "individual",       "full",        MIN_ACTIVE_DAYS_FULL,
  "fixed_pre_wave1",  "30day",       MIN_ACTIVE_DAYS,
  "fixed_pre_wave1",  "full",        MIN_ACTIVE_DAYS_FULL
)

all_habitual <- cross_join(analysis_grid, diag_rules) %>%
  mutate(result = pmap(list(flag_col, channel, baseline_version, window_type, min_active_days),
    function(fc, ch, bv, wt, mad)
      build_variant_baseline(fc, visits_by_channel[[ch]], pid_reference_lookup[[bv]],
                             window_start_rules[[wt]], mad))) %>%
  dplyr::select(channel, channel_label, variant, variant_label,
                baseline_version, window_type, result) %>%
  unnest(result) %>%
  mutate(channel = factor(channel, levels = channel_levels),
         variant = factor(variant, levels = variant_levels))

write_csv(all_habitual, file.path(diagnostics_dir, "diagnostic_all_variants_versions.csv"))
cat("Diagnostic rows (participants x 6 combinations x 4 rules):", nrow(all_habitual), "\n")
```

## A: reference date

The individual date is preferred because it is the only rule that
guarantees each participant's baseline precedes their own first search
task. A high correlation shows that the choice does not materially
change the measure.

```{r diagnostic-a}
all_habitual %>%
  filter(window_type == "30day") %>%
  dplyr::select(pid, channel, variant, baseline_version, duration_weighted_pc1) %>%
  pivot_wider(names_from = baseline_version, values_from = duration_weighted_pc1) %>%
  group_by(channel, variant) %>%
  summarise(n = sum(complete.cases(individual, fixed_pre_wave1)),
            r = round(cor(individual, fixed_pre_wave1, use = "complete.obs"), 3),
            .groups = "drop")
```

## B: window length

```{r diagnostic-b}
agreement_30day_full <- all_habitual %>%
  filter(baseline_version == "individual", window_type == "30day") %>%
  dplyr::select(pid, channel, channel_label, variant, variant_label,
                pc1_30day = duration_weighted_pc1) %>%
  inner_join(all_habitual %>%
               filter(baseline_version == "individual", window_type == "full") %>%
               dplyr::select(pid, channel, variant, pc1_full = duration_weighted_pc1),
             by = c("pid", "channel", "variant")) %>%
  filter(!is.na(pc1_30day), !is.na(pc1_full))

agreement_30day_full %>%
  group_by(channel, variant) %>%
  summarise(n = n(), r = round(cor(pc1_30day, pc1_full), 3), .groups = "drop")
```

```{r diagnostic-b-plot, fig.width=11, fig.height=4.5}
plot_by_channel(
  agreement_30day_full,
  function(d, lab)
    ggplot(d, aes(x = pc1_30day, y = pc1_full)) +
      geom_point(alpha = 0.4) +
      geom_abline(slope = 1, intercept = 0, linetype = "dashed", colour = "firebrick") +
      variant_facets() +
      labs(title = "Quality level: 30-day window versus full history", subtitle = lab,
           x = "30-day duration-weighted PC1", y = "Full-history duration-weighted PC1") +
      theme_minimal(),
  "diagB_window_agreement.png")
```

## C: duration weighting

```{r diagnostic-c}
all_habitual %>%
  filter(baseline_version == "individual", window_type == "30day") %>%
  group_by(channel, variant) %>%
  group_modify(function(df, ...) {
    m <- df %>%
      dplyr::select(unweighted_pc1, duration_weighted_pc1, duration_weighted_sd_pc1) %>%
      filter(complete.cases(.))
    if (nrow(m) < 3) return(tibble(note = "insufficient complete cases"))
    as_tibble(round(cor(m), 3), rownames = "metric")
  }) %>%
  print(n = Inf)
```

## D: median versus mean

```{r diagnostic-d}
habitual_long %>%
  group_by(channel, variant) %>%
  summarise(across(c(duration_weighted_pc1, duration_weighted_sd_pc1),
                   list(median = ~ round(median(.x, na.rm = TRUE), 4),
                        mean   = ~ round(mean(.x, na.rm = TRUE), 4))),
            .groups = "drop")
```

```{r diagnostic-d-plot, fig.width=11, fig.height=4.5}
plot_by_channel(
  habitual_long %>% filter(!is.na(duration_weighted_pc1)) %>%
    group_by(channel, variant_label) %>%
    mutate(med = median(duration_weighted_pc1), avg = mean(duration_weighted_pc1)) %>%
    ungroup(),
  function(d, lab)
    ggplot(d, aes(x = duration_weighted_pc1)) +
      geom_density(fill = "steelblue", alpha = 0.4) +
      geom_vline(aes(xintercept = med), linetype = "dashed", colour = "firebrick") +
      geom_vline(aes(xintercept = avg), linetype = "dotted", colour = "darkgreen") +
      variant_facets() +
      labs(title = "Median (dashed) versus mean (dotted) quality level", subtitle = lab,
           x = "Duration-weighted PC1", y = "Density") +
      theme_minimal(),
  "diagD_median_vs_mean.png")
```

## E: repeated-source behaviour

Computed within each combination's qualifying visits, so a repeat source
for the news variant means a repeatedly visited news source, not a
repeatedly visited domain in general.

```{r diagnostic-e}
compute_repeat_summary <- function(flag_col, visits_df) {
  if (!is.na(flag_col)) visits_df <- visits_df[visits_df[[flag_col]] %in% TRUE, , drop = FALSE]

  visits_df %>%
    filter(!is.na(content_id)) %>%
    count(pid, content_id, name = "n_visits_this_source") %>%
    mutate(is_repeat_source = n_visits_this_source > 1) %>%
    group_by(pid) %>%
    summarise(n_distinct_sources = n(),
              n_repeat_sources = sum(is_repeat_source),
              share_repeat_visits = sum(n_visits_this_source[is_repeat_source]) /
                                    sum(n_visits_this_source),
              has_any_repeat_source = any(is_repeat_source),
              .groups = "drop")
}

habitual_with_repeats <- analysis_grid %>%
  mutate(repeats = map2(flag_col, channel,
                        ~ compute_repeat_summary(.x, visits_baseline[[.y]]))) %>%
  dplyr::select(channel, variant, repeats) %>%
  unnest(repeats) %>%
  right_join(habitual_long %>%
               dplyr::select(pid, channel, channel_label, variant, variant_label,
                             meets_activity_threshold),
             by = c("pid", "channel", "variant")) %>%
  mutate(across(c(n_distinct_sources, n_repeat_sources), ~ coalesce(.x, 0L)),
         share_repeat_visits = coalesce(share_repeat_visits, 0),
         has_any_repeat_source = coalesce(has_any_repeat_source, FALSE))

write_csv(habitual_with_repeats,
          file.path(diagnostics_dir, "diagnostic_repeat_visits_all_variants.csv"))

qualifying <- habitual_with_repeats %>% filter(meets_activity_threshold)

qualifying %>%
  group_by(channel, variant) %>%
  summarise(n_qualifying = n(),
            n_with_repeat_source = sum(has_any_repeat_source),
            median_share_repeat = round(median(share_repeat_visits, na.rm = TRUE), 3),
            .groups = "drop")
```

```{r diagnostic-e-plot, fig.width=11, fig.height=4.5}
plot_by_channel(
  qualifying,
  function(d, lab)
    ggplot(d, aes(x = share_repeat_visits)) +
      geom_histogram(binwidth = 0.05, fill = "darkorange", alpha = 0.7, boundary = 0) +
      variant_facets() +
      labs(title = "Share of visits to repeatedly visited sources", subtitle = lab,
           x = "Share of repeat-source visits", y = "Participants") +
      theme_minimal(),
  "diagE_repeat_source_share.png")
```

## F: log-duration weighting versus raw duration weighting

Session duration in tracking data is heavily right-skewed and
approximately log-normally distributed (Meiss et al., 2009; Brinberg et
al., 2022), so a few very long sessions -- idle tabs, autoplay,
background windows -- can dominate a linearly duration-weighted average.
This checks whether that matters here: level is recomputed with
`log1p(duration)` as the weight and correlated against the raw-weighted
version, per variant. `log1p()` avoids the `log(0)` problem without an
arbitrary epsilon.

```{r diagnostic-f-logweight}
weighted_mean_log_na <- function(x, w) {
  keep <- !is.na(x) & !is.na(w) & w > 0
  if (!any(keep)) return(NA_real_)
  w_log <- log1p(w[keep])
  sum(x[keep] * w_log) / sum(w_log)
}

# Takes the channel name and indexes straight into visits_baseline, which is
# already channel-split and window-filtered -- same input as the main build.
build_variant_logw <- function(channel, flag_col) {
  v <- visits_baseline[[channel]]
  v <- if (is.na(flag_col)) v else v[v[[flag_col]] %in% TRUE, , drop = FALSE]

  v %>%
    group_by(pid) %>%
    summarise(log_duration_weighted_pc1 = weighted_mean_log_na(pc1, duration),
              .groups = "drop")
}

habitual_logw <- analysis_grid %>%
  mutate(activity = map2(channel, flag_col, build_variant_logw)) %>%
  dplyr::select(channel, variant, activity) %>%
  unnest(activity)

logw_compare <- habitual_long %>%
  dplyr::select(pid, channel, variant, variant_label,
                meets_activity_threshold, duration_weighted_pc1) %>%
  left_join(habitual_logw, by = c("pid", "channel", "variant")) %>%
  mutate(log_duration_weighted_pc1 =
           if_else(meets_activity_threshold, log_duration_weighted_pc1, NA_real_))

# Guard against the fan-out that produced n > 791 in the first run.
stopifnot(nrow(logw_compare) == nrow(habitual_long))

cat("Raw vs. log-duration-weighted level, per channel and variant:\n")
logw_compare %>%
  filter(!is.na(duration_weighted_pc1), !is.na(log_duration_weighted_pc1)) %>%
  group_by(channel, variant, variant_label) %>%
  summarise(n = n(),
            r = round(cor(duration_weighted_pc1, log_duration_weighted_pc1), 3),
            mean_abs_diff = round(mean(abs(duration_weighted_pc1 - log_duration_weighted_pc1)), 4),
            .groups = "drop") %>%
  print()

write_csv(logw_compare, file.path(diagnostics_dir, "diagF_log_weighting.csv"))
```

```{r diagnostic-f-plot, fig.width=12, fig.height=7}
p_logw <- logw_compare %>%
  filter(!is.na(duration_weighted_pc1), !is.na(log_duration_weighted_pc1)) %>%
  ggplot(aes(x = duration_weighted_pc1, y = log_duration_weighted_pc1)) +
  geom_point(alpha = 0.4) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "firebrick") +
  facet_grid(channel ~ variant_label) +
  labs(title = "Quality level: raw vs. log-duration weighting",
       x = "Duration-weighted PC1", y = "Log-duration-weighted PC1") +
  theme_minimal()

print(p_logw)
ggsave(file.path(diagnostics_dir, "diagF_logweight_faceted.png"), p_logw, width = 12, height = 7)
```

**Reading rule.** `r` above roughly .95 means the weighting choice does
not materially reorder participants; keep raw duration-weighting for
interpretability and note the check in one sentence. Markedly lower `r`
means a minority of extreme sessions is driving that variant's score,
and the log-weighted version should be carried forward as a reported
robustness check.

```{r diagnostic-f-split-agreement}
split_agreement <- logw_compare %>%
  filter(!is.na(duration_weighted_pc1), !is.na(log_duration_weighted_pc1)) %>%
  group_by(channel, variant, variant_label) %>%
  mutate(
    split_raw = if_else(duration_weighted_pc1     <= median(duration_weighted_pc1),     "low", "high"),
    split_log = if_else(log_duration_weighted_pc1 <= median(log_duration_weighted_pc1), "low", "high")
  ) %>%
  summarise(
    n            = n(),
    n_agree      = sum(split_raw == split_log),
    pct_agree    = round(100 * mean(split_raw == split_log), 1),
    n_switch     = sum(split_raw != split_log),
    .groups = "drop"
  )

cat("Median-split agreement, raw vs. log weighting:\n")
print(split_agreement)
write_csv(split_agreement, file.path(diagnostics_dir, "diagF_split_agreement.csv"))
```

```{r diagnostic-f-export-split}
# Exported so 03b can re-run the moderation with the alternative weighting.
logw_split <- logw_compare %>%
  filter(!is.na(log_duration_weighted_pc1)) %>%
  group_by(channel, variant) %>%
  mutate(habitual_diet_logw = if_else(
    log_duration_weighted_pc1 <= median(log_duration_weighted_pc1), "low", "high")) %>%
  ungroup() %>%
  dplyr::select(pid, channel, variant,
                log_duration_weighted_pc1, habitual_diet_logw)

write_csv(logw_split, file.path(output_dir, "habitual_logweighted_split.csv"))
cat("Exported log-weighted level and split for", n_distinct(logw_split$pid), "participants\n")
```


```{r diagnostic-f2-duration-distribution}
dur_check_hab <- bind_rows(visits_baseline) %>%
  as_tibble() %>%
  filter(!is.na(pc1))

cat("Duration distribution of scored baseline visits (seconds):\n")
dur_check_hab %>%
  summarise(n = n(),
            min = min(duration, na.rm = TRUE),
            p25 = quantile(duration, .25, na.rm = TRUE),
            median = median(duration, na.rm = TRUE),
            p75 = quantile(duration, .75, na.rm = TRUE),
            p95 = quantile(duration, .95, na.rm = TRUE),
            p99 = quantile(duration, .99, na.rm = TRUE),
            max = max(duration, na.rm = TRUE),
            n_zero = sum(duration == 0, na.rm = TRUE)) %>%
  print(width = Inf)

cat("\nVisits above plausible reading thresholds:\n")
dur_check_hab %>%
  summarise(n = n(),
            over_30min = sum(duration > 1800, na.rm = TRUE),
            over_1h    = sum(duration > 3600, na.rm = TRUE),
            over_3h    = sum(duration > 10800, na.rm = TRUE),
            over_8h    = sum(duration > 28800, na.rm = TRUE),
            pct_over_30min = round(100 * mean(duration > 1800, na.rm = TRUE), 2),
            share_of_total_time_over_30min =
              round(100 * sum(duration[duration > 1800], na.rm = TRUE) /
                      sum(duration, na.rm = TRUE), 1)) %>%
  print(width = Inf)

# Same, split by diet definition -- the overall diet was the most
# weighting-sensitive variant in Diagnostic F.
cat("\nBy diet definition:\n")
bind_rows(
  dur_check_hab %>% mutate(variant = "overall"),
  dur_check_hab %>% filter(is_news %in% TRUE) %>% mutate(variant = "news"),
  dur_check_hab %>% filter(is_news_corrected %in% TRUE) %>% mutate(variant = "news_corrected")
) %>%
  group_by(variant) %>%
  summarise(n = n(),
            median = median(duration, na.rm = TRUE),
            p99 = quantile(duration, .99, na.rm = TRUE),
            max = max(duration, na.rm = TRUE),
            pct_over_30min = round(100 * mean(duration > 1800, na.rm = TRUE), 2),
            share_time_over_30min =
              round(100 * sum(duration[duration > 1800], na.rm = TRUE) /
                      sum(duration, na.rm = TRUE), 1),
            .groups = "drop") %>%
  print(width = Inf)
```
## G: Capping
```{r diagnostic-g-capping}
# Capping addresses a measurement artefact: sessions of several hours are
# parked tabs, not reading time. Unlike the log transformation, capping
# leaves the 97% of unremarkable visits untouched and keeps the measure
# interpretable as quality per unit of browsing time.
caps <- c("cap_30min" = 1800L, "cap_1h" = 3600L, "cap_3h" = 10800L)

build_variant_capped <- function(channel, flag_col, cap_seconds) {
  v <- visits_baseline[[channel]]
  v <- if (is.na(flag_col)) v else v[v[[flag_col]] %in% TRUE, , drop = FALSE]

  v %>%
    mutate(duration_capped = pmin(duration, cap_seconds)) %>%
    group_by(pid) %>%
    summarise(level_capped = weighted_mean_na(pc1, duration_capped),
              .groups = "drop")
}

capped_levels <- purrr::imap_dfr(caps, function(cap_seconds, cap_label) {
  analysis_grid %>%
    mutate(activity = map2(channel, flag_col, build_variant_capped,
                           cap_seconds = cap_seconds)) %>%
    dplyr::select(channel, variant, activity) %>%
    unnest(activity) %>%
    mutate(cap = cap_label)
})

cap_compare <- habitual_long %>%
  dplyr::select(pid, channel, variant, variant_label,
                meets_activity_threshold, duration_weighted_pc1) %>%
  left_join(capped_levels, by = c("pid", "channel", "variant"),
            relationship = "one-to-many") %>%
  mutate(level_capped = if_else(meets_activity_threshold, level_capped, NA_real_)) %>%
  filter(!is.na(duration_weighted_pc1), !is.na(level_capped))
```

```{r diagnostic-g-time-affected}
# How much weight is actually removed at each threshold?
cat("Share of weighted time removed by capping, by variant:\n")
bind_rows(
  dur_check_hab %>% mutate(variant = "overall"),
  dur_check_hab %>% filter(is_news %in% TRUE) %>% mutate(variant = "news"),
  dur_check_hab %>% filter(is_news_corrected %in% TRUE) %>% mutate(variant = "news_corrected")
) %>%
  group_by(variant) %>%
  summarise(
    n_visits = n(),
    pct_visits_capped_30min = round(100 * mean(duration > 1800), 2),
    pct_visits_capped_1h    = round(100 * mean(duration > 3600), 2),
    pct_visits_capped_3h    = round(100 * mean(duration > 10800), 2),
    pct_time_removed_30min  = round(100 * (1 - sum(pmin(duration, 1800))  / sum(duration)), 1),
    pct_time_removed_1h     = round(100 * (1 - sum(pmin(duration, 3600))  / sum(duration)), 1),
    pct_time_removed_3h     = round(100 * (1 - sum(pmin(duration, 10800)) / sum(duration)), 1),
    .groups = "drop"
  ) %>%
  as.data.frame() %>% print()
```

```{r diagnostic-g-level-agreement}
cat("\nCapped vs. uncapped level, by cap and variant (with_apps only):\n")
cap_compare %>%
  filter(channel == "with_apps") %>%
  group_by(cap, variant, variant_label) %>%
  summarise(n = n(),
            r = round(cor(duration_weighted_pc1, level_capped), 3),
            mean_diff = round(mean(level_capped - duration_weighted_pc1), 4),
            mean_abs_diff = round(mean(abs(level_capped - duration_weighted_pc1)), 4),
            .groups = "drop") %>%
  arrange(variant, cap) %>%
  as.data.frame() %>% print()
```

```{r diagnostic-g-split-agreement}
# The moderation analysis uses the median split, so this is the comparison
# that decides whether the choice of threshold matters substantively.
cat("\nMedian-split agreement, capped vs. uncapped:\n")
cap_compare %>%
  group_by(channel, cap, variant, variant_label) %>%
  mutate(split_uncapped = if_else(duration_weighted_pc1 <= median(duration_weighted_pc1), "low", "high"),
         split_capped   = if_else(level_capped          <= median(level_capped),          "low", "high")) %>%
  summarise(n = n(),
            pct_agree = round(100 * mean(split_uncapped == split_capped), 1),
            n_switch  = sum(split_uncapped != split_capped),
            .groups = "drop") %>%
  arrange(channel, variant, cap) %>%
  as.data.frame() %>% print()

# And the comparison that decides whether the threshold itself is an
# analytic fork: do the three caps agree with each other?
cat("\nAgreement between cap thresholds (with_apps):\n")
cap_compare %>%
  filter(channel == "with_apps") %>%
  dplyr::select(pid, variant, variant_label, cap, level_capped) %>%
  pivot_wider(names_from = cap, values_from = level_capped) %>%
  group_by(variant, variant_label) %>%
  summarise(n = n(),
            r_30min_vs_1h = round(cor(cap_30min, cap_1h), 4),
            r_1h_vs_3h    = round(cor(cap_1h, cap_3h), 4),
            r_30min_vs_3h = round(cor(cap_30min, cap_3h), 4),
            .groups = "drop") %>%
  as.data.frame() %>% print()

write_csv(cap_compare, file.path(diagnostics_dir, "diagG_capping_comparison.csv"))
```
# Part 8: Which Definition Carries the Most Information

"Most information" is not one number. It trades off how many
participants get a usable score, how much that score varies across
participants, how stable it is against arbitrary design choices, and —
once an outcome exists — how strongly it relates to that outcome. The
table assembles the design-stage criteria.

```{r variant-comparison}
variant_comparison <- habitual_long %>%
  group_by(channel, channel_label, variant, variant_label) %>%
  summarise(
    n_participants          = n(),
    n_meets_activity        = sum(meets_activity_threshold),
    pct_level_available     = round(100 * sum(!is.na(duration_weighted_pc1)) / n(), 1),
    pct_diversity_available = round(100 * sum(!is.na(duration_weighted_sd_pc1)) / n(), 1),
    sd_level                = round(sd(duration_weighted_pc1, na.rm = TRUE), 4),
    sd_diversity            = round(sd(duration_weighted_sd_pc1, na.rm = TRUE), 4),
    median_n_rows_with_pc1  = median(n_rows_with_pc1),
    .groups = "drop"
  ) %>%
  left_join(agreement_30day_full %>%
              group_by(channel, variant) %>%
              summarise(stability_30day_vs_full_r = round(cor(pc1_30day, pc1_full), 3),
                        .groups = "drop"),
            by = c("channel", "variant"))

variant_comparison
write_csv(variant_comparison, file.path(channel_dirs[["with_apps"]],
                                        "habitual_media_diet_variant_comparison.csv"))
```

```{r variant-comparison-plot, fig.width=9, fig.height=5}
plot_by_channel(
  variant_comparison %>%
    dplyr::select(channel, variant_label, pct_level_available,
                  pct_diversity_available, sd_level, sd_diversity) %>%
    pivot_longer(-c(channel, variant_label), names_to = "criterion", values_to = "value") %>%
    mutate(criterion_group = if_else(grepl("^pct_", criterion),
                                     "Coverage (% participants)", "Variance (SD)"),
           criterion = if_else(grepl("level", criterion), "Level", "Diversity")),
  function(d, lab)
    ggplot(d, aes(x = variant_label, y = value, fill = criterion)) +
      geom_col(position = "dodge") +
      facet_wrap(~ criterion_group, scales = "free_y") +
      labs(title = "Coverage and variance trade-off", subtitle = lab,
           x = NULL, y = NULL, fill = NULL) +
      theme_minimal() + theme(axis.text.x = element_text(angle = 15, hjust = 1)),
  "MAIN_plot_variant_comparison.png", width = 9, height = 5)
```

# Final notes

| Analysis purpose | Variable in the wide file |
|------------------------------------|------------------------------------|
| Broad scored information diet | `hab_overall_dw_pc1`, `hab_overall_dw_sd_pc1` |
| Sensitivity to the automated coding | `hab_news_dw_pc1`, `hab_news_dw_sd_pc1` |
| Primary news-quality analysis | `hab_news_corrected_dw_pc1`, `hab_news_corrected_dw_sd_pc1` |
| Descriptive subgroup analysis only | `hab_<variant>_level_group`, `hab_<variant>_diversity_group`, `hab_<variant>_level_diversity_group` |
| App-traffic robustness | the same measures from the `without_apps` directory |

Every one of these is a **pre-treatment** measure. None of them may be
used as an endogenous exposure or as a mediator in `03b`--`03e`; that
role belongs to the `exp_` measures from `03a`.

Before using a news-specific diversity measure in a model, check
`pct_diversity_available`. Diversity requires at least two distinct PC1
values among the relevant visits, so its sample can be smaller than the
sample for level.
