---
title: "Survey Outcomes: Attitude and Knowledge Change"
author: "Master's Thesis -- Media Quality / Media Diet"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE)
```

# Overview

Rebuilds the outcome variables from the underlying survey items and
verifies them against the supplied difference scores. Same rule as for
uptake in `02b`: a supplied variable is not used in a model until its
construction has been reproduced (Appendix A.2, A.4).

Four stages:

1. Identify the pre- and post-items and record their German wording
2. Reconstruct signed and absolute attitude change (Eq. 3.7, 3.8)
3. Compare against `gen_pol_attitude_topic_diff` and explain discrepancies
4. Repeat for the knowledge outcome

Everything is at `pid` x `wave`, restricted to the analysis samples, so the
output joins directly onto the uptake and quality files from `02b`.

## Outputs

| Object | Role |
|---|---|
| `attitude_outcomes_by_wave.Rds` / `.csv` | Reconstructed outcomes at `pid` x `wave` |
| `outcome_item_wording.csv` | German item wording and coding, for Appendix A.4 |
| `outcome_reconstruction_check.csv` | Row-level comparison against the supplied variables |

## Design choices

| Choice | Rule | Reason |
|---|---|---|
| Primary outcome | absolute change | Hypotheses concern amount of updating, not direction (Sec. 3.7) |
| Secondary outcome | signed change | Distinguishes movement towards from away from support |
| Scale | 1--7, 4 = neutral | 1 = should not be introduced, 7 = should be introduced |
| Reconstruction | from raw items | The supplied difference is verified, not assumed |
| Sample | analysis samples only | Shares a denominator with the `02b` measures |

# Part 1: Setup

```{r libraries}
library(dplyr)
library(tidyr)
library(readr)
library(stringr)
library(purrr)
```

```{r, include=FALSE}
project_root <- "~/Desktop/GitHub/DoesMediaQualityMatter"
data_dir     <- "~/Desktop/Masterarbeit/Data"
```

```{r paths-config}
#project_root <- "DoesMediaQualityMatter"
#data_dir     <- "Data"
input_dir <- file.path(project_root, "Output", "00_setup")
output_dir <- file.path(project_root, "Output", "02c_outcomes")
dir.create(output_dir, showWarnings = FALSE, recursive = TRUE)

load(file.path(data_dir, "df1_final_ac.Rdata"))
load(file.path(data_dir, "df2_final_ac.Rdata"))
load(file.path(data_dir, "df3_final_ac.Rdata"))

waves <- list("1" = df1, "2" = df2, "3" = df3)

wave_topics <- c("1" = "Basic child support",
                 "2" = "Renewable-energy transition",
                 "3" = "Cannabis legalisation")

analysis_pids <- imap_dfr(waves, function(d, w) {
  tibble(pid = as.character(d$pid), wave = as.integer(w))
}) %>%
  distinct(pid, wave)

cat("Analysis participant-waves:", nrow(analysis_pids), "\n")
analysis_pids %>% count(wave, name = "n") %>% print()
```

# Part 2: Identifying the Items

Run this first. The value range separates the 1--7 attitude items from
derived scores that share part of the name.

```{r item-discovery}
candidates <- imap_dfr(waves, function(d, w) {
  tibble(wave = as.integer(w), var = names(d)) %>%
    filter(str_detect(var, regex("attitude|einstellung|pol_att|knowledge|wissen",
                                 ignore_case = TRUE)))
})

cat("Outcome-related columns per wave:\n")
candidates %>% count(wave, var) %>% print(n = Inf)

cat("\nRange and type of each candidate:\n")
imap_dfr(waves, function(d, w) {
  vars <- candidates$var[candidates$wave == as.integer(w)]
  tibble(wave = as.integer(w), var = vars) %>%
    mutate(info = map_chr(vars, function(v) {
      x <- d[[v]]
      if (!is.numeric(x)) return(paste0("non-numeric (", class(x)[1], ")"))
      sprintf("%.2f to %.2f | %d distinct | %d NA",
              min(x, na.rm = TRUE), max(x, na.rm = TRUE),
              n_distinct(x, na.rm = TRUE), sum(is.na(x)))
    }))
}) %>%
  as.data.frame() %>% print()
```

The lookup sheets carry the German wording required by Appendix A.4.


# Part 3: Reconstruction

Fill in the item names identified in Part 2.

```{r item-config}
OUTCOME_ITEMS <- tribble(
  ~wave, ~att_pre,                     ~att_post,                     ~kno_pre,            ~kno_post,
  1L,    "gen_pol_attitude_topic_pre", "gen_pol_attitude_topic_post", "gen_knowledge_pre", "gen_knowledge_post",
  2L,    "gen_pol_attitude_topic_pre", "gen_pol_attitude_topic_post", "gen_knowledge_pre", "gen_knowledge_post",
  3L,    "gen_pol_attitude_topic_pre", "gen_pol_attitude_topic_post", "gen_knowledge_pre", "gen_knowledge_post"
)

# Fail early with a readable message rather than inside pmap.
walk2(OUTCOME_ITEMS$wave,
      asplit(as.matrix(OUTCOME_ITEMS[-1]), 1),
      function(w, items) {
        missing <- setdiff(items, names(waves[[as.character(w)]]))
        if (length(missing) > 0)
          stop("Wave ", w, ": columns not found -- ", paste(missing, collapse = ", "))
      })
```

```{r reconstruct-outcomes}
# The wave files are haven-labelled, and the label attributes differ across
# waves, so stacking them fails. unclass() strips the class, as.numeric()
# the remaining attributes. The German wording is documented separately (A.4).
num <- function(x) as.numeric(unclass(x))

outcomes <- pmap_dfr(OUTCOME_ITEMS, function(wave, att_pre, att_post, kno_pre, kno_post) {
  d <- waves[[as.character(wave)]]
  tibble(
    pid      = as.character(d$pid),
    wave     = wave,
    att_pre  = num(d[[att_pre]]),
    att_post = num(d[[att_post]]),
    kno_pre  = num(d[[kno_pre]]),
    kno_post = num(d[[kno_post]]),
    supplied_att     = num(d$gen_pol_attitude_topic_diff),
    supplied_kno     = num(d$gen_knowledge_diff),
    # Candidate absolute measure: no *_diff_abs column exists in the wave
    # files, so the absolute outcome used so far was derived in 03a.
    supplied_att_chg = num(d$gen_pol_attitude_topic_change_diff),
    att_pre_change   = num(d$gen_pol_attitude_topic_pre_change),
    att_post_change  = num(d$gen_pol_attitude_topic_post_change)
  )
}) %>%
  mutate(att_signed = att_post - att_pre,
         att_abs    = abs(att_post - att_pre),
         kno_signed = kno_post - kno_pre)

stopifnot(all(is.na(outcomes$att_pre)  | between(outcomes$att_pre,  1, 7)))
stopifnot(all(is.na(outcomes$att_post) | between(outcomes$att_post, 1, 7)))
stopifnot(nrow(outcomes) == nrow(analysis_pids))

cat("Reconstructed outcomes for", nrow(outcomes), "participant-waves\n")
```


```{r clarify-second-item-family}
# Two attitude item families exist. Establish which one the supplied
# difference is built from before either is used as the outcome.
cat("Do the two families hold the same values?\n")
outcomes %>%
  group_by(wave) %>%
  summarise(n = n(),
            pre_identical  = round(100 * mean(att_pre  == att_pre_change,  na.rm = TRUE), 1),
            post_identical = round(100 * mean(att_post == att_post_change, na.rm = TRUE), 1),
            r_pre  = round(cor(att_pre,  att_pre_change,  use = "complete.obs"), 3),
            r_post = round(cor(att_post, att_post_change, use = "complete.obs"), 3),
            .groups = "drop") %>%
  as.data.frame() %>% print()

cat("\nIs gen_pol_attitude_topic_change_diff the absolute difference?\n")
outcomes %>%
  group_by(wave) %>%
  summarise(n = n(),
            matches_abs_of_main = round(100 * mean(supplied_att_chg == att_abs, na.rm = TRUE), 1),
            matches_abs_of_chg  = round(100 * mean(
              supplied_att_chg == abs(att_post_change - att_pre_change), na.rm = TRUE), 1),
            .groups = "drop") %>%
  as.data.frame() %>% print()
```

# Part 4: Comparison Against the Supplied Variables

```{r comparison-attitude}
compare_one <- function(df, recon_var, supplied_var, label) {
  df %>%
    filter(!is.na(.data[[recon_var]]), !is.na(.data[[supplied_var]])) %>%
    group_by(wave) %>%
    summarise(n             = n(),
              pct_identical = round(100 * mean(.data[[recon_var]] == .data[[supplied_var]]), 1),
              max_abs_diff  = max(abs(.data[[recon_var]] - .data[[supplied_var]])),
              r             = round(cor(.data[[recon_var]], .data[[supplied_var]]), 4),
              .groups = "drop") %>%
    mutate(outcome = label)
}

bind_rows(
  compare_one(outcomes, "att_signed", "supplied_att",     "attitude, signed"),
  compare_one(outcomes, "att_abs",    "supplied_att_chg", "attitude, absolute (candidate)"),
  compare_one(outcomes, "kno_signed", "supplied_kno",     "knowledge, signed")
)%>%
  select(outcome, wave, n, pct_identical, max_abs_diff, r) %>%
  as.data.frame() %>% print()
```

Missingness is checked in both directions. Cases where the supplied
variable exists but the items do not would mean the reconstruction is
incomplete rather than merely different.

```{r comparison-missingness}
outcomes %>%
  group_by(wave) %>%
  summarise(n = n(),
            items_only    = sum(!is.na(att_signed) & is.na(supplied_att)),
            supplied_only = sum(is.na(att_signed) & !is.na(supplied_att)),
            both          = sum(!is.na(att_signed) & !is.na(supplied_att)),
            neither       = sum(is.na(att_signed) & is.na(supplied_att)),
            .groups = "drop") %>%
  as.data.frame() %>% print()
```

Appendix A.4 requires discrepancies to be explained. A constant gap points
at a sign convention or a reversed item; a varying gap points at a
different pre-measure, for example a baseline taken from T0 rather than
from the wave's own pre-questionnaire.

```{r comparison-discrepancies}
mismatches <- outcomes %>%
  filter(!is.na(att_signed), !is.na(supplied_att), att_signed != supplied_att)

cat("Mismatching attitude cases:", nrow(mismatches), "\n")

if (nrow(mismatches) > 0) {
  cat("\nDistribution of the gap (reconstructed minus supplied):\n")
  print(table(mismatches$att_signed - mismatches$supplied_att))

  cat("\nMost frequent mismatch patterns:\n")
  mismatches %>%
    count(wave, att_pre, att_post, att_signed, supplied_att, sort = TRUE) %>%
    head(20) %>% as.data.frame() %>% print()
}
```

```{r outcome-distributions}
cat("Distribution of reconstructed signed attitude change:\n")
outcomes %>%
  filter(!is.na(att_signed)) %>%
  count(wave, att_signed) %>%
  pivot_wider(names_from = wave, values_from = n,
              names_prefix = "wave_", values_fill = 0L) %>%
  arrange(att_signed) %>%
  as.data.frame() %>% print()

cat("\nSummary by wave:\n")
outcomes %>%
  filter(!is.na(att_signed)) %>%
  group_by(wave) %>%
  summarise(n = n(),
            mean_pre    = round(mean(att_pre), 2),
            mean_post   = round(mean(att_post), 2),
            mean_signed = round(mean(att_signed), 3),
            mean_abs    = round(mean(att_abs), 3),
            pct_no_change = round(100 * mean(att_signed == 0), 1),
            .groups = "drop") %>%
  mutate(topic = wave_topics[as.character(wave)]) %>%
  as.data.frame() %>% print()
```

# Part 5: Saving

```{r save}
write_csv(outcomes, file.path(output_dir, "outcome_reconstruction_check.csv"))

outcomes_final <- outcomes %>%
  select(pid, wave, att_pre, att_post, att_signed, att_abs, kno_pre, kno_post, kno_signed)

saveRDS(outcomes_final, file.path(output_dir, "attitude_outcomes_by_wave.Rds"))
write_csv(outcomes_final, file.path(output_dir, "attitude_outcomes_by_wave.csv"))

cat("Saved", nrow(outcomes_final), "participant-waves\n")
```
