---
title: "Analysis Dataset Assembly"
author: "Master's Thesis -- Media Quality / Media Diet"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning = FALSE, message = TRUE)
```

# Overview

Merges the four construct files from `02a`--`02c` with the wave survey files
into one analysis dataset per wave. This is the only place where merging
happens; `03b` estimates and never joins.

Concentrating the merge here is deliberate. In the earlier pipeline the
same exposure was merged in five separate scripts, and a pre-treatment
habitual measure was silently substituted for the experimental exposure in
three of them (Appendix G). The assertions in Part 5 make that failure mode
impossible to repeat: prefixes are disjoint, row counts are checked, and
every variable's non-missing count is verified against its expected coverage
before the file is saved.

## Inputs

| Source | File | Level |
|---|---|---|
| `02a` | `habitual_media_diet_FINAL.csv` | `pid` |
| `02b` | `experimental_topic_uptake_by_wave.Rds` | `pid` x `wave` |
| `02b` | `experimental_quality_by_wave.Rds` | `pid` x `wave` |
| `02c` | `attitude_outcomes_by_wave.Rds` | `pid` x `wave` |
| survey | `df1`--`df3` | `pid`, one file per wave |

## Output

| Object | Content |
|---|---|
| `analysis_data_by_wave.Rds` | Named list of three data frames, one per wave |
| `analysis_data_wave{1,2,3}.csv` | The same, flat, for inspection |
| `variable_roles.csv` | Every analysis variable with its role and expected coverage |

## Naming convention

Prefixes are disjoint by construction, so a habitual measure can never be
mistaken for an experimental one.

| Prefix | Timing | Role |
|---|---|---|
| `hab_` | 30 days before the wave's search task | Moderator, pre-treatment |
| `exp_` | During the wave's information period | Exposure and mediator, post-treatment |
| `att_`, `kno_` | Pre and post survey blocks of the wave | Outcomes |
| none | Baseline survey or assignment | Treatment, covariates |

# Part 1: Setup

```{r libraries, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(readr)
library(purrr)
library(stringr)
```

```{r paths-config, echo=FALSE}
project_root <- "~/Desktop/GitHub/DoesMediaQualityMatter"
data_dir     <- "~/Desktop/Masterarbeit/Data"

dir_02a <- file.path(project_root, "Output", "02_media_quality/habitual_media_diet_baseline")
dir_02b <- file.path(project_root, "Output", "02a_experimental_visits")
dir_02c <- file.path(project_root, "Output", "02c_outcomes")
output_dir <- file.path(project_root, "Output", "03_analysis_data")
dir.create(output_dir, showWarnings = FALSE, recursive = TRUE)

load(file.path(data_dir, "df1_final_ac.Rdata"))
load(file.path(data_dir, "df2_final_ac.Rdata"))
load(file.path(data_dir, "df3_final_ac.Rdata"))

waves <- list("1" = df1, "2" = df2, "3" = df3)
```

```{r config-constants}
WAVE_TOPICS <- c("1" = "Basic child support",
                 "2" = "Renewable-energy transition",
                 "3" = "Cannabis legalisation")

# Habitual diet definitions carried through the whole analysis (Sec. 4.10).
DIET_VARIANTS <- c("overall", "news", "news_corrected")

# Two-item NFC short form, used only in the Section 4.10 sensitivity check.
NFC_ITEMS <- c("cog_nfc1", "cog_nfc2")

num <- function(x) as.numeric(unclass(x))
```

# Part 2: Analysis Samples

```{r analysis-pids}
analysis_pids <- imap_dfr(waves, function(d, w) {
  tibble(pid = as.character(d$pid), wave = as.integer(w))
}) %>%
  distinct(pid, wave)

stopifnot(!any(duplicated(analysis_pids)))
analysis_pids %>% count(wave, name = "n") %>% as.data.frame() %>% print()
```

# Part 3: Treatment, Outcomes, and Covariates from the Survey Files

Treatment is taken from `group_f` and recoded into the two instruments used
in the IV models. `z_verbal` and `z_money` each compare one arm against
control and set the other arm to `NA`, so that each instrument identifies a
single contrast.

Covariates follow Table 3.1. Baseline attitude and prior issue engagement
are wave-specific; the rest come from the baseline survey.

```{r survey-variables}
survey_vars <- imap_dfr(waves, function(d, w) {
  tibble(
    pid  = as.character(d$pid),
    wave = as.integer(w),

    # Treatment and instruments
    group_f  = d$group_f,
    z_verbal = case_when(d$group_f == "control" ~ 0L,
                         d$group_f == "verbal"  ~ 1L,
                         TRUE ~ NA_integer_),
    z_money  = case_when(d$group_f == "control"  ~ 0L,
                         d$group_f == "monetary" ~ 1L,
                         TRUE ~ NA_integer_),

    # Covariates (Table 3.1)
    att_baseline        = num(d$gen_pol_attitude_topic_pre),
    prior_engagement    = num(d$SR_visit_internet_pre),
    polknow_total       = num(d$polknow_total),
    pol_interest_general = num(d$pol_interest_general),
    newsuse_online      = num(d$newsuse_online),
    edu_time            = num(d$edu_time),
    age                 = num(d$age),
    gender_f            = as.factor(d$gender_f),

    # Supplied uptake, retained for the Appendix A.2 comparison only
    url_int_visits_yn = num(d$url_int_visits_yn)
  )
})

stopifnot(nrow(survey_vars) == nrow(analysis_pids))

cat("Instrument coding by wave:\n")
survey_vars %>%
  count(wave, group_f, z_verbal, z_money) %>%
  as.data.frame() %>% print()

cat("\nCovariate missingness (Table 3.1 covariates should be complete):\n")
survey_vars %>%
  group_by(wave) %>%
  summarise(across(c(att_baseline, prior_engagement, polknow_total,
                     pol_interest_general, newsuse_online, edu_time, age),
                   ~ sum(is.na(.x))),
            gender_f = sum(is.na(gender_f)),
            .groups = "drop") %>%
  as.data.frame() %>% print()
```

## Need for cognition

Measured once per participant at study entry, so it is available in the
wave file where a participant first appears and missing in later ones. It
is reconstructed here as a person-level constant and used only in the
Section 4.10 sensitivity analysis, not in the main covariate set: the two
items correlate at r = .44 (Spearman-Brown .61), and including it would
drop 107 participants from models that are already small.

```{r need-for-cognition}
nfc_baseline <- imap_dfr(waves, function(d, w) {
  tibble(pid = as.character(d$pid), wave = as.integer(w),
         cog_nfc1 = num(d[[NFC_ITEMS[1]]]),
         cog_nfc2 = num(d[[NFC_ITEMS[2]]]))
}) %>%
  filter(!is.na(cog_nfc1), !is.na(cog_nfc2)) %>%
  arrange(pid, wave) %>%
  distinct(pid, .keep_all = TRUE) %>%
  transmute(pid, nfc = rowMeans(cbind(cog_nfc1, cog_nfc2)),
            nfc_item1 = cog_nfc1, nfc_item2 = cog_nfc2)

cat("NFC available for", nrow(nfc_baseline), "participants\n")
cat("Two-item correlation:", round(cor(nfc_baseline$nfc_item1,
                                       nfc_baseline$nfc_item2), 3), "\n")
r_nfc <- cor(nfc_baseline$nfc_item1, nfc_baseline$nfc_item2)
cat("Spearman-Brown reliability:", round(2 * r_nfc / (1 + r_nfc), 3), "\n")
```

# Part 4: Construct Files

Habitual measures are renamed with a `hab_` prefix on read, before they can
reach any downstream object. The habitual file is at participant level and
is joined to every wave.

```{r load-constructs}
# Already wide and hab_-prefixed, one row per participant.
hab_keep <- as.vector(outer(
  DIET_VARIANTS,
  c("_dw_pc1", "_dw_sd_pc1", "_level_group", "_diversity_group",
    "_level_diversity_group"),
  function(v, s) paste0("hab_", v, s)))

habitual <- read_csv(file.path(dir_02a, "habitual_media_diet_FINAL.csv"),
                     show_col_types = FALSE) %>%
  mutate(pid = as.character(pid)) %>%
  select(pid, meets_activity_threshold, all_of(hab_keep))

stopifnot(!any(duplicated(habitual$pid)))

uptake   <- readRDS(file.path(dir_02b, "experimental_topic_uptake_by_wave.Rds"))
quality  <- readRDS(file.path(dir_02b, "experimental_quality_by_wave.Rds"))
outcomes <- readRDS(file.path(dir_02c, "attitude_outcomes_by_wave.Rds"))

cat("habitual:", nrow(habitual), "participants |",
    "uptake:", nrow(uptake), "| quality:", nrow(quality),
    "| outcomes:", nrow(outcomes), "participant-waves\n")

# Prefixes must stay disjoint (Appendix G).
stopifnot(!any(str_starts(names(habitual)[-1], "exp_")))
stopifnot(all(str_starts(setdiff(names(quality), c("pid", "wave")), "exp_|n_")))
```


# Part 5: Merge and Assertions

```{r merge}
analysis_long <- analysis_pids %>%
  left_join(survey_vars, by = c("pid", "wave")) %>%
  left_join(outcomes,    by = c("pid", "wave")) %>%
  left_join(uptake,      by = c("pid", "wave")) %>%
  left_join(quality,     by = c("pid", "wave")) %>%
  left_join(habitual,    by = "pid") %>%
  left_join(nfc_baseline %>% select(pid, nfc), by = "pid") %>%
  mutate(topic = WAVE_TOPICS[as.character(wave)])

# No join may add or duplicate rows.
stopifnot(nrow(analysis_long) == nrow(analysis_pids))
stopifnot(!any(duplicated(analysis_long[c("pid", "wave")])))

# No name collision may have produced .x / .y variants.
stopifnot(!any(str_detect(names(analysis_long), "\\.(x|y)$")))
```

Each variable's non-missing count is checked against what its construction
permits. This is the check that would have caught the Appendix G error: a
habitual measure used as an experimental exposure shows several hundred
non-missing cells per wave where the experimental measure permits at most
a hundred.

```{r coverage-assertions}
coverage <- analysis_long %>%
  group_by(wave) %>%
  summarise(
    n                = n(),
    outcome_abs      = sum(!is.na(att_abs)),
    uptake           = sum(!is.na(exp_topic_uptake_yn)),
    quality_primary  = sum(!is.na(exp_q_dur)),
    quality_news     = sum(!is.na(exp_q_dur_news)),
    quality_all      = sum(!is.na(exp_q_dur_all)),
    hab_overall      = sum(!is.na(hab_overall_dw_pc1)),
    nfc              = sum(!is.na(nfc)),
    .groups = "drop"
  )

cat("Non-missing counts by wave:\n")
coverage %>% as.data.frame() %>% print()

# Uptake is coded 0 where there was no topic-relevant visit, so it must be
# complete. Quality is left NA and must not exceed its known coverage.
stopifnot(all(coverage$uptake == coverage$n))
stopifnot(all(coverage$outcome_abs == coverage$n))
stopifnot(all(coverage$quality_primary <= coverage$n))
stopifnot(all(coverage$quality_news <= coverage$quality_primary))

# A quality measure with more non-missing cells than the primary one would
# mean a pre-treatment variable has been merged in its place.
if (any(coverage$quality_primary > 200)) {
  stop("Experimental quality coverage exceeds what the construction permits. ",
       "Check that exp_q_* comes from 02b and not from the habitual file.")
}
```

```{r habitual-timing-check}
# The moderator must be pre-treatment: it is constant within participant
# across waves, whereas any experimental measure varies.
hab_varying <- analysis_long %>%
  group_by(pid) %>%
  filter(n() > 1) %>%
  summarise(hab_varies = n_distinct(hab_overall_dw_pc1) > 1,
            exp_varies = n_distinct(exp_q_dur) > 1,
            .groups = "drop")

cat("Participants in >1 wave:", nrow(hab_varying), "\n")
cat("Habitual measure varies within participant:",
    sum(hab_varying$hab_varies), "(should be 0)\n")

stopifnot(sum(hab_varying$hab_varies) == 0)
```

# Part 6: Derived Analysis Variables

```{r derived-variables}
analysis_long <- analysis_long %>%
  mutate(
    # Primary outcome: magnitude of updating (Sec. 3.7).
    y_abs    = att_abs,
    y_signed = att_signed,

    # Primary effort measure (Eq. 3.2); duration and domains are supplementary.
    effort_count = exp_topic_uptake_n,

    # Primary exposure (Eq. 3.3, category set of Sec. 3.5).
    q_primary = exp_q_dur,

    # Treatment dummies for the ITT models (Eq. 4.2).
    t_verbal = as.integer(group_f == "verbal"),
    t_money  = as.integer(group_f == "monetary"),

    # Median splits are computed within wave, since each wave has its own
    # analytical sample.
    across(all_of(paste0("hab_", DIET_VARIANTS, "_level_group")),
    ~ factor(.x, levels = c("low", "high")))
  )

cat("Subgroup sizes by wave and diet definition:\n")
map_dfr(DIET_VARIANTS, function(v) {
  analysis_long %>%
    count(wave, group = .data[[paste0("hab_", v, "_level_group")]]) %>%
    mutate(variant = v)
}) %>%
  pivot_wider(names_from = group, values_from = n, values_fill = 0L) %>%
  as.data.frame() %>% print()
```

# Part 7: Variable Roles

Written out so that `03b` can assert on roles rather than on names, and so
that the appendix table can be generated from the data rather than typed.

```{r variable-roles}
variable_roles <- tribble(
  ~variable,                ~role,        ~timing,        ~note,
  "group_f",                "treatment",  "randomised",   "Three-level assignment",
  "z_verbal",               "instrument", "randomised",   "Verbal vs. control",
  "z_money",                "instrument", "randomised",   "Monetary vs. control",
  "y_abs",                  "outcome",    "post",         "Primary, |post - pre|",
  "y_signed",               "outcome",    "post",         "Secondary, signed",
  "kno_signed",             "outcome",    "post",         "Knowledge change",
  "exp_topic_uptake_yn",    "uptake",     "experimental", "Eq. 3.1, complete",
  "effort_count",           "effort",     "experimental", "Eq. 3.2, primary",
  "topic_duration",         "effort",     "experimental", "Supplementary",
  "n_topic_domains",        "effort",     "experimental", "Supplementary",
  "q_primary",              "exposure",   "experimental", "Eq. 3.3, primary",
  "exp_q_unw",              "exposure",   "experimental", "Eq. 3.4, sensitivity",
  "exp_q_log",              "exposure",   "experimental", "Eq. 3.5, sensitivity",
  "exp_q_dur_news",         "exposure",   "experimental", "News-only set, sensitivity",
  "exp_q_dur_all",          "exposure",   "experimental", "Incl. search, sensitivity",
  "hab_overall_level_group",        "moderator", "pre-treatment", "Median split",
  "hab_news_level_group",           "moderator", "pre-treatment", "Median split",
  "hab_news_corrected_level_group", "moderator", "pre-treatment", "Median split",
  "att_baseline",           "covariate",  "pre",          "Wave-specific",
  "prior_engagement",       "covariate",  "pre",          "Wave-specific",
  "polknow_total",          "covariate",  "baseline",     "",
  "pol_interest_general",   "covariate",  "baseline",     "",
  "newsuse_online",         "covariate",  "baseline",     "0-8 days/week",
  "edu_time",               "covariate",  "baseline",     "",
  "age",                    "covariate",  "baseline",     "",
  "gender_f",               "covariate",  "baseline",     "",
  "nfc",                    "covariate",  "baseline",     "Sec. 4.10 sensitivity only"
)

missing_vars <- setdiff(variable_roles$variable, names(analysis_long))
if (length(missing_vars) > 0) stop("Not in the dataset: ", paste(missing_vars, collapse = ", "))

variable_roles %>% count(role) %>% as.data.frame() %>% print()
write_csv(variable_roles, file.path(output_dir, "variable_roles.csv"))
```

# Part 8: Split and Save

```{r save}
analysis_data <- split(analysis_long, analysis_long$wave)
names(analysis_data) <- paste0("wave", names(analysis_data))

walk2(analysis_data, names(analysis_data), function(d, nm) {
  write_csv(d, file.path(output_dir, paste0("analysis_data_", nm, ".csv")))
})
saveRDS(analysis_data, file.path(output_dir, "analysis_data_by_wave.Rds"))

cat("Saved", length(analysis_data), "wave datasets:\n")
imap(analysis_data, ~ cat("  ", .y, ":", nrow(.x), "rows,", ncol(.x), "columns\n")) %>% invisible()
```
